### 2023-12-27 paper/sections/detector_response.tex
Initial Overleaf Import

\textbf{\textit{Detector Response and Statistical Treatment}}---
The first step in our processing chain is to attain $\nu_{e}$, $\bar{\nu}_{e}$, and $\nu_{X}$ fluxes at the detector.
These should take the form of the flux---in units of $\mathrm{MeV}^{-1}\,\mathrm{s}^{-1}\,\mathrm{cm}^{-2}$---as a function of energy at different points in time.
These fluxes are then converted to hits in the IceCube detector using the \texttt{ASTERIA} package~\cite{ASTERIA}.
In order to interface with this package, the tabulated fluxes must first be converted to a \texttt{SNEWPY}~\cite{SNEWS:2021ewj} model.
This is done using the \texttt{Analytic3Species} model, which forgoes taking the tabulated flux as an input in favor of taking the expansion of the flux up to the third moment at each point in time.
Our \texttt{ParameterizedFlux} class offers and interface between these parameters and the necessary portions of \texttt{SNEWPY} and \texttt{ASTERIA}.
Additionally, we provide a convenience function, \texttt{parameterized\_flux\_from\_txt\_files} that automatically converts from tabulated fluxes stored in text files to a \texttt{ParametrizedFlux}.

The parameters that \texttt{SNEWPY} takes in are assumed to describe the neutrino luminosity---the energy per unit time leaving the SN in neutrinos---at the source, and \texttt{SNEWPY} then handles oscillations before handing the final fluxes to \texttt{ASTERIA}.
However, this is not desirable for BSM studies since the new effects may manifest in flight, and thus we typically wish to provide the flux at the detector.
We circumvent this by taking advantage of the fact that \texttt{SNEWPY} uses the plane-wave approximation of a flux, reducing the magnitude of the flux by the the surface area of the sphere but otherwise neglecting the spherical geometry of neutrino front.
This allows us to simulate a \textit{virtual supernova} near enough to the detector that oscillations will not play a role, scaling up the input flux by an appropriate amount to get a luminosity.
Since at energies relevant to SNe, \textit{i.e.} between 1~MeV and 50~MeV, the smallest neutrino oscillation length is on the order of 100~m--50~km, we place the virtual supernova 1~m from the detector.
We have tested the impact of using different lengths and, as expected, found no impact on our final sensitivities.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/100MeV_HNL_hits-v-time.pdf}
    \caption{\textbf{\textit{Hits versus time.}}}
    \label{fig:hvt_100MeV}
\end{figure}

Having appropriately treated the flux at Earth, we can then take the number of hits created by the SM and neutrino fluxes as well as by the SM background, we may now turn to converting the hits to a sensitivity.
In our study cases, the fluxes---and thus the hits in the detector---have different temporal profiles, see Fig.~\ref{fig:hvt_100MeV}.
We then consider hits arriving within a certain time window defined by $t_{\mathrm{min.}}$ and $\Delta t$, where these times are measured relative to the so-called bounce time when the first neutrinos from the SN reach the detector.
In practice, this time can be difficult to reconstruct, and so we consider time bins that are 0.1~s wide, well larger than the uncertainty on the SN start time.
I NEED TO MAKE SURE THIS IS TRUE...
We then consider the test given by:
$$
-2\log\mathcal{L} = 2\left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}} \log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right]
$$
where $N_{\mathrm{exp.}}$ is the number of events expected from a given model and $N_{\mathrm{obs.}}$ is the number of neutrinos that would be observed in the SM only case.
We then say that we are sensitive to a given model then this test statistic exceeds 3.841. WHY ???
See Fig.~\ref{fig:sensitivity_heatmap} for an example of the test statistic as a function of these two variables for two different models.

\begin{figure}
    \centering
    \includegraphics[width=0.47\textwidth]{figures/100MeV_sensitivity_heatmap.pdf}
    \caption{\textbf{\textit{Test statistic as a function of $t_{\mathrm{start}}$ and $\Delta$t.}
    }}
    \label{fig:sensitivity_heatmap}
\end{figure}

### 2023-12-27 paper/sections/introduction.tex
Initial Overleaf Import

\textbf{\textit{Introduction}}---
Standard Model (SM) is a remarkable but also an incomplete theory. The discovery of neutrino oscillations implying non-vanishing neutrino mass, the existence of dark matter and the baryon asymmetry of the Universe seek a Beyond the Standard Model (BSM) explanation. However, we presently do not understand at what energy scale the yet undiscovered particles should appear. Numerous BSM searches across the scales have been performed, from collider searches at high energies \cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero \cite{Baumann:2015rya}. In this work we will focus on testing BSM using anticipated galactic SN explosion, where majority of emitted energy is released in the form of neutrinos carrying $\mathcal{O}(10)$ MeV energy. So far we have observed SN 1987A in neutrinos and the duration of such a signal \cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} as well as the inferred total emitted energy \cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} allow us already to set a tentative constraint that any light BSM particle copiously produced in the interior of a star could not have taken more energy than what was released in neutrinos. Indeed, many different BSM scenarios models have been constrained in this way, see \emph{e.g.} \cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.

 If, additionally, new physics particles, emitted from the SN core, can decay to neutrinos, even stronger limits can be set. In particular, after being produced, such light states stream out without further interactions and therefore typically exit with the energy of $\mathcal{O}(100)$ MeV. Neutrinos, on the other hand, interact frequently in the core and eventually leave the star with $\mathcal{O}(10)$ MeV energy. If $\mathcal{O}(100)$ MeV state can decay to neutrinos, limits can be set from the fact that $\mathcal{O}(100)$ MeV neutrinos were not recorded from SN 1987A \cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan}. once produced from SN, the new state can be non-relativistic and travels slowly, high energy neutrinos from such state decay can arrive at the detector at later time. 
 Combined with the time delay signal, searching for higher energy neutrinos from decay was recently employed to constrain neutrinophilic bosons \cite{Fiorillo:2022cdq} (throughout this work we will refer to this scenario as the Majoron model) and transition magnetic moment between active and sterile neutrino \cite{Brdar:2023tmi}. %\yy{shall we, from here, start to talk about the bright potential of IceCube?}
 We will employ these two models, which contain light BSM boson and fermion, respectively,  as a case study to illustrate that there is a plethora of low scale neutrinophilic models that can be tested.

In this work we will be focused on demonstrating the exquisite power of neutrino telescopes for testing light BSM physics from SNe. In doing so, we will chiefly focus on IceCube which has pioneered in detecting neutrinos at high energies \cite{IceCube:2014stg,IceCube:2018cha} and also from specific extragalactic sources \cite{IceCube:2023ame,IceCube:2022der}. IceCube is not optimized for SN neutrino detection at MeV energies and yet it will be very successful; IceCube would discover SN through the increase in detector noise during the SN observational window \cite{Kopke:2017req,SN2011}. In addition to discovering SN via neutrinos, in this work we will demonstrate that IceCube can constrain or discover new physics particles that are emitted from SN and decaying to neutrinos en route to Earth. Such neutrinos would induce additional activity in the photomultipliers and based on that, we will present sensitivity projections which are stronger than the present limits. While we will be focused on the two specific models mentioned above, together with this paper we also release 
a code that allows for efficient and robust calculation of projected sensitivity to an arbitrary neutrinophilic new physics realization.

### 2023-12-27 paper/sections/model.tex
Initial Overleaf Import

\textbf{\textit{The Models}}---
Let us start by discussing aforementioned new physics models in more detail.
The first scenario under consideration is active-to-sterile neutrino transition magnetic moment described by \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
\begin{align}
    \mathcal{L} \supset \sum_\alpha d_\alpha \bar{N}\sigma_{\mu\nu} \nu^{\alpha} F^{\mu\nu}-\frac{M_N}{2} \bar{N}^c N + \text{h.c.}\,,
    \label{eq:Lag}
\end{align}
where $\nu^{\alpha}$ and $N$ represent active and sterile neutrinos, respectively. Further, $F^{\mu\nu}$ is the field strength tensor of the electromagnetic field and $d_\alpha$ is the dimensionful coefficient of this dimension-5 term and $M_N$ is sterile neutrino mass. We will abbreviate $d_\alpha \equiv d$ given that we assume flavor universal interaction. The dominant production channels for $N$ inside the SN are $\nu e^- \to \nu e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies. Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}.

The second model that will be analyzed in this work is the Majoron model from \cite{Fiorillo:2022cdq}. The relevant part of the Lagrangian reads
\begin{align}
\mathcal{L} \supset -\frac{g_{\alpha\beta}}{2} \nu_\alpha \nu_\beta \phi - M_\phi \phi\phi^* + \text{h.c.}\,,
\end{align}
where $M_\phi$ is the Majoron mass and $g$ parametrizes interaction strength between $\phi$ and neutrinos. As in the previous model, we assume flavor universal interaction, hence we abbreviate $g_{\alpha\beta}\equiv g$. Majorons are produced from neutrino coalescence in the star and then subsequently decay to a pair of neutrinos with the total decay width to all flavor of neutrinos given by $\Gamma_\phi = 3g^2 m_\phi/16 \pi$, and as a result, BSM neutrino flux is produced.

%The differential number of sterile neutrinos $\mathcal{N}_s$ produced per unit time $t$ at position $r$ is \cite{Arguelles:2016uwb}
%\begin{align}
%\frac{1}{4\pi r^2}\frac{\partial^2}{\partial r\partial t}\left(\frac{d\mathcal{N}_s}{dE_N}\right)= \sigma n_\nu \frac{d n}{dE}\,.
%\label{eq:simplified}
%\end{align}
%where $\sigma n_\nu$ is the interaction rate for the production process with $n_\nu$ being the number densities of the neutrino. $n$ is the number density of electron (neutrino) for sterile neutrion $N$ (Majoron $\phi$) production. 
Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of sterile neutrino $N$ and Majoron $\phi$, and produced the cooling limit as depicted in Fig. \cref{fig:exclusion}. The results are in agreement with those obtained in literature \cite{Fiorillo:2022cdq, Brdar:2023tmi}.
%, with the  ``cooling'' bound depicted in \cref{fig:exclusion} (gray region).
%Requiring the total energy carried away by $N$ to be less than $10\%$ of the total available neutrino energy leads to the  ``cooling'' bound depicted in \cref{fig:exclusion} (gray region). Our estimate is in agreement with the one obtained in \cite{Fiorillo:2022cdq, Brdar:2023tmi}. 
As we are interested in cases where the coupling strength is below the cooling limit, these new states once produced in the SN core will stream out without further interacting with SN plasma before decaying.
 For a given emission angle $\alpha$ of daughter neutrino relative to the direction of mother particle, and the angle $\theta$ at which the daughter neutrino arrives at the Earth, the time delay $\Delta t$, the arrival time of the daughter $\gamma$/$\nu$ relative to that of the neutrinos produced in the explosion via SM processes, is \cite{Jaeckel:2017tud}
\begin{align}
    \Delta t = L_1/\beta + D_{\rm SN} \cos\theta-L_1 \cos\alpha -D_{\rm SN}\,,
    \label{eq:deltat}
\end{align}
with $D_{\rm SN}$ the distance between the SN and the Earth, and $L_1$ the distance mother particles propagated before decaying.
The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\gamma/\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$. As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
$L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained. For the time delay bounded by $\delta t = \unit[100]{s}$, $\theta < 5^\circ$ \cite{Brdar:2023tmi}. We show the fluxes of daughter neutrino in comparison to the standard neutrino flux in Fig. \cref{fig:fluxes}.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
    \caption{\textbf{\textit{Neutrino flux from Standard Model production and two majoran hypotheses.}}
    Jeff needs to write here.
    }
    \label{fig:fluxes}
\end{figure}

### 2023-12-27 paper/sections/preamble.tex
Initial Overleaf Import

\preprint{APS/123-QED, USTC-ICTS/PCFT-23-xx}

\title{Supernova Detection with Neutrino Telescopes as a Portal to New Physics}

\author{Jeff Lazar}
\email{jlazar@icecube.wisc.edu}
\affiliation{Department of Physics \& Laboratory for Particle Physics and Cosmology, Harvard University, Cambridge, MA 02138, USA}
\affiliation{Department of Physics \& Wisconsin IceCube Particle Astrophysics Center, University of Wisconsin-Madison, Madison, WI 53706, USA}
\author{Ying-Ying Li}
\email{yingyingli@ustc.edu.cn}
\affiliation{Peng Huanwu Center for Fundamental Theory, Hefei, Anhui 230026, China}
\affiliation{Interdisciplinary Center for Theoretical Study, University of Science and Technology of China, Hefei, Anhui 230026, China}
\author{Carlos A. Arg\"{u}elles}
\email{carguelles@g.harvard.edu}
\affiliation{Department of Physics \& Laboratory for Particle Physics and Cosmology, Harvard University, Cambridge, MA 02138, USA}
\author{Vedran Brdar}
\email{vedran.brdar@cern.ch}
\affiliation{Theoretical Physics Department, CERN, Esplande des Particules, 1211 Geneva 23, Switzerland}

\date{\today}

\begin{abstract}
More than 30 years ago, a handful of neutrino events from SN 1987A was recorded in several 
neutrino experiments. In this decade, several large-scale neutrino experiments will operate and be able to detect thousands of neutrino events from the next galactic supernova (SN). Such detection would not only lead to a great progress in our understanding of the astrophysical properties of SNe, but would also have a great importance in testing light dark sector models. Traditionally, the new physics constraints from SNe have been associated with SN energy loss arguments. Recently, it was shown that if light new physics states streaming out of the SN decay to neutrinos, non-observation of additional events at present and near future neutrino experiments would lead to limits that surpass the energy loss ones. In this work, focusing on the two representative new physics scenarios, we perform sensitivity projections for new physics searches at several neutrino telescopes, in particular IceCube, where a galactic SN event would be observed through the sharp rise in  photomultiplier counts. Based on these counts, new physics induced events can be constrained. The derived sensitivities strongly exceed constraints from both energy loss and non-observation of additional neutrino events from SN 1987A. We also release a code that allows for efficient computation of sensitivities for new physics searches at neutrino telescopes in the context of galactic SN event. An arbitrary light dark sector model can be studied and the only requirement is that the decay of a light dark sector particle(s) to neutrinos is realized.      
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

### 2023-12-27 sne_bsm/__init__.py
Add code

@@ -1,0 +1,2 @@
+from .units import units
+from .flux import ParameterizedFlux, parameterized_flux_from_files

### 2023-12-27 sne_bsm/compute_hits.py

@@ -1,0 +1,17 @@
+import numpy as np
+
+from tqdm.notebook import tqdm
+
+import os
+if "ASTERIA" not in os.environ.keys():
+    raise RuntimeError(
+        "'ASTERIA' not in os.environ.keys"
+    )
+os.environ["ASTERIA"] = "/Users/jlazar/research/ASTERIA"
+
+import astropy.units as u
+
+from snewpy.models import ccsn
+from asteria.simulation import Simulation
+
+from ic_sn_hnl import units, ParameterizedFlux

### 2023-12-27 sne_bsm/flux/__init__.py

@@ -1,0 +1,1 @@
+from .parametrize_flux import ParameterizedFlux, parameterized_flux_from_files

### 2023-12-27 sne_bsm/flux/flux.py

@@ -1,0 +1,26 @@
+import numpy as np
+
+from abc import ABC
+
+from ..units import units
+
+class Flux(ABC):
+    """Base class for fluxes"""
+
+    def __init__(self):
+        pass
+
+    def get_flux(self, t: float, enu: float, nutype: int) -> float:
+        """
+        Returns the flux at a certain energy at a certain point
+        in time
+        """
+        pass
+
+    def get_hits(
+        self,
+        tmin=units["second"],
+        tmax=20*units["second"],
+        dt=0.01*units["second"]
+    ) -> np.ndarray:
+        pass

### 2023-12-27 sne_bsm/flux/parametrize_flux.py

@@ -1,0 +1,580 @@
+import numpy as np
+import h5py as h5
+import os
+
+from tqdm import tqdm
+from dataclasses import dataclass
+from scipy.integrate import quad
+from scipy.interpolate import interp1d
+from scipy.special import gamma
+from asteria.simulation import Simulation
+
+from .flux import Flux
+from .sanitize_flux import sanitize_flux
+from ..units import units
+
+from typing import Tuple, List
+
+@dataclass
+class Params:
+    L: float
+    e_exp: float
+    rms: float
+    alpha: float
+
+    def __add__(self, other):
+        if not(isinstance(self, Params) and isinstance(other, Params)):
+            raise ValueError()
+        return Params(
+            self.L + other.L,
+            self.e_exp + other.e_exp,
+            self.rms + other.rms,
+            self.alpha + other.alpha
+        )
+
+    def __sub__(self, other):
+        if not(isinstance(self, Params) and isinstance(other, Params)):
+            raise ValueError()
+        return Params(
+            self.L - other.L,
+            self.e_exp - other.e_exp,
+            self.rms - other.rms,
+            self.alpha - other.alpha
+        )
+
+    def __rmul__(self, other):
+        return Params(
+            other * self.L,
+            other * self.e_exp,
+            other * self.rms,
+            other * self.alpha,
+        )
+
+    def __mul__(self, other):
+        return Params(
+            other * self.L,
+            other * self.e_exp,
+            other * self.rms,
+            other * self.alpha,
+        )
+
+
+def parameterized_flux_from_files(
+    nuefile: str,
+    nuebarfile: str,
+    nuxfile: str,
+    dist: float,
+    thin=1,
+    track=True
+):
+    nuearr = massage_infile(nuefile)
+    nuebararr = massage_infile(nuebarfile)
+    nuxarr = massage_infile(nuxfile)
+    _validate_fluxes(nuearr, nuebararr, nuxarr)
+    params = parameterize(nuearr, nuebararr, nuxarr, thin=thin, track=track)
+    return ParameterizedFlux(params, dist)
+ 
+def parameterized_flux_from_h5(
+    group: h5.Group,
+    dist: float,
+    thin: int=1,
+    track: bool=True
+):
+    times = group["times"][::thin]
+    energies = group["energies"][:]
+    fluxes = group["fluxes"][::thin, :, :]
+    params = []
+    itr = enumerate(times)
+    if track:
+        itr = enumerate(tqdm(times))
+    for idx, time in itr:
[…]

### 2023-12-27 sne_bsm/flux/sanitize_flux.py

@@ -1,0 +1,44 @@
+import numpy as np
+
+def find_first_spike(arr: np.ndarray, thresh=1e-10):
+
+    if len(arr)==0:
+        return 0
+    
+    if arr[0]==0 or arr[-1]==0:
+        raise ValueError("Array cannot start with zero")
+    
+    for idx, (v1, v2) in enumerate(zip(arr, arr[1:])):
+        if v2==0:
+            continue
+        if v1 / v2 < thresh:
+            return idx + 1
+    return 0
+
+def argtrim_zeros(arr: np.ndarray):
+    l, r = 0, len(arr)
+    
+    # Catch length 0 arrays
+    if r==0:
+        return l, r
+    
+    while arr[l]==0:
+        l += 1
+        # Catch arrays that are full 0s
+        if l==len(arr):
+            return l, r
+    
+    while arr[r-1]==0:
+        r -= 1
+        
+    return l, r
+
+def sanitize_flux(energies: np.ndarray, flux: np.ndarray):
+    l, r = argtrim_zeros(flux)
+    flux = flux[l:r]
+    energies = energies[l:r]
+
+    idx = find_first_spike(flux)
+    flux = flux[idx:]
+    energies = energies[idx:]
+    return energies, flux

### 2024-01-03 sne_bsm/flux/parametrize_flux.py
Add hacky rebinning fix

@@ -230,7 +230,8 @@ class ParameterizedFlux(Flux):
             "dE": de / units["MeV"] * u.MeV,
             "tmin": tmin / units["second"] * u.s,
             "tmax": tmax / units["second"] * u.s,
-            "dt": dt / units["second"] * u.s,
+            "dt": 1e-3 * u.s,
+            #"dt": dt / units["second"] * u.s,
             "mixing_scheme": mixing_scheme,
             "hierarchy": mass_ordering,
         }
@@ -297,6 +298,8 @@ class ParameterizedFlux(Flux):
             keep_model_file=keep_model_file,
             dist0=dist0
         )
+        if dt!=1e-3*units.second:
+            sim.rebin_result(dt / units["second"] * u.s)
         t, hits = sim.detector_signal(dt / units["second"] * u.s)
         return t.value * units["second"], hits
         

### 2024-01-03 paper/main.tex

\documentclass[aps,twocolumn,prl,showpacs,showkeys,preprintnumbers,superscriptaddress,nobibnotes,floatfix,longbibliography,notitlepage,nofootinbib]{revtex4-2}

\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{comment}
\usepackage{bbold}
\usepackage[shortlabels]{enumitem}
\usepackage{color}
\usepackage{slashed}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{footnote}
\usepackage{lipsum}
\usepackage{multirow}
%\usepackage{longtable}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage{braket}
\usepackage[compat=1.1.0]{tikz-feynman}
\usepackage{multirow}
\usepackage{physics}
\usepackage{feynmp-auto}
\usepackage[normalem]{ulem}
\usepackage{url}
\usepackage{units}
\usepackage[normalem]{ulem}
\newcommand{\yy}[1]{\color{red}[YY:#1]\color{black}}

\input{sections/packages}
\begin{document}

\input{paper/sections/preamble}
\input{paper/sections/introduction}
\input{paper/sections/model}
\input{paper/sections/detector_response}
\input{paper/sections/stats}
\input{paper/`sections/conclusion}

\bibliography{ic_sn_hnl}

\end{document}

% Outline
- Introduction: 
- Detector response
  - What kind of noise, Standard neutrino
  - Atm. background reduction ?
- SNEWPY treatment for general models the pipeline etc.
  - The two models that we have condsidered Lagrangians
  - fluxes and results for them
- Conclusion
  - IC is useful for SN
  - Use our software

### 2024-01-03 paper/sections/detector_response.tex

@@
 \textbf{\textit{Detector Response and Statistical Treatment}}---
-The first step in our processing chain is to attain $\nu_{e}$, $\bar{\nu}_{e}$, and $\nu_{X}$ fluxes at the detector.
-These should take the form of the flux---in units of $\mathrm{MeV}^{-1}\,\mathrm{s}^{-1}\,\mathrm{cm}^{-2}$---as a function of energy at different points in time.
-These fluxes are then converted to hits in the IceCube detector using the \texttt{ASTERIA} package~\cite{ASTERIA}.
-In order to interface with this package, the tabulated fluxes must first be converted to a \texttt{SNEWPY}~\cite{SNEWS:2021ewj} model.
-This is done using the \texttt{Analytic3Species} model, which forgoes taking the tabulated flux as an input in favor of taking the expansion of the flux up to the third moment at each point in time.
-Our \texttt{ParameterizedFlux} class offers and interface between these parameters and the necessary portions of \texttt{SNEWPY} and \texttt{ASTERIA}.
-Additionally, we provide a convenience function, \texttt{parameterized\_flux\_from\_txt\_files} that automatically converts from tabulated fluxes stored in text files to a \texttt{ParametrizedFlux}.
+% The first step in our processing chain is to attain $\nu_{e}$, $\bar{\nu}_{e}$, and $\nu_{X}$ fluxes at the detector.
+% These should take the form of the flux---in units of $\mathrm{MeV}^{-1}\,\mathrm{s}^{-1}\,\mathrm{cm}^{-2}$---as a function of energy at different points in time.
+% These fluxes are then converted to hits in the IceCube detector using the \texttt{ASTERIA} package~\cite{ASTERIA}.
+% In order to interface with this package, the tabulated fluxes must first be converted to a \texttt{SNEWPY}~\cite{SNEWS:2021ewj} model.
+% This is done using the \texttt{Analytic3Species} model, which forgoes taking the tabulated flux as an input in favor of taking the expansion of the flux up to the third moment at each point in time.
+% Our \texttt{ParameterizedFlux} class offers and interface between these parameters and the necessary portions of \texttt{SNEWPY} and \texttt{ASTERIA}.
+% Additionally, we provide a convenience function, \texttt{parameterized\_flux\_from\_txt\_files} that automatically converts from tabulated fluxes stored in text files to a \texttt{ParametrizedFlux}.
 
-The parameters that \texttt{SNEWPY} takes in are assumed to describe the neutrino luminosity---the energy per unit time leaving the SN in neutrinos---at the source, and \texttt{SNEWPY} then handles oscillations before handing the final fluxes to \texttt{ASTERIA}.
-However, this is not desirable for BSM studies since the new effects may manifest in flight, and thus we typically wish to provide the flux at the detector.
-We circumvent this by taking advantage of the fact that \texttt{SNEWPY} uses the plane-wave approximation of a flux, reducing the magnitude of the flux by the the surface area of the sphere but otherwise neglecting the spherical geometry of neutrino front.
-This allows us to simulate a \textit{virtual supernova} near enough to the detector that oscillations will not play a role, scaling up the input flux by an appropriate amount to get a luminosity.
-Since at energies relevant to SNe, \textit{i.e.} between 1~MeV and 50~MeV, the smallest neutrino oscillation length is on the order of 100~m--50~km, we place the virtual supernova 1~m from the detector.
-We have tested the impact of using different lengths and, as expected, found no impact on our final sensitivities.
+% The parameters that \texttt{SNEWPY} takes in are assumed to describe the neutrino luminosity---the energy per unit time leaving the SN in neutrinos---at the source, and \texttt{SNEWPY} then handles oscillations before handing the final fluxes to \texttt{ASTERIA}.
+% However, this is not desirable for BSM studies since the new effects may manifest in flight, and thus we typically wish to provide the flux at the detector.
+% We circumvent this by taking advantage of the fact that \texttt{SNEWPY} uses the plane-wave approximation of a flux, reducing the magnitude of the flux by the the surface area of the sphere but otherwise neglecting the spherical geometry of neutrino front.
+% This allows us to simulate a \textit{virtual supernova} near enough to the detector that oscillations will not play a role, scaling up the input flux by an appropriate amount to get a luminosity.
+% Since at energies relevant to SNe, \textit{i.e.} between 1~MeV and 50~MeV, the smallest neutrino oscillation length is on the order of 100~m--50~km, we place the virtual supernova 1~m from the detector.
+% We have tested the impact of using different lengths and, as expected, found no impact on our final sensitivities.
 
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.47\textwidth]{figures/100MeV_HNL_hits-v-time.pdf}
-    \caption{\textbf{\textit{Hits versus time.}}}
-    \label{fig:hvt_100MeV}
-\end{figure}
+% \begin{figure}[t!]
+%     \centering
+%     \includegraphics[width=0.47\textwidth]{figures/100MeV_HNL_hits-v-time.pdf}
+%     \caption{\textbf{\textit{Hits versus time.}}}
+%     \label{fig:hvt_100MeV}
+% \end{figure}
 
-Having appropriately treated the flux at Earth, we can then take the number of hits created by the SM and neutrino fluxes as well as by the SM background, we may now turn to converting the hits to a sensitivity.
-In our study cases, the fluxes---and thus the hits in the detector---have different temporal profiles, see Fig.~\ref{fig:hvt_100MeV}.
-We then consider hits arriving within a certain time window defined by $t_{\mathrm{min.}}$ and $\Delta t$, where these times are measured relative to the so-called bounce time when the first neutrinos from the SN reach the detector.
-In practice, this time can be difficult to reconstruct, and so we consider time bins that are 0.1~s wide, well larger than the uncertainty on the SN start time.
-I NEED TO MAKE SURE THIS IS TRUE...
-We then consider the test given by:
-$$
--2\log\mathcal{L} = 2\left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}} \log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right]
-$$
-where $N_{\mathrm{exp.}}$ is the number of events expected from a given model and $N_{\mathrm{obs.}}$ is the number of neutrinos that would be observed in the SM only case.
-We then say that we are sensitive to a given model then this test statistic exceeds 3.841. WHY ???
-See Fig.~\ref{fig:sensitivity_heatmap} for an example of the test statistic as a function of these two variables for two different models.
+% Having appropriately treated the flux at Earth, we can then take the number of hits created by the SM and neutrino fluxes as well as by the SM background, we may now turn to converting the hits to a sensitivity.
+% In our study cases, the fluxes---and thus the hits in the detector---have different temporal profiles, see Fig.~\ref{fig:hvt_100MeV}.
+% We then consider hits arriving within a certain time window defined by $t_{\mathrm{min.}}$ and $\Delta t$, where these times are measured relative to the so-called bounce time when the first neutrinos from the SN reach the detector.
+% In practice, this time can be difficult to reconstruct, and so we consider time bins that are 0.1~s wide, well larger than the uncertainty on the SN start time.
+% I NEED TO MAKE SURE THIS IS TRUE...
+% We then consider the test given by:
+% $$
+% -2\log\mathcal{L} = 2\left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}} \log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right]
+% $$
+% where $N_{\mathrm{exp.}}$ is the number of events expected from a given model and $N_{\mathrm{obs.}}$ is the number of neutrinos that would be observed in the SM only case.
+% We then say that we are sensitive to a given model then this test statistic exceeds 3.841.
+% See Fig.~\ref{fig:sensitivity_heatmap} for an example of the test statistic as a function of these two variables for two different models.
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.47\textwidth]{figures/100MeV_sensitivity_heatmap.pdf}
-    \caption{\textbf{\textit{Test statistic as a function of $t_{\mathrm{start}}$ and $\Delta$t.}
-    }}
-    \label{fig:sensitivity_heatmap}
-\end{figure}
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.47\textwidth]{figures/100MeV_sensitivity_heatmap.pdf}
+%     \caption{\textbf{\textit{Test statistic as a function of $t_{\mathrm{start}}$ and $\Delta$t.}
+%     }}
+%     \label{fig:sensitivity_heatmap}
+% \end{figure}

### 2024-01-05 paper/sections/introduction.tex
Updates from Overleaf

@@
 \textbf{\textit{Introduction}}---
-Standard Model (SM) is a remarkable but also an incomplete theory.
-The discovery of neutrino oscillations implying non-vanishing neutrino mass, the existence of dark matter and the baryon asymmetry of the Universe seek a Beyond the Standard Model (BSM) explanation.
-However, we presently do not understand at what energy scale the yet undiscovered particles should appear.
+The Standard Model (SM) is a remarkable but incomplete theory.
+Puzzles such as the non-vanishing tiny neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, all seek explanations beyond the Standard Model (BSM).
+However, there are no affirmative clues for the energy scale the yet undiscovered particles should appear.
 Numerous BSM searches across the scales have been performed, from collider searches at high energies \cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero \cite{Baumann:2015rya}.
-In this work we will focus on testing BSM using anticipated galactic SN explosion, where majority of emitted energy is released in the form of neutrinos carrying $\mathcal{O}(10)$ MeV energy.
-So far we have observed SN 1987A in neutrinos and the duration of such a signal \cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} as well as the inferred total emitted energy \cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} allow us already to set a tentative constraint that any light BSM particle copiously produced in the interior of a star could not have taken more energy than what was released in neutrinos.
+Galactic SN explosion, where majority of emitted energy is released in the form of neutrinos, offers unique opportunities in testing BSM physics via interactions with active neutrinos.
+So far we have observed SN 1987A in neutrinos.
+The duration of such a signal \cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} as well as the inferred total emitted energy \cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} allow us already to set a tentative constraint on the energies that could be taken away from any light BSM particle copiously produced in the interior of a star.
 Indeed, many different BSM scenarios models have been constrained in this way, see \emph{e.g.} \cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.
@@
 If, additionally, new physics particles, emitted from the SN core, can decay to neutrinos, even stronger limits can be set.
-In particular, after being produced, such light states stream out without further interactions and therefore typically exit with the energy of $\mathcal{O}(100)$ MeV.
-Neutrinos, on the other hand, interact frequently in the core and eventually leave the star with $\mathcal{O}(10)$ MeV energy.
-If $\mathcal{O}(100)$ MeV state can decay to neutrinos, limits can be set from the fact that $\mathcal{O}(100)$ MeV neutrinos were not recorded from SN 1987A \cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan}.
-once produced from SN, the new state can be non-relativistic and travels slowly, high energy neutrinos from such state decay can arrive at the detector at later time.
- Combined with the time delay signal, searching for higher energy neutrinos from decay was recently employed to constrain neutrinophilic bosons \cite{Fiorillo:2022cdq} (throughout this work we will refer to this scenario as the Majoron model) and transition magnetic moment between active and sterile neutrino \cite{Brdar:2023tmi}.
-%\yy{shall we, from here, start to talk about the bright potential of IceCube?}
- We will employ these two models, which contain light BSM boson and fermion, respectively,  as a case study to illustrate that there is a plethora of low scale neutrinophilic models that can be tested.
+In particular, for the standard case, neutrinos interact frequently in the core and eventually leave the star with $\mathcal{O}(10)$ MeV energy.
+New states after being produced can stream out without further interactions.
+Consequently, they typically exit with higher energies, subsequently decaying into neutrinos with an energy on the order of $\mathcal{O}(100)$ MeV.
+Limits can be set from the fact that such high energy neutrinos were not recorded from SN 1987A \cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan, Fiorillo:2022cdq, Brdar:2023tmi}.
+Once produced from SN, the new state can be non-relativistic and travels slowly, causing time delays to the arrival time of its daughter particle which was also recently employed \cite{Brdar:2023tmi} for a time window around one day.
+However, as being decoupled immediately, it is possible that new states can exit the supernova at an earlier time instead—an effect that has not been previously considered.
+These two effects in combination would cause advanced or delayed neutrino signals to the standard case.
 
-In this work we will be focused on demonstrating the exquisite power of neutrino telescopes for testing light BSM physics from SNe.
-In doing so, we will chiefly focus on IceCube which has pioneered in detecting neutrinos at high energies \cite{IceCube:2014stg,IceCube:2018cha} and also from specific extragalactic sources \cite{IceCube:2023ame,IceCube:2022der}.
-IceCube is not optimized for SN neutrino detection at MeV energies and yet it will be very successful; IceCube would discover SN through the increase in detector noise during the SN observational window \cite{Kopke:2017req,SN2011}.
-In addition to discovering SN via neutrinos, in this work we will demonstrate that IceCube can constrain or discover new physics particles that are emitted from SN and decaying to neutrinos en route to Earth.
-Such neutrinos would induce additional activity in the photomultipliers and based on that, we will present sensitivity projections which are stronger than the present limits.
-While we will be focused on the two specific models mentioned above, together with this paper we also release
-a code that allows for efficient and robust calculation of projected sensitivity to an arbitrary neutrinophilic new physics realization.
+On the other hand, neutrino telescopes such as IceCube have not only pioneered in detecting neutrinos at ultra-high energies \cite{IceCube:2014stg,IceCube:2018cha} and from specific extragalactic sources \cite{IceCube:2023ame,IceCube:2022der}, but also in testing temporal correlation of MeV neutrino events with fast radio bursts with its precise timing measurements \cite{IceCube:2019acm}.
+In this work, we demonstrate that such timing measurements will play a crucial role in tracking the delayed neutrino signals, and interestingly reveil new features of advanced neutrino signals coming from the immediate-decoupling of its mother particles.
+This novel timing patterns generically exist in models with new weakly interacting particles, such as sterile neutrino via the dipole portal \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi} or mixing portals \cite{Arg_elles_2019, Suliga_2020}, Majoron models \cite{Fiorillo:2022cdq}.
+Once produced inside the SN, these particles stream out at an earlier time than the standard neutrino signal.
+Meanwhile, for non-negligible mass, these particle would travel slower than active neutrino before decaying or converting back to active neutrinos.
+Via the timing measurement, we will show that neutrino telescope can provide unprecedented constraints on the parameter space in BSM.\\

### 2024-01-05 paper/sections/detector_response.tex
Updates from Overleaf

--- 2023-12-27 paper/sections/detector_response.tex
@@
-\textbf{\textit{Detector Response and Statistical Treatment}}---
-The first step in our processing chain is to attain $\nu_{e}$, $\bar{\nu}_{e}$, and $\nu_{X}$ fluxes at the detector.
-These should take the form of the flux---in units of $\mathrm{MeV}^{-1}\,\mathrm{s}^{-1}\,\mathrm{cm}^{-2}$---as a function of energy at different points in time.
-These fluxes are then converted to hits in the IceCube detector using the \texttt{ASTERIA} package~\cite{ASTERIA}.
-In order to interface with this package, the tabulated fluxes must first be converted to a \texttt{SNEWPY}~\cite{SNEWS:2021ewj} model.
-This is done using the \texttt{Analytic3Species} model, which forgoes taking the tabulated flux as an input in favor of taking the expansion of the flux up to the third moment at each point in time.
-Our \texttt{ParameterizedFlux} class offers and interface between these parameters and the necessary portions of \texttt{SNEWPY} and \texttt{ASTERIA}.
-Additionally, we provide a convenience function, \texttt{parameterized\_flux\_from\_txt\_files} that automatically converts from tabulated fluxes stored in text files to a \texttt{ParametrizedFlux}.
+\textbf{\textit{Detector Response and Statistical Treatment}}---In order to simulate the
 
-The parameters that \texttt{SNEWPY} takes in are assumed to describe the neutrino luminosity---the energy per unit time leaving the SN in neutrinos---at the source, and \texttt{SNEWPY} then handles oscillations before handing the final fluxes to \texttt{ASTERIA}.
-However, this is not desirable for BSM studies since the new effects may manifest in flight, and thus we typically wish to provide the flux at the detector.
-We circumvent this by taking advantage of the fact that \texttt{SNEWPY} uses the plane-wave approximation of a flux, reducing the magnitude of the flux by the the surface area of the sphere but otherwise neglecting the spherical geometry of neutrino front.
-This allows us to simulate a \textit{virtual supernova} near enough to the detector that oscillations will not play a role, scaling up the input flux by an appropriate amount to get a luminosity.
-Since at energies relevant to SNe, \textit{i.e.} between 1~MeV and 50~MeV, the smallest neutrino oscillation length is on the order of 100~m--50~km, we place the virtual supernova 1~m from the detector.
-We have tested the impact of using different lengths and, as expected, found no impact on our final sensitivities.
-
-\begin{figure}[t!]
+\begin{figure*}
     \centering
-    \includegraphics[width=0.47\textwidth]{figures/100MeV_HNL_hits-v-time.pdf}
-    \caption{\textbf{\textit{Hits versus time.}}}
-    \label{fig:hvt_100MeV}
-\end{figure}
-
-Having appropriately treated the flux at Earth, we can then take the number of hits created by the SM and neutrino fluxes as well as by the SM background, we may now turn to converting the hits to a sensitivity.
-In our study cases, the fluxes---and thus the hits in the detector---have different temporal profiles, see Fig.~\ref{fig:hvt_100MeV}.
-We then consider hits arriving within a certain time window defined by $t_{\mathrm{min.}}$ and $\Delta t$, where these times are measured relative to the so-called bounce time when the first neutrinos from the SN reach the detector.
-In practice, this time can be difficult to reconstruct, and so we consider time bins that are 0.1~s wide, well larger than the uncertainty on the SN start time.
-I NEED TO MAKE SURE THIS IS TRUE...
-We then consider the test given by:
-$$
--2\log\mathcal{L} = 2\left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}} \log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right]
-$$
-where $N_{\mathrm{exp.}}$ is the number of events expected from a given model and $N_{\mathrm{obs.}}$ is the number of neutrinos that would be observed in the SM only case.
-We then say that we are sensitive to a given model then this test statistic exceeds 3.841. WHY ???
-See Fig.~\ref{fig:sensitivity_heatmap} for an example of the test statistic as a function of these two variables for two different models.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.47\textwidth]{figures/100MeV_sensitivity_heatmap.pdf}
+    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
     \caption{\textbf{\textit{Test statistic as a function of $t_{\mathrm{start}}$ and $\Delta$t.}
     }}
-    \label{fig:sensitivity_heatmap}
-\end{figure}
+    \label{fig:hits_and_likelihood}
+\end{figure*}

### 2024-01-05 paper/sections/preamble.tex

@@
-\preprint{APS/123-QED, USTC-ICTS/PCFT-23-xx}
+\preprint{APS/123-QED, USTC-ICTS/PCFT-24-xx}
 
-\title{Supernova Detection with Neutrino Telescopes as a Portal to New Physics}
+\title{Time Prints of New Physics at Neutrino Telescopes
+%Supernova Detection with Neutrino Telescopes as a Portal to New Physics
+}
 
@@
 \email{vedran.brdar@cern.ch}
+\affiliation{Department of Physics, Oklahoma State University, Stillwater, OK, 74078, USA}
 \affiliation{Theoretical Physics Department, CERN, Esplande des Particules, 1211 Geneva 23, Switzerland}

### 2024-01-05 paper/sections/model.tex

@@
 \textbf{\textit{The Models}}---
-Let us start by discussing aforementioned new physics models in more detail.
-The first scenario under consideration is active-to-sterile neutrino transition magnetic moment described by \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
-\begin{align}
-    \mathcal{L} \supset \sum_\alpha d_\alpha \bar{N}\sigma_{\mu\nu} \nu^{\alpha} F^{\mu\nu}-\frac{M_N}{2} \bar{N}^c N + \text{h.c.}\,,
-    \label{eq:Lag}
-\end{align}
-where $\nu^{\alpha}$ and $N$ represent active and sterile neutrinos, respectively.
-Further, $F^{\mu\nu}$ is the field strength tensor of the electromagnetic field and $d_\alpha$ is the dimensionful coefficient of this dimension-5 term and $M_N$ is sterile neutrino mass.
-We will abbreviate $d_\alpha \equiv d$ given that we assume flavor universal interaction.
-The dominant production channels for $N$ inside the SN are $\nu e^- \to \nu e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies.
-Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}.
-
-The second model that will be analyzed in this work is the Majoron model from \cite{Fiorillo:2022cdq}. The relevant part of the Lagrangian reads
+As an example, we will consider the Majoron model.
+Nevertheless the study can also be applied to sterile neutrinos via magnetic portal.
+For the case of sterile neutrino with mixing portal, special care needs to be taken for resonant conversions in which case active neutrinos with plasma mass would travel as slowly as the sterile neutrinos at specific distances.
+The relevant part of the Lagrangian in the Majoron case reads
 \begin{align}
@@
 where $M_\phi$ is the Majoron mass and $g$ parametrizes interaction strength between $\phi$ and neutrinos.
-As in the previous model, we assume flavor universal interaction, hence we abbreviate $g_{\alpha\beta}\equiv g$.
+Consider flavor universal interaction, we abbreviate $g_{\alpha\beta}\equiv g$.
 Majorons are produced from neutrino coalescence in the star and then subsequently decay to a pair of neutrinos with the total decay width to all flavor of neutrinos given by $\Gamma_\phi = 3g^2 m_\phi/16 \pi$, and as a result, BSM neutrino flux is produced.
 
-%The differential number of sterile neutrinos $\mathcal{N}_s$ produced per unit time $t$ at position $r$ is \cite{Arguelles:2016uwb}
-%\begin{align}
-%\frac{1}{4\pi r^2}\frac{\partial^2}{\partial r\partial t}\left(\frac{d\mathcal{N}_s}{dE_N}\right)= \sigma n_\nu \frac{d n}{dE}\,.
-%\label{eq:simplified}
-%\end{align}
-%where $\sigma n_\nu$ is the interaction rate for the production process with $n_\nu$ being the number densities of the neutrino.
-$n$ is the number density of electron (neutrino) for sterile neutrion $N$ (Majoron $\phi$) production.
-Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of sterile neutrino $N$ and Majoron $\phi$, and produced the cooling limit as depicted in Fig.
-\cref{fig:exclusion}.
-The results are in agreement with those obtained in literature \cite{Fiorillo:2022cdq, Brdar:2023tmi}.
-%, with the  ``cooling'' bound depicted in \cref{fig:exclusion} (gray region).
-%Requiring the total energy carried away by $N$ to be less than $10\%$ of the total available neutrino energy leads to the  ``cooling'' bound depicted in \cref{fig:exclusion} (gray region).
-Our estimate is in agreement with the one obtained in \cite{Fiorillo:2022cdq, Brdar:2023tmi}.
-As we are interested in cases where the coupling strength is below the cooling limit, these new states once produced in the SN core will stream out without further interacting with SN plasma before decaying.
- For a given emission angle $\alpha$ of daughter neutrino relative to the direction of mother particle, and the angle $\theta$ at which the daughter neutrino arrives at the Earth, the time delay $\Delta t$, the arrival time of the daughter $\gamma$/$\nu$ relative to that of the neutrinos produced in the explosion via SM processes, is \cite{Jaeckel:2017tud}
+Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of Majoron $\phi$, and produced the cooling limit.
+The results are in agreement with those obtained in literature \cite{Fiorillo:2022cdq}.
+As mentioned above, for the regions below the coupling strength, Majorons produced will immediately stream out.
+Along its way towards the Earth, Majorons will decay to active neutrinos.
+For a given emission angle $\alpha$ of daughter neutrino relative to the direction of mother particle, and the angle $\theta$ at which the daughter neutrino arrives at the Earth, the time delay $\Delta t$, the arrival time of the daughter $\nu$ relative to that of the neutrinos produced in the explosion via SM processes, is \cite{Jaeckel:2017tud}
 \begin{align}
@@
 with $D_{\rm SN}$ the distance between the SN and the Earth, and $L_1$ the distance mother particles propagated before decaying.
-The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\gamma/\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$.
+The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$.
 As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
-$L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained.
-For the time delay bounded by $\delta t = \unit[100]{s}$, $\theta < 5^\circ$ \cite{Brdar:2023tmi}.
-We show the fluxes of daughter neutrino in comparison to the standard neutrino flux in Fig.
-\cref{fig:fluxes}.
-
+$L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}.
+For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrino in comparison to the standard neutrino flux in \cref{fig:fluxes} at different time.
 \begin{figure}[t!]
@@
     Jeff needs to write here.
+{\color{red} Also, as for 1MeV case, the limit is set by the flux between 0.01s -0.1s, shall we choose t = 0.05s as one benchmark time in this plot?
+we can choose t = 0.05, 0.1, 0.5, 1, 5.
+Also I forgot why I can only see four lines here for each color?}
     }
@@
 \end{figure}
+{\color{red} Yingying will add some discussions about the updated flux plot.}

### 2024-01-05 paper/sections/detector_response.tex

@@
-\textbf{\textit{Detector Response and Statistical Treatment}}---In order to simulate the
+\textbf{\textit{Detector Response and Statistical Treatment}}---Neutrinos produced by SNe do not have sufficient energy to be individually resolved; however, the large number of neutrinos arriving together gives rise to a temporally localized increase in the noise rate of the detector.
+In order to simulate the signal the prreviously described models would produce, we use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} software.
+This program estimates the light yield from low-energy neutrinos in the IceCube Neutrino Observatory.
+In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY} packages, which allows us to define custom supernova fluxes.
 

### 2024-01-05 paper/sections/introduction.tex

@@
 
-On the other hand, neutrino telescopes such as IceCube have not only pioneered in detecting neutrinos at ultra-high energies \cite{IceCube:2014stg,IceCube:2018cha} and from specific extragalactic sources \cite{IceCube:2023ame,IceCube:2022der}, but also in testing temporal correlation of MeV neutrino events with fast radio bursts with its precise timing measurements \cite{IceCube:2019acm}.
-In this work, we demonstrate that such timing measurements will play a crucial role in tracking the delayed neutrino signals, and interestingly reveil new features of advanced neutrino signals coming from the immediate-decoupling of its mother particles.
-This novel timing patterns generically exist in models with new weakly interacting particles, such as sterile neutrino via the dipole portal \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi} or mixing portals \cite{Arg_elles_2019, Suliga_2020}, Majoron models \cite{Fiorillo:2022cdq}.
+On the other hand, neutrino telescopes such as IceCube have not only pioneered in detecting neutrinos at ultra-high energies \cite{IceCube:2014stg,IceCube:2018cha} and from specific extragalactic sources \cite{IceCube:2023ame,IceCube:2022der},but also in testing temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm} by detecting a collective rise in all photomultiplier rates within a time window as short as 0.01 second on the top of the background noise.
+In this work, we demonstrate that such precise time resolutions will play a crucial role in tracking the delayed neutrino signals, and interestingly reveil new features of advanced neutrino signals coming from the immediate-decoupling of its mother particles.
+This novel timing patterns generically exist in models with new weakly interacting particles, such as the aforementioned Majoron models \cite{Fiorillo:2022cdq}, sterile neutrino via the dipole portal \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi} or mixing portals \cite{Arg_elles_2019, Suliga_2020}.
 Once produced inside the SN, these particles stream out at an earlier time than the standard neutrino signal.
-Meanwhile, for non-negligible mass, these particle would travel slower than active neutrino before decaying or converting back to active neutrinos.
+Meanwhile, for non-negligible mass, they would travel slower than active neutrino before decaying or converting back to active neutrinos.
 Via the timing measurement, we will show that neutrino telescope can provide unprecedented constraints on the parameter space in BSM.\\

### 2024-01-05 paper/sections/model.tex

@@
 
-Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of Majoron $\phi$, and produced the cooling limit.
-The results are in agreement with those obtained in literature \cite{Fiorillo:2022cdq}.
+Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of Majoron $\phi$, and produced the cooling limit, which is in agreement with those obtained in literature \cite{Fiorillo:2022cdq}.
 As mentioned above, for the regions below the coupling strength, Majorons produced will immediately stream out.
@@
 with $D_{\rm SN}$ the distance between the SN and the Earth, and $L_1$ the distance mother particles propagated before decaying.
+
 The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$.
@@
 $L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}.
-For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrino in comparison to the standard neutrino flux in \cref{fig:fluxes} at different time.
+For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrino in comparison to the standard neutrino flux in \cref{fig:fluxes} at different times for two benchmarks
 \begin{figure}[t!]
@@
     Jeff needs to write here.
-{\color{red} Also, as for 1MeV case, the limit is set by the flux between 0.01s -0.1s, shall we choose t = 0.05s as one benchmark time in this plot?
-we can choose t = 0.05, 0.1, 0.5, 1, 5.
-Also I forgot why I can only see four lines here for each color?}
     }
@@
 \end{figure}
-{\color{red} Yingying will add some discussions about the updated flux plot.}

### 2024-01-05 paper/sections/conclusion.tex
Updates from Overleaf

\textbf{\textit{Results}}---
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_sensitivity}
    \caption{\textbf{\textit{Exclusion limit for the majoron case.}}
    }
    \label{fig:sensitivity}
\end{figure}
We present the exclusion limit in \fig{sensitivity}.

\textbf{\textit{Outlook}}---

### 2024-01-05 paper/sections/model.tex
Updates from Overleaf

@@
 $L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}.
-For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrino in comparison to the standard neutrino flux in \cref{fig:fluxes} at different times for two benchmarks
+For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrinos at different time for two benchmarks of the Majoron case, in comparison to the standard neutrino flux in \cref{fig:fluxes}.
+We can observe that the energy of neutrinos from Majoron decay extends to $\unit[100]{Mev}$ and above, as expected.
+For heavy Majoron case, the resulting neutrino flux typically is larger at later time, manifesting the time delay from slowly moving Majorons.
+The flux for light Majoron case contain very rich physics.
 \begin{figure}[t!]
@@
     \caption{\textbf{\textit{Neutrino flux from Standard Model production and two majoran hypotheses.}}
-    Jeff needs to write here.
+    Jeff needs to write here. {\color{red}also need to write the couplings used}
     }
     \label{fig:fluxes}
-\end{figure}
+\end{figure}\\

### 2024-01-05 paper/sections/detector_response.tex

--- 2024-01-05 paper/sections/detector_response.tex
@@
-\textbf{\textit{Detector Response and Statistical Treatment}}---In order to simulate the
+\textbf{\textit{Detector Response and Statistical Treatment}}---While neutrinos produced by SNe do not have sufficient energy to be individually resolved by neutrino telescopes, the large number arriving together generates a temporally localized increase in the detector's noise rate.
+In order to simulate the light yield from signal the previously described models would produce, we use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} software.
+This program uses parameteriations of \texttt{GEANT4} photon yields from neutrino interactions and photon propagation to estimate the light observed for different neutrino 
+In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY} packages, which allows us to define custom supernova fluxes.
 

### 2024-01-18 paper/sections/conclusion.tex
Updates from Overleaf

@@
     \includegraphics[width=0.47\textwidth]{figures/majoran_sensitivity}
-    \caption{\textbf{\textit{Exclusion limit for the majoron case.}}
+    \caption{\textbf{\textit{Exclusion sensitivities for the Majoron case.}}
+    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
+    Additionally, we also show the reaches by SN cooling (blue) and by the lack of observation of high-energy neutrinos from SN1987A (grey) \cite{Fiorillo:2022cdq}, with the width of the lines quantifying uncertainties from SN modeling.
     }
@@
 \end{figure}
-We present the exclusion limit in \fig{sensitivity}.
+Looking for rapid raises within various time windows at neutrino telescope in the occurrence of future nearby SN explosion will provide exceptional tests of the parameter space.
+Assuming the SN event happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}, we consider the currently operating IceCube neutrino observatory as an example.
+The expected exclusion limit are shown in \cref{fig:sensitivity} (dark red) if no excess of hits on top of those from background noise and the standard neutrino flux were observed.
+JUNO expected to start taking data soon, while DUNE and Hyper-K requiring longer time to start operating, will be able to test the parameter of Majorons by looking for high energy neutrino following \cite{Fiorillo:2022cdq} if such SN event happens during their operation time.
+We present the estimated reaches of JUNO, DUNE and Hyper-K in \cref{fig:sensitivity} as xxx, red and orange lines, respectively, leaving aside careful detector analysis, together with current limits \cite{Fiorillo:2022cdq} from the aforementioned energy loss requirement (blue band), and non-observation of high energy neutrinos from SN 1987A (gray band) in \cref{fig:sensitivity}.
+
+We observe that while for the intermediate mass region, the constraints from IceCube are comparable to that from DUNE and Hyper-K, at both low mass region $m_\phi \lesssim \unit[10]{MeV}$ and high mass region $m_\phi \gtrsim \unit[200]{MeV}$, IceCube can provide stronger constraints.
+This is the outcome we expect.
+For light $\phi$ case with negligible time delay, the neutrino signals can  arrive at the detector even before the peak of standard neutrino flux arrives.
+The resulting hits would appear in a time window separated from that when most of standard flux contribution appears, as we show in the left panel of \cref{fig:hits_and_likelihood}, thus enhancing the reaches.
+On the high mass end, neutrino signals will arrive much later than the standard case, where a time window at late time can be considered to reduce the standard neutrino contaminations.
+
+Uncertainties on the analysis from different modeling SN explosion are minor, as studies in \cite{li2023old} and potential discrepancies between data and modeling are unresolved questions.
+Nevertheless we point out that the discrepancy could be within $2\sigma$ level which will only change our exclusion limit by a small factor.
 
 \textbf{\textit{Outlook}}---
+we can also study axion cases, mixing cases with this strategy. Pre-supernova bouncing.
+
+\begin{acknowledgments}
+We would like to thank xxx for stimulating discussions about this work. Y.-Y. L is supported by the NSF of China through Grant
+No. 12247103 and Grant No. xxx.
+\end{acknowledgments}

### 2024-01-18 paper/sections/detector_response.tex
Updates from Overleaf

--- 2024-01-05 paper/sections/detector_response.tex
@@
-\textbf{\textit{Detector Response and Statistical Treatment}}---In order to simulate the
+\textbf{\textit{Detector Response and Statistical Treatment}}---The IceCube Neutrino Observatory comprises 5,160 light-detecting digital optical modules (DOMs) buried in a cubic kilometer of the deep, transparent Antarctic ice sheet.
+When neutrinos interact within or near the detector, the charged by-products emit photons that the DOMs can detect.
+The DOMs are arranged on 86 strings of 60 DOMs with an inter-string distance between 70~m and 125~m.
+This enables IceCube to resolve individual neutrinos with energies approximately ranging between a few GeV and a few PeV.
+The neutrinos produced by SNe are far below this threshold, and the neutrinos cannot be individually resolved; however, the immense number of neutrinos produced in a SN produces an increase in the single-photon rate of the detector.
+This increase in the rate of photons can be distinguished by the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic SNe events~\cite{Griswold:2023iwz}.
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
-    \caption{\textbf{\textit{Test statistic as a function of $t_{\mathrm{start}}$ and $\Delta$t.}
-    }}
-    \label{fig:hits_and_likelihood}
-\end{figure*}
+New neutrino physics will affect the development of a SN, and will distort the temporal structure of the photon signal seen in the IceCube detector.
+Thus, one may look for excess events in certain time intervals as evidence of this new physics.
+In this work, we simulate the light curve produced by a standard SN with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for example light curves.
+We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package in order to simulate the detector response to the different SNe scenarios as well as the thermal and radioactive noise in the DOMs.
+\yy{we need to provide a brief recasting of simulating the detector response, especially for different flavors.}
+This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, inverse beta decay of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$.
+In order to interface to this package, we use \texttt{SNEWPY}~\cite{baxter2021snewpy} package and, in particular, the \texttt{ParametrizedFlux} object.
+
+With the number of hits in the detector from noise, SM-only scenarios, and BSM scenarios as a function of time, we can then quantify the probability of seeing a certain number of hits in a given time window with:
+\begin{equation}
+    -2\Delta\mathrm{LLH} = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right].
+    % -2\Delta\mathrm{LLH}(t_{\mathrm{start}}, \Delta t) = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right].
+\end{equation}
+where $N_{\mathrm{obs.}}$ is the number of photons seen in the detector in the given time given and $N_{\mathrm{exp.}}$ is the number of photons expected from a particular BSM hypothesis.
+In the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}, we show the likelihood space as a function of the time at which the time range begins, $t_{\mathrm{start}}$ and the duration of the time range, $\Delta t$ for an example BSM hypothesis.
+
+For each physics hypothesis, we then select the time range that maximizes the test statistic and use that maximal test statistic value.
+The optimal ranges for each physics hypothesis are shown by the dashed lines and arrows in the left panel of Fig.~\ref{fig:hits_and_likelihood}.

### 2024-01-18 paper/sections/model.tex
Updates from Overleaf

--- 2024-01-05 paper/sections/model.tex
@@
 As an example, we will consider the Majoron model.
-Nevertheless the study can also be applied to sterile neutrinos via magnetic portal.
+Nevertheless the study can also be applied to sterile neutrinos via magnetic portal, as we discuss in the Supplementary Materials.
 For the case of sterile neutrino with mixing portal, special care needs to be taken for resonant conversions in which case active neutrinos with plasma mass would travel as slowly as the sterile neutrinos at specific distances.
@@
 \begin{align}
-\mathcal{L} \supset -\frac{g_{\alpha\beta}}{2} \nu_\alpha \nu_\beta \phi - M_\phi \phi\phi^* + \text{h.c.}\,,
+\mathcal{L} \supset -\frac{g_{\alpha\beta}}{2} \nu_\alpha \nu_\beta \phi - m_\phi \phi\phi^* + \text{h.c.}\,,
 \end{align}
-where $M_\phi$ is the Majoron mass and $g$ parametrizes interaction strength between $\phi$ and neutrinos.
+where $m_\phi$ is the Majoron mass and $g$ parametrizes interaction strength between $\phi$ and neutrinos.
 Consider flavor universal interaction, we abbreviate $g_{\alpha\beta}\equiv g$.
@@
 
-Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of Majoron $\phi$, and produced the cooling limit, which is in agreement with those obtained in literature \cite{Fiorillo:2022cdq}.
+Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of standard neutrino case that can be fitted to the parametrization in \cite{baxter2021snewpy} and the fluxes of Majoron $\phi$.
+Requiring the energy loss to Majorons to be less than 10\% of the standard neutrino energy, we can produce the cooling limit, which is in agreement with those obtained in literature \cite{Fiorillo:2022cdq}.
 As mentioned above, for the regions below the coupling strength, Majorons produced will immediately stream out.
@@
 \end{align}
-with $D_{\rm SN}$ the distance between the SN and the Earth, and $L_1$ the distance mother particles propagated before decaying.
-
+with $D_{\rm SN}$ the distance between the SN and the Earth, $L_1$ the distance mother particles propagated before decaying, and $\beta$ being the speed of $\phi$.
 The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$.
@@
 $L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}.
-For $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show the differential fluxes of daughter neutrino in comparison to the standard neutrino flux in \cref{fig:fluxes} at different times for two benchmarks
+
 \begin{figure}[t!]
@@
     \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
-    \caption{\textbf{\textit{Neutrino flux from Standard Model production and two majoran hypotheses.}}
-    Jeff needs to write here.
+    \caption{\textit{\textbf{Neutrino flux from Standard Model production and two majoron hypotheses}.
+    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.7}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[100]{MeV}$, respectively.}
     }
@@
 \end{figure}
+
+For $D_{\rm SN} = \unit[10]{kpc}$ and $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show in \cref{fig:fluxes} the differential fluxes of daughter neutrinos at different time for two benchmarks of the Majoron case, in comparison to the standard neutrino flux.
+We can observe that the energy of neutrinos from Majoron decay extends to $\unit[100]{MeV}$ and above, as expected.
+For heavy Majoron case, the resulting neutrino flux typically is larger at later time, manifesting the time delay from slowly moving Majorons.
+The flux for light Majoron case contain very rich physics.
+Majorons, generating neutrinos with $E_\nu \geq \unit[150]{MeV}$, are nearly-relativistic with its daughter particles moving in parallel.
+In such a case, for couplings comparable to or larger than the one shown in \cref{fig:fluxes}, $\Delta t \sim L_d (1/\beta -1)\lesssim \unit[0.01]{sec}$, with $L_d = E_\phi/m_\phi \Gamma^{-1}_\phi \beta$ being the decay length of $\phi$ for the given $\phi$ energy $E_\phi$.
+The time dependence of neutrino flux thus are mainly inherited from the Majorons upon production, which exhibits in \cref{fig:fluxes} larger fluxes from producing Majorons from the denser and hotter core of SN at earlier time.
+For neutrinos with lower energy, i.e $E_\nu \lesssim \unit[40]{MeV}$, the mother Majorons can be non-relativistic, resulting in $\Delta t \gtrsim \unit[0.04]{sec}$.
+This non-negligible time delay would shift the neutrino flux to later time, lowering the fluxes at earlier time as shown in \cref{fig:fluxes}.
+For the heavy mass benchmark in \cref{fig:fluxes}, we have $\Delta t \gtrsim 10 sec$, which would yield the active neutrino flux at sizeable $t\sim \mathcal{sec}$.
+
+%in details in the following, we consider energy deposits at the photomultipliers, 
+%due to denser and hotter core of SN  as Majorans shortly after the bouncing time $t_{\rm bounce}$ from the hot dense core of SN.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
+    \caption{\textbf{\textit{Test statistic as a function of $t_{\mathrm{start}}$ and $\Delta$t.}
+    }}
+    \label{fig:hits_and_likelihood}
+\end{figure*}

### 2024-01-18 paper/sections/preamble.tex
Updates from Overleaf

@@
 \preprint{APS/123-QED, USTC-ICTS/PCFT-24-xx}
-
-\title{Time Prints of New Physics at Neutrino Telescopes
-%Supernova Detection with Neutrino Telescopes as a Portal to New Physics
+\bibliographystyle{apsrev4-1}
+\title{
+% New Physics in Supernovae at Neutrino Telescopes
+% Time Prints of New Physics from Supernovae at Neutrino Telescopes
+% Supernova Detection with Neutrino Telescopes as a Portal to New Physics
+Supernovae Time Profiles as a Portal to New Physics at Neutrino Telescopes
 }
@@
 \author{Vedran Brdar}
-\email{vedran.brdar@cern.ch}
+\email{vedran.brdar@okstate.edu}
 \affiliation{Department of Physics, Oklahoma State University, Stillwater, OK, 74078, USA}
-\affiliation{Theoretical Physics Department, CERN, Esplande des Particules, 1211 Geneva 23, Switzerland}
 
-\date{\today}
+%\date{\today}
 
 \begin{abstract}
-More than 30 years ago, a handful of neutrino events from SN 1987A was recorded in several 
-neutrino experiments.
-In this decade, several large-scale neutrino experiments will operate and be able to detect thousands of neutrino events from the next galactic supernova (SN).
-Such detection would not only lead to a great progress in our understanding of the astrophysical properties of SNe, but would also have a great importance in testing light dark sector models.
-Traditionally, the new physics constraints from SNe have been associated with SN energy loss arguments.
-Recently, it was shown that if light new physics states streaming out of the SN decay to neutrinos, non-observation of additional events at present and near future neutrino experiments would lead to limits that surpass the energy loss ones.
-In this work, focusing on the two representative new physics scenarios, we perform sensitivity projections for new physics searches at several neutrino telescopes, in particular IceCube, where a galactic SN event would be observed through the sharp rise in  photomultiplier counts.
-Based on these counts, new physics induced events can be constrained.
-The derived sensitivities strongly exceed constraints from both energy loss and non-observation of additional neutrino events from SN 1987A.
-We also release a code that allows for efficient computation of sensitivities for new physics searches at neutrino telescopes in the context of galactic SN event.
-An arbitrary light dark sector model can be studied and the only requirement is that the decay of a light dark sector particle(s) to neutrinos is realized.
+Neutrino telescopes, such as IceCube, have promised precise time resolutions at the millisecond level for detecting collective rise signals in all photomultiplier.
+We demonstrate that such precise time resolutions will play a crucial role in tracking neutrino signals with novel timing patterns related to weakly interacting massive particles in physics beyond the Standard Model.
+Focusing on future Supernova explosion in the operation time of IceCube, Focusing on a future Supernova explosion in the operation time of IceCube as an example, we show that neutrino telescopes can provide unprecedented probes of new particles with both low and high masses, where neutrino signals are advanced and delayed, respectively, while comparable to DUNE and Hyper-K in the intermediate mass region.
 \end{abstract}

### 2024-01-18 paper/sections/supplements.tex
Updates from Overleaf

\section{Appendix A: Dipole Magnetic Moment Portal}
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/magnetic_moment_sensitivity}
    \caption{\textbf{\textit{Exclusion sensitivities for the magnetic moment case.}}
    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE. The shaded regions are excluded by the energy loss constraints, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by   constraints on the energy release from SN explosion following \cite{PhysRevLett.128.221103}.
    }
    \label{fig:magnetic_moment_sensitivity}
\end{figure}
The first scenario under consideration is active-to-sterile neutrino transition magnetic moment described by \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
\begin{align}
    \mathcal{L} \supset \sum_\alpha d_\alpha \bar{N}\sigma_{\mu\nu} \nu^{\alpha} F^{\mu\nu}-\frac{M_N}{2} \bar{N}^c N + \text{h.c.}\,,
    \label{eq:Lag}
\end{align}
where $\nu^{\alpha}$ and $N$ represent active and sterile neutrinos, respectively. Further, $F^{\mu\nu}$ is the field strength tensor of the electromagnetic field and $d_\alpha$ is the dimensionful coefficient of this dimension-5 term and $M_N$ is sterile neutrino mass. We will abbreviate $d_\alpha \equiv d$ given that we assume flavor universal interaction. The dominant production channels for $N$ inside the SN are $\nu e^- \to \nu e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies. Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}. We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$sec, which overlaps with the standard burst time scale. We don't expect improvements over DUNE and Hyper-K.

{\color{red} Check the bg for DUNE and Hyper-K is the atmospheric neutrino bg which should also contribute to our analysis? IceCube sees at}

### 2024-01-23 paper/sections/preamble.tex

@@
 We demonstrate that such precise time resolutions will play a crucial role in tracking neutrino signals with novel timing patterns related to weakly interacting massive particles in physics beyond the Standard Model.
-Focusing on future Supernova explosion in the operation time of IceCube, Focusing on a future Supernova explosion in the operation time of IceCube as an example, we show that neutrino telescopes can provide unprecedented probes of new particles with both low and high masses, where neutrino signals are advanced and delayed, respectively, while comparable to DUNE and Hyper-K in the intermediate mass region.
+Focusing on a future Supernova explosion in the operation time of IceCube as an example, we show that neutrino telescopes can provide unprecedented probes of new particles with both low and high masses from probing early-glow and after-glow neutrino signals, respectively, while comparable to DUNE and Hyper-K in the intermediate mass region.
 \end{abstract}

### 2024-01-23 paper/sections/supplements.tex

@@
 We will abbreviate $d_\alpha \equiv d$ given that we assume flavor universal interaction.
-The dominant production channels for $N$ inside the SN are $\nu e^- \to \nu e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies.
+The dominant production channels for $N$ inside the SN are $\nu e^- \to N e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies.
 Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}.
-We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$sec, which overlaps with the standard burst time scale.
+The limits from IceCube are shown in \cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}.
+We also estimates the excluded regions (xxx shaded) where photons from $N$ decay inside the photosphere exceeds the energy release observed following \cite{PhysRevLett.128.221103}.
+We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$ sec, which overlaps with the standard burst time scale.
 We don't expect improvements over DUNE and Hyper-K.
-
-{\color{red} Check the bg for DUNE and Hyper-K is the atmospheric neutrino bg which should also contribute to our analysis? IceCube sees at}
+We also point out by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside supernove, all the limits presented in \cref{fig:magnetic_moment_sensitivity} are conservative.

### 2024-01-23 paper/sections/conclusion.tex

@@
     The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
-    Additionally, we also show the reaches by SN cooling (blue) and by the lack of observation of high-energy neutrinos from SN1987A (grey) \cite{Fiorillo:2022cdq}, with the width of the lines quantifying uncertainties from SN modeling.
+    Additionally, we also show the reaches by SN cooling (blue) and by the lack of observation of high-energy neutrinos from SN1987A (grey) \cite{Fiorillo:2022cdq}, with the width of the shading region quantifying uncertainties from SN modeling.
     }
@@
 The expected exclusion limit are shown in \cref{fig:sensitivity} (dark red) if no excess of hits on top of those from background noise and the standard neutrino flux were observed.
-JUNO expected to start taking data soon, while DUNE and Hyper-K requiring longer time to start operating, will be able to test the parameter of Majorons by looking for high energy neutrino following \cite{Fiorillo:2022cdq} if such SN event happens during their operation time.
-We present the estimated reaches of JUNO, DUNE and Hyper-K in \cref{fig:sensitivity} as xxx, red and orange lines, respectively, leaving aside careful detector analysis, together with current limits \cite{Fiorillo:2022cdq} from the aforementioned energy loss requirement (blue band), and non-observation of high energy neutrinos from SN 1987A (gray band) in \cref{fig:sensitivity}.
+DUNE and Hyper-K will be operating and be able to test the parameter of Majorons by looking for time-integrated high energy neutrinos following \cite{Fiorillo:2022cdq} if such SN event happens during their operation time.
+We present the estimated reaches of DUNE and Hyper-K in \cref{fig:sensitivity} as red and orange lines, respectively, leaving aside careful detector analysis, together with current limits \cite{Fiorillo:2022cdq} from the aforementioned energy loss requirement (blue band), and non-observation of high energy neutrinos from SN 1987A (gray band) in \cref{fig:sensitivity}.
 
@@
 
-Uncertainties on the analysis from different modeling SN explosion are minor, as studies in \cite{li2023old} and potential discrepancies between data and modeling are unresolved questions.
-Nevertheless we point out that the discrepancy could be within $2\sigma$ level which will only change our exclusion limit by a small factor.
+Uncertainties on the analysis from different modeling SN explosions are minor, as studies in \cite{li2023old} and potential discrepancies between data and modeling are unresolved questions.
+Nevertheless, we point out that the discrepancy could be within $2\sigma$ level which will only change our exclusion limit by a small factor.
+We also provide the code used in this work so that the impact of SN modeling uncertainties on the sensitivity of neutrino telescopes may be evaluated in the future.
 
 \textbf{\textit{Outlook}}---
-we can also study axion cases, mixing cases with this strategy. Pre-supernova bouncing.
+We demonstrated that neutrino telescope such as IceCube provides unprecedented probes of new physics, such as Majoron neutrinos and sterile neutrinos with magnetic portal, via measuring Supernova time profiles to a window as short as $\mathcal{O}(0.01)$ sec.
+Signatures outside the standard signal time window, including early-glow and after-glow, can be probed at neutrino telescope which enhances probes of new physics.
+This analysis can also be extended to probing new particles such as sterile neutrinos with mixing portal where the resulting time profile requires more dedicated studies, especially for resonantly conversions.
 

### 2024-01-23 paper/sections/detector_response.tex

@@
 This enables IceCube to resolve individual neutrinos with energies approximately ranging between a few GeV and a few PeV.
-The neutrinos produced by SNe are far below this threshold, and the neutrinos cannot be individually resolved; however, the immense number of neutrinos produced in a SN produces an increase in the single-photon rate of the detector.
+The neutrinos produced by SNe are far below this threshold, and the neutrinos cannot be individually resolved; however, the immense number of neutrinos produced in an SN produces an increase in the single-photon rate of the detector.
 This increase in the rate of photons can be distinguished by the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic SNe events~\cite{Griswold:2023iwz}.
@@
 We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package in order to simulate the detector response to the different SNe scenarios as well as the thermal and radioactive noise in the DOMs.
-\yy{we need to provide a brief recasting of simulating the detector response, especially for different flavors.}
+\yy{we need to provide a brief recasting of simulating the detector response, especially for different flavors.} \yy{contributions to bg}
 This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, inverse beta decay of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$.

### 2024-01-23 paper/sections/introduction.tex

@@
 However, as being decoupled immediately, it is possible that new states can exit the supernova at an earlier time instead—an effect that has not been previously considered.
-These two effects in combination would cause advanced or delayed neutrino signals to the standard case.
+This early-glow signal can also be induced by light new states produced from $\nu_e$ scattering inside the supernova given that $\nu_e$ burst happens at an earlier time than the other neutrino flavors \cite{Brdar_2018}.
 

### 2024-01-23 paper/sections/model.tex

@@
     \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
-    \caption{\textit{\textbf{Neutrino flux from Standard Model production and two majoron hypotheses}.
-    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.7}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[100]{MeV}$, respectively.}
+    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from Standard Model production and two majoron hypotheses}}.
+    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
     }
@@
 This non-negligible time delay would shift the neutrino flux to later time, lowering the fluxes at earlier time as shown in \cref{fig:fluxes}.
-For the heavy mass benchmark in \cref{fig:fluxes}, we have $\Delta t \gtrsim 10 sec$, which would yield the active neutrino flux at sizeable $t\sim \mathcal{sec}$.
+For the heavy mass benchmark in \cref{fig:fluxes}, we have $\Delta t \gtrsim \unit[10]{sec}$, which would yield the active neutrino flux at sizeable $t$.
 
@@
     \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
-    \caption{\textbf{\textit{Test statistic as a function of $t_{\mathrm{start}}$ and $\Delta$t.}
-    }}
+    \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
+    These are the same points in the parameter space as Fig.~\ref{fig:fluxes}.
+    }
     \label{fig:hits_and_likelihood}

### 2024-02-03 paper/sections/model.tex
Updates from Overleaf

@@
     We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
+    In the case of the lower-mass model, the majoron can still travel relativistically, leading to a peak in the spectrum at an earlier time.
+    In the case of the higher-mass model, the majoron travels subliminally, and thus, the flux peaks at later times.
+    Since the dominant interaction is inverse beta decay at these energies, we expect the observed timing distribution to follow the $\bar{\nu}_{e}$
     }
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
-    \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
-    These are the same points in the parameter space as Fig.~\ref{fig:fluxes}.
-    }
-    \label{fig:hits_and_likelihood}
-\end{figure*}
+% \begin{figure*}
+%     \centering
+%     \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
+%     \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
+%     These are the same points in the parameter space as Fig.~\ref{fig:fluxes}.
+%     }
+%     \label{fig:hits_and_likelihood}
+% \end{figure*}

### 2024-02-03 paper/sections/detector_response.tex

@@
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
+    \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
+    The hit rate from the SM neutrino flux peaks at around 0.1~s, coinciding with the peak emission of $\bar{\nu}_{e}$ from the SN.
+    The shaded regions correspond to the timing windows that give peak sensitivity to the particular model.
+    The low-mass models can give more prompt signals since they decay quickly and travel luminally, while the subliminal speeds and relatively long decay times for larger-mass models lead to a delayed signal.
+    In the right panel, we show the test statistic as a function of the starting time and length of the window.
+    The relatively broad distribution of high test-statistic values shows that this analysis technique does not require extremely precise reconstruction of the $t_{\mathrm{bounce}}$.
+    These are the same points in the parameter space as Fig.~\ref{fig:fluxes}.
+    }
+    \label{fig:hits_and_likelihood}
+\end{figure*}
+\
 \textbf{\textit{Detector Response and Statistical Treatment}}---The IceCube Neutrino Observatory comprises 5,160 light-detecting digital optical modules (DOMs) buried in a cubic kilometer of the deep, transparent Antarctic ice sheet.
@@
 
-New neutrino physics will affect the development of a SN, and will distort the temporal structure of the photon signal seen in the IceCube detector.
+New neutrino physics will affect the development of an SN and distort the temporal structure of the photon signal seen in the IceCube detector.
 Thus, one may look for excess events in certain time intervals as evidence of this new physics.
 In this work, we simulate the light curve produced by a standard SN with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for example light curves.
-We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package in order to simulate the detector response to the different SNe scenarios as well as the thermal and radioactive noise in the DOMs.
-\yy{we need to provide a brief recasting of simulating the detector response, especially for different flavors.} \yy{contributions to bg}
+Since more than 93\% of the photons detected in IceCube originate in inverse beta decay interactions, the SM-only event rate peaks at around 0.1~s.
+BSM scenarios, on the other hand, can give rise to a prompt or delayed signal depending on the particulars of the model.
+For instance, since low-mass majorons have fast decay times, they can escape the SN early and decay to an all-flavor flux of neutrinos, producing $\bar{\nu}_{e}$ before the SM peak.
+The higher-mass majorons, on the other hand, decay less quickly and acquire a time decay from traveling sub-luminally, thus producing a later signal.
+We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different SNe scenarios and the thermal and radioactive noise in the DOMs.
 This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, inverse beta decay of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$.
 In order to interface to this package, we use \texttt{SNEWPY}~\cite{baxter2021snewpy} package and, in particular, the \texttt{ParametrizedFlux} object.
+In addition to photons produced in neutrino interactions, this package also simulates photons from thermal noise in the IceCube PMTs and from radioactive decay in the pressure glass housing.
 
@@
 For each physics hypothesis, we then select the time range that maximizes the test statistic and use that maximal test statistic value.
-The optimal ranges for each physics hypothesis are shown by the dashed lines and arrows in the left panel of Fig.~\ref{fig:hits_and_likelihood}.
+The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}.
+Furthermore, the test statistic value relative to the SM-only hypothesis is shown in the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}.
+The distribution of test-statistic values is not sharply peaked, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}$ $\mathcal{O}\left(1~\mathrm{s}\right)$.

### 2024-02-21 paper/sections/detector_response.tex
Updates from Overleaf

@@
     The shaded regions correspond to the timing windows that give peak sensitivity to the particular model.
-    The low-mass models can give more prompt signals since they decay quickly and travel luminally, while the subliminal speeds and relatively long decay times for larger-mass models lead to a delayed signal.
     In the right panel, we show the test statistic as a function of the starting time and length of the window.
@@
 This enables IceCube to resolve individual neutrinos with energies approximately ranging between a few GeV and a few PeV.
-The neutrinos produced by SNe are far below this threshold, and the neutrinos cannot be individually resolved; however, the immense number of neutrinos produced in an SN produces an increase in the single-photon rate of the detector.
-This increase in the rate of photons can be distinguished by the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic SNe events~\cite{Griswold:2023iwz}.
+The neutrinos produced by SNe are far below this threshold, and the neutrinos cannot be individually resolved; however, the immense number of neutrinos produced in an SN increases the single-photon rate of the detector.
+This dramatic increase in the rate of photons can be distinguished from the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic CCSNe events~\cite{Griswold:2023iwz}.
 
@@
 Thus, one may look for excess events in certain time intervals as evidence of this new physics.
-In this work, we simulate the light curve produced by a standard SN with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for example light curves.
+In this work, we simulate the light curve produced by a standard SN with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios aforementioned; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for light curves of the same two benchmarks discussed above.
 Since more than 93\% of the photons detected in IceCube originate in inverse beta decay interactions, the SM-only event rate peaks at around 0.1~s.
-BSM scenarios, on the other hand, can give rise to a prompt or delayed signal depending on the particulars of the model.
-For instance, since low-mass majorons have fast decay times, they can escape the SN early and decay to an all-flavor flux of neutrinos, producing $\bar{\nu}_{e}$ before the SM peak.
-The higher-mass majorons, on the other hand, decay less quickly and acquire a time decay from traveling sub-luminally, thus producing a later signal.
+BSM scenarios, on the other hand, can give rise to an early or delayed signal depending on the particulars of the model.
+In essence, Majorons can be generated before the peak of SM $\bar{\nu}_{e}$ flux and as light majorons can travel nearly relativistically, they can escape the SN with negligible time-delay then decay to an all-flavor flux of neutrinos, producing early $\bar{\nu}_{e}$ fluxes before the SM case.
+The higher-mass majorons, on the other hand acquire a time decay from traveling sub-luminally and at a large detour, thus producing a later signal with sizable time delay.
 We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different SNe scenarios and the thermal and radioactive noise in the DOMs.
  This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, inverse beta decay of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$.
-In order to interface to this package, we use \texttt{SNEWPY}~\cite{baxter2021snewpy} package and, in particular, the \texttt{ParametrizedFlux} object.
+In order to interface to this package, we use \texttt{SNEWPY}~\cite{SNEWS:2021ewj} package and, in particular, the \texttt{ParametrizedFlux} object.
 In addition to photons produced in neutrino interactions, this package also simulates photons from thermal noise in the IceCube PMTs and from radioactive decay in the pressure glass housing.
@@
 \end{equation}
-where $N_{\mathrm{obs.}}$ is the number of photons seen in the detector in the given time given and $N_{\mathrm{exp.}}$ is the number of photons expected from a particular BSM hypothesis.
+where $N_{\mathrm{obs.}}$ is the number of photons seen in the detector in the given time and $N_{\mathrm{exp.}}$ is the number of photons expected from a particular BSM hypothesis.
 In the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}, we show the likelihood space as a function of the time at which the time range begins, $t_{\mathrm{start}}$ and the duration of the time range, $\Delta t$ for an example BSM hypothesis.
@@
 For each physics hypothesis, we then select the time range that maximizes the test statistic and use that maximal test statistic value.
-The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}.
+The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}, which is around $\unit[0.1]{s}$ ($\unit[10]{s}$) for the light (heavy) benchmark case, consistent with its time spread of $\bar{\nu}_e$ flux produced.
 Furthermore, the test statistic value relative to the SM-only hypothesis is shown in the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}.
-The distribution of test-statistic values is not sharply peaked, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}$ $\mathcal{O}\left(1~\mathrm{s}\right)$.
+The distribution of test-statistic values is not sharply peaked, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$ \cite{Halzen_2009}.

### 2024-02-21 paper/sections/introduction.tex
Updates from Overleaf

--- 2024-01-05 paper/sections/introduction.tex
@@
 The Standard Model (SM) is a remarkable but incomplete theory.
-Puzzles such as the non-vanishing tiny neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, all seek explanations beyond the Standard Model (BSM).
-However, there are no affirmative clues for the energy scale the yet undiscovered particles should appear.
-Numerous BSM searches across the scales have been performed, from collider searches at high energies \cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero \cite{Baumann:2015rya}.
-Galactic SN explosion, where majority of emitted energy is released in the form of neutrinos, offers unique opportunities in testing BSM physics via interactions with active neutrinos.
-So far we have observed SN 1987A in neutrinos.
-The duration of such a signal \cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} as well as the inferred total emitted energy \cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} allow us already to set a tentative constraint on the energies that could be taken away from any light BSM particle copiously produced in the interior of a star.
-Indeed, many different BSM scenarios models have been constrained in this way, see \emph{e.g.} \cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.
+Puzzles such as the non-vanishing neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, seek explanations beyond the Standard Model (BSM).
+There are also no firmly established clues on the energy scale at which the new particles should appear.
+To this end, numerous BSM searches across the scales have been performed, from collider searches at high energies \cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero \cite{Baumann:2015rya}.
+Core collapse supernovae (CCSNe) release most energy in neutrinos, offering unique opportunities to test BSM physics via interactions with neutrinos.
+The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only CCSN observed in neutrinos---have already given tentative constraints on the energies that could be taken away by any light BSM particle copiously produced in the interior of a star.
+Indeed, many different BSM scenarios models have been constrained in this way, see \textit{e.g.}~\cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.
 
-If, additionally, new physics particles, emitted from the SN core, can decay to neutrinos, even stronger limits can be set.
-In particular, for the standard case, neutrinos interact frequently in the core and eventually leave the star with $\mathcal{O}(10)$ MeV energy.
-New states after being produced can stream out without further interactions.
-Consequently, they typically exit with higher energies, subsequently decaying into neutrinos with an energy on the order of $\mathcal{O}(100)$ MeV.
-Limits can be set from the fact that such high energy neutrinos were not recorded from SN 1987A \cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan, Fiorillo:2022cdq, Brdar:2023tmi}.
-Once produced from SN, the new state can be non-relativistic and travels slowly, causing time delays to the arrival time of its daughter particle which was also recently employed \cite{Brdar:2023tmi} for a time window around one day.
-However, as being decoupled immediately, it is possible that new states can exit the supernova at an earlier time instead—an effect that has not been previously considered.
-These two effects in combination would cause advanced or delayed neutrino signals to the standard case.
+If, additionally, BSM particles emitted from supernovae can decay to neutrinos en route to Earth, even stronger limits can be set, as shown for instance in \cite{Fiorillo:2022cdq} for Majoron-like bosons and in \cite{Brdar:2023tmi} for a realization featuring neutrino magnetic moment portal.
+Specifically, unlike neutrinos inside the supernova core, produced BSM states can stream out without further interactions.
+Consequently, they exit with higher energies than neutrinos, typically around $\mathcal{O}(100)$ MeV.
+Provided such particles decay to neutrinos, strong limits can be set from the fact that $\mathcal{O}(100)$ MeV energy neutrinos were not recorded from SN 1987A \cite{Fiorillo:2022cdq, Brdar:2023tmi}.
+So far, such strategies were utilized for neutrino experiments operating during the SN 1987A event as well as future DUNE \cite{DUNE:2015lol} and Hyper-Kamiokande \cite{Hyper-Kamiokande:2018ofw} in light of anticipated galactic supernova event.
+%However, as being decoupled immediately, it is possible that new states can exit the supernova at an earlier time instead---an effect that has not been previously considered.
+%This early-glow signal can also be induced by light new states produced from $\nu_e$ scattering inside the supernova given that $\nu_e$ burst happens at an earlier time than the other neutrino flavors \cite{Brdar_2018}.
 
-On the other hand, neutrino telescopes such as IceCube have not only pioneered in detecting neutrinos at ultra-high energies \cite{IceCube:2014stg,IceCube:2018cha} and from specific extragalactic sources \cite{IceCube:2023ame,IceCube:2022der}, but also in testing temporal correlation of MeV neutrino events with fast radio bursts with its precise timing measurements \cite{IceCube:2019acm}.
-In this work, we demonstrate that such timing measurements will play a crucial role in tracking the delayed neutrino signals, and interestingly reveil new features of advanced neutrino signals coming from the immediate-decoupling of its mother particles.
-This novel timing patterns generically exist in models with new weakly interacting particles, such as sterile neutrino via the dipole portal \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi} or mixing portals \cite{Arg_elles_2019, Suliga_2020}, Majoron models \cite{Fiorillo:2022cdq}.
-Once produced inside the SN, these particles stream out at an earlier time than the standard neutrino signal.
-Meanwhile, for non-negligible mass, these particle would travel slower than active neutrino before decaying or converting back to active neutrinos.
-Via the timing measurement, we will show that neutrino telescope can provide unprecedented constraints on the parameter space in BSM.\\
+On the other hand, neutrino telescopes such as IceCube has pioneered in detecting neutrinos at $\mathcal{O}$(PeV) energies \cite{IceCube:2014stg,IceCube:2018cha} and has identified several specific astrophysical neutrino sources \cite{IceCube:2018cha,IceCube:2023ame,IceCube:2022der}.
+IceCube is also expected to be able to detect next galactic supernova  \cite{Kopke_2011}.
+In fact, search for MeV neutrinos from optically obscured galactic supernovae was recently performed \cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm}.
+In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise  within a certain time window and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ s.
+In this work, we demonstrate that such precise time resolution will play a crucial role in testing new physics from supernovae.
+
+ Once produced, the new state can be non-relativistic and travel slowly, causing time delays of the secondary neutrinos.
+However, it is also possible that new states are rather light implying that they may even exit the supernova at earlier times with respect to certain flavors of SM neutrinos.
+Such an early BSM signal, which to the best of our knowledge has not been previously considered, can for instance be induced by light BSM states produced from $\nu_e$ scattering inside the supernova; then subsequently decaying to $\bar{\nu}_e$ which chiefly induces the signal at IceCube.
+This would happen at early stages of supernova, around the neutralization burst, when $\nu_e$ are present and antineutrinos did not get produced yet.
+Such novel timing patterns generically exist in models with new weakly interacting particles, such as the aforementioned Majoron model \cite{Fiorillo:2022cdq} and neutrino magnetic moment portal \cite{Magill:2018jla,Brdar:2020quo}.
+%, but also in scenarios with the mixing portals \cite{Arg_elles_2019,Suliga_2020,Chauhan:2023sci}.
+Via the timing measurement, we will show that neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association to forthcoming galactic supernova event.\\

### 2024-02-21 paper/sections/model.tex
Updates from Overleaf

@@
 \textbf{\textit{The Models}}---
-As an example, we will consider the Majoron model.
-Nevertheless the study can also be applied to sterile neutrinos via magnetic portal, as we discuss in the Supplementary Materials.
+%Nevertheless the study can also be applied to sterile neutrinos via magnetic portal, as we discuss in the Supplementary Materials.
 For the case of sterile neutrino with mixing portal, special care needs to be taken for resonant conversions in which case active neutrinos with plasma mass would travel as slowly as the sterile neutrinos at specific distances.
-The relevant part of the Lagrangian in the Majoron case reads
+Let us consider the Majoron model, studied in \cite{Fiorillo:2022cdq}, where supernova 1987A constraints were derived. The relevant part of the Lagrangian reads
 \begin{align}
@@
 \end{align}
-where $m_\phi$ is the Majoron mass and $g$ parametrizes interaction strength between $\phi$ and neutrinos.
-Consider flavor universal interaction, we abbreviate $g_{\alpha\beta}\equiv g$.
-Majorons are produced from neutrino coalescence in the star and then subsequently decay to a pair of neutrinos with the total decay width to all flavor of neutrinos given by $\Gamma_\phi = 3g^2 m_\phi/16 \pi$, and as a result, BSM neutrino flux is produced.
+where $\phi$ is the (pseudo)scalar, $m_\phi$ is the respective mass and $g$ parametrizes interaction strength between $\phi$ and neutrinos.
+We assume flavor universal interaction and hence $g_{\alpha\beta}\equiv g_\phi \, \delta_{\alpha\beta}$.
+Majorons are produced from (anti)neutrino coalescence in the star and subsequently decay to a pair of (anti)neutrinos resulting in BSM (anti)neutrino flux emitted from the star.
+The total decay width is given by $\Gamma_\phi = 3g^2 m_\phi/16 \pi$.
 
-Using data simulated by the Garching group for an $8.8 M_\odot$ progenitor star \cite{Huedepohl2010}, we obtained the fluxes of standard neutrino case that can be fitted to the parametrization in \cite{baxter2021snewpy} and the fluxes of Majoron $\phi$.
-Requiring the energy loss to Majorons to be less than 10\% of the standard neutrino energy, we can produce the cooling limit, which is in agreement with those obtained in literature \cite{Fiorillo:2022cdq}.
-As mentioned above, for the regions below the coupling strength, Majorons produced will immediately stream out.
-Along its way towards the Earth, Majorons will decay to active neutrinos.
-For a given emission angle $\alpha$ of daughter neutrino relative to the direction of mother particle, and the angle $\theta$ at which the daughter neutrino arrives at the Earth, the time delay $\Delta t$, the arrival time of the daughter $\nu$ relative to that of the neutrinos produced in the explosion via SM processes, is \cite{Jaeckel:2017tud}
+We will set SN bounce time $t_{\rm bounce}$ as $t = 0$.
+Using data from the simulation of $8.8 M_\odot$ progenitor star \cite{Huedepohl2010, Garching} and including effects of neutrino oscillations assuming normal mass ordering, we calculated standard neutrino fluxes at Earth that can be presented in terms of the parametrization with the ``pinching'' factor \cite{Keil:2002in,baxter2021snewpy}.
+Following \cite{Fiorillo:2022cdq}, we also calculated the flux of emitted Majorons.
+At $t \leq \unit[0.05]{s}$, Majorons are mainly produced through
+$\nu_e$ and $\nu_x$ coalescence with $\nu_x$ including (anti)neutrinos of $\tau$ and $\mu$ flavor. 
+After $\unit[0.05]{s}$, the flux of Majorons decreases as the total flux of neutrinos of all flavors. Thus we found that Majoron flux peaks around $t \sim \unit[0.05]{s}$.
+We further cross checked the agreement with \cite{Fiorillo:2022cdq} by reproducing the bound from SN energy loss criteria.
+
+Very weakly coupled Majorons immediately stream out after the production.
+On their way to Earth, Majorons of energy $E_\phi$ will travel at the speed of $\beta$ for a distance of $L_1$, then decay to (anti)neutrinos of energy $E_\nu$ at an emission angle $\cos\alpha = (2 E_\phi E_{\nu} - M^2_N)/(2E_{\nu}E_\phi\beta)$.
+Daughter (anti)neutrino will travel for a distance $L_2$ and reach the Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a SN that is $D_{\rm SN}$ away (see such geometry in \cite{Brdar:2023tmi}).
+The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from SN to reach the Earth is given by
+\cite{Jaeckel:2017tud}
 \begin{align}
-    \Delta t = L_1/\beta + D_{\rm SN} \cos\theta-L_1 \cos\alpha -D_{\rm SN}\,,
+    \delta t = (\frac{L_1}{\beta}-L_1) + (L_1 + L_2 -D_{\rm SN})\,,
+    \label{eq:deltatexa}
+\end{align}
+where we have split the contribution to $\delta t$ into two parts: the first part comes from the slowly moving of Majorons before its decay, and the second part is due to the detour from the line-of-sight path at the given emission angle $\alpha$.
+
+To get the characteristic value of $\delta t$, we can take $L_1 = L_\phi$ with $L_\phi = (E_\phi/m_\phi) \Gamma^{-1}_\phi \beta$ being the decay length of $\phi$.
+As for the parameter regions we considered, $(D_{\rm SN} -D_{\rm SN} \cos\theta) \ll \unit[10^{-3}]{s}$, $\delta t$ can be approximated
+\begin{align}
+    \delta t &\simeq L_\phi(\frac{1}{\beta} -1) + L_\phi(1-\cos\alpha) = \frac{8\pi}{3 E_{\bar{\nu}_{e}}g_\phi^2}\,,
     \label{eq:deltat}
 \end{align}
-with $D_{\rm SN}$ the distance between the SN and the Earth, $L_1$ the distance mother particles propagated before decaying, and $\beta$ being the speed of $\phi$.
-The flux of daughter $\nu$ is obtained by considering decays that only occur at $R^{\nu}_{\rm SN}\leq L_1 \leq L^{\rm max}_1$.
+which is roughly independent of Majoron energy $E_\phi$.
+However, at small values of $E_\phi$, the main contribution to $\delta t$ comes from the first term due to slowing moving Majorons, while at larger values of $E_\phi$, from the second term due to larger detour given the increase of $L_\phi$ over the decrease of $(1-\cos\alpha)$.
+%For neutrinos from light Majoron decay, the characeristic time delay is set by the detour, while for   
+%We have $L_1 \lesssim L_\phi$ with $L_\phi = (E_\phi/m_\phi) \Gamma^{-1}_\phi \beta$ being the decay length of $\phi$.
+%As $L_\phi$ is much smaller than $D_{\rm SN}$ for all values of $E_\phi$ and the parameter regions considered, we can estimate that $(D_{\rm SN} -D_{\rm SN} \cos\theta) \ll \unit[10^{-3}]{s}$.
+Thus we can approximate $\Delta t$ as
+%\begin{align}
+%    \delta t &\simeq L_1/\beta -L_1 \cos\alpha\ \\\notag
+%    &= (L_1/\beta -L_1) + (L_1-L_1 \cos\alpha)\,.
+%    \label{eq:deltat}
+%\end{align}
+%Taking $L_1 \simeq L_\phi$, we have $\Delta t \sim 8\pi/(3 E_e g_\phi^2)$.
+
+We can obtain the flux of daughter $\nu$ by considering decays that occur only at $R^{\nu}_{\rm SN}\leq L_1$.
 As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
-$L^{\rm max}_1$ corresponds to the distance $L_1$ with the largest time delay $\delta t$ \cite{Brdar:2023tmi}.
-
+We will also limit our analysis to a maximal time window of $\unit[100]{s}$ after SN bounce.
+This time window is larger than typical values of time delay considered for the parameter space in consideration.
 \begin{figure}[t!]
@@
     We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
-    In the case of the lower-mass model, the majoron can still travel relativistically, leading to a peak in the spectrum at an earlier time.
-    In the case of the higher-mass model, the majoron travels subliminally, and thus, the flux peaks at later times.
-    Since the dominant interaction is inverse beta decay at these energies, we expect the observed timing distribution to follow the $\bar{\nu}_{e}$
+\yy{the unit for the x-axis should be MeV, for y-axis, we chose to use $\rm s$ for second instead of $\rm sec$.}
     }
@@
 \end{figure}
+We will consider a SN event that happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}.
+As $\bar{\nu}_e$ contribute chiefly to the signals at IceCube via inverse beta decay (IBD), we show in \cref{fig:fluxes} the differential fluxes of daughter $\bar{\nu}_e$ at different time for two benchmark points in the Majoron model, in comparison to the SM $\bar{\nu}_e$ flux.
+We expect the observed signal timing distribution at IceCube to follow these patterns of $\bar{\nu}_{e}$ flux.
 
-For $D_{\rm SN} = \unit[10]{kpc}$ and $\delta t = \unit[100]{s}$ while larger values of $\delta t$ do not affect the limits obtained, we show in \cref{fig:fluxes} the differential fluxes of daughter neutrinos at different time for two benchmarks of the Majoron case, in comparison to the standard neutrino flux.
-We can observe that the energy of neutrinos from Majoron decay extends to $\unit[100]{MeV}$ and above, as expected.
-For heavy Majoron case, the resulting neutrino flux typically is larger at later time, manifesting the time delay from slowly moving Majorons.
-The flux for light Majoron case contain very rich physics.
-Majorons, generating neutrinos with $E_\nu \geq \unit[150]{MeV}$, are nearly-relativistic with its daughter particles moving in parallel.
-In such a case, for couplings comparable to or larger than the one shown in \cref{fig:fluxes}, $\Delta t \sim L_d (1/\beta -1)\lesssim \unit[0.01]{sec}$, with $L_d = E_\phi/m_\phi \Gamma^{-1}_\phi \beta$ being the decay length of $\phi$ for the given $\phi$ energy $E_\phi$.
-The time dependence of neutrino flux thus are mainly inherited from the Majorons upon production, which exhibits in \cref{fig:fluxes} larger fluxes from producing Majorons from the denser and hotter core of SN at earlier time.
-For neutrinos with lower energy, i.e $E_\nu \lesssim \unit[40]{MeV}$, the mother Majorons can be non-relativistic, resulting in $\Delta t \gtrsim \unit[0.04]{sec}$.
-This non-negligible time delay would shift the neutrino flux to later time, lowering the fluxes at earlier time as shown in \cref{fig:fluxes}.
-For the heavy mass benchmark in \cref{fig:fluxes}, we have $\Delta t \gtrsim \unit[10]{sec}$, which would yield the active neutrino flux at sizeable $t$.
+From \cref{fig:fluxes}, we can observe that the energy of $\bar{\nu}_e$ from Majoron decay extends to $\unit[100]{MeV}$ and above for both benchmarks, as expected. 
+Consider the light Majoron case in \cref{fig:fluxes}.
+Majorons, generating neutrinos with $E_{\bar{\nu}_e} \geq \unit[150]{MeV}$, are nearly-relativistic with the emission angle $\alpha$ close to zero.
+The time delay can be estimated from the first term in \cref{eq:deltat} given by $\delta t \sim L_\phi (1/\beta -1)\lesssim \unit[0.01]{s}$.
+With such a negligible time delay, the time dependence of the $\bar{\nu}_e$ flux is mainly inherited from that of the Majorons upon production, with larger fluxes at $t\leq \unit[0.05]{s}$.
+Notice that such $\bar{\nu}_e$ flux would arrive at the detector earlier than the peak of the SM $\bar{\nu}_e$ flux which is around $t\simeq \unit[0.1]{s}$ from \cref{fig:fluxes}, it potentially leads to early signals at IceCube.
+%For $\bar{\nu}_e$ produced with energy, i.e $E_{\bar{\nu}_{e}} \sim \unit[10]{MeV}$, a fraction of their mother Majorons will have energy $E_\phi\sim\mathcal{O}(\unit[10]{MeV})$, resulting in typical $\delta t \gtrsim \unit[0.1]{s}$.
+For higher values of $E_\phi$, the main contribution from detour also leads to $\delta t \gtrsim \unit[0.1]{s}$.
+The time delay for $\bar{\nu}_e$ with energy, i.e $E_{\bar{\nu}_{e}} \sim \unit[10]{MeV}$ is typically $\gtrsim \unit[0.1]{s}$ from \cref{eq:deltat}.
+These $\bar{\nu}_e$ could be produced from Majorons with low energy of $\mathcal{O}(\unit[10]{MeV})$ or high energies.
+For the low energy Majoron case, the time delay is mainly due to slowly moving Majoron, while for high energy case, mainly from the detour.
+Such sizable time delay will shift $\bar{\nu}_e$ peak flux to later time, in comparison to that of their mother Majorons, as exhibited in \cref{fig:fluxes}.
 
+For heavy Majoron case, the resulting $\bar{\nu}_e$ flux is larger at later time, manifesting the time delay from slowly moving Majorons.
+For the heavy Majoron benchmark in \cref{fig:fluxes}, we can estimate that $\delta t \gtrsim \unit[10]{s}$ for $E_{\bar{\nu}_{e}}\sim \unit[200]{MeV}$ which is delayed comparing to the peak of SM $\bar{\nu}_e$ flux.
+Comparing to the light Majoron case, such large time delay is a combination of a more slowly moving Majoron and a larger detour due to its large emission angle.
+As $L_1\lesssim L_\phi$, the time spread of the flux is roughly given by the aforementioned characteristic value of time delay which is $\unit[0.1]{s}$ ($\gtrsim\unit[10]{s}$) for the light (heavy) benchmark case.
+%which yield sizable $\bar{\nu}_e$ flux extending to sizeable $t$.
 %in details in the following, we consider energy deposits at the photomultipliers, 

### 2024-02-21 paper/sections/preamble.tex
Updates from Overleaf

@@
-\preprint{APS/123-QED, USTC-ICTS/PCFT-24-xx}
+\preprint{USTC-ICTS/PCFT-24-07, APS/123-QED}
 \bibliographystyle{apsrev4-1}
@@
 % Supernova Detection with Neutrino Telescopes as a Portal to New Physics
-Supernovae Time Profiles as a Portal to New Physics at Neutrino Telescopes
+Supernovae Time Profiles as a Probe of New Physics at Neutrino Telescopes
 }
@@
 \begin{abstract}
-Neutrino telescopes, such as IceCube, have promised precise time resolutions at the millisecond level for detecting collective rise signals in all photomultiplier.
-We demonstrate that such precise time resolutions will play a crucial role in tracking neutrino signals with novel timing patterns related to weakly interacting massive particles in physics beyond the Standard Model.
-Focusing on a future Supernova explosion in the operation time of IceCube as an example, we show that neutrino telescopes can provide unprecedented probes of new particles with both low and high masses from probing early-glow and after-glow neutrino signals, respectively, while comparable to DUNE and Hyper-K in the intermediate mass region.
+Neutrino telescopes, including IceCube, can detect galactic supernova events by observing the collective rise in photomultiplier count rates with a sub-second time resolution.
+Leveraging precise timing, we demonstrate for the first time the capability of neutrino telescopes to explore new weakly coupled states emitted from supernovae and subsequently decaying to neutrinos.
+Our approach utilizes publicly available packages, \texttt{ASTERIA} and \texttt{SNEWPY}, for simulating detector responses and implementing neutrino fluxes originated from Standard Model and new physics.
+We present results for two new physics models
+employing a specific supernova model and introduce the tool developed for testing a diverse range of new physics models.
 \end{abstract}

### 2024-02-21 paper/sections/conclusion.tex

--- 2024-01-05 paper/sections/conclusion.tex
@@
-\textbf{\textit{Results}}---
+\textbf{\textit{Results and Discussions}}---
 \begin{figure}[t!]
@@
     \includegraphics[width=0.47\textwidth]{figures/majoran_sensitivity}
-    \caption{\textbf{\textit{Exclusion limit for the majoron case.}}
+    \caption{\textbf{\textit{Exclusion sensitivities for the Majoron case.}}
+    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
+    Additionally, we also show the reaches by SN cooling (blue) and by the lack of observation of high-energy neutrinos from SN1987A (grey) \cite{Fiorillo:2022cdq}, with the width of the shading region quantifying uncertainties from SN modeling.
     }
@@
 \end{figure} 
-We present the exclusion limit in \fig{sensitivity}.
+Following our strategies above, we obtain the expected exclusion limit for various BSM if no excess of hits on top of those from background noise and the standard neutrino flux were observed.
+The expected exclusion limit are presented in \cref{fig:sensitivity} for the Majoron case.
+To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
+Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement (blue band), and non-observation of high energy neutrinos from SN 1987A (gray band) are also shown in \cref{fig:sensitivity} for the Majoron case.
+With future SN explosion, IceCube can improve existing limits by one orders of magnitude.
+Moreover, while existing limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.
 
-\textbf{\textit{Outlook}}---
+We also present the estimated reaches of DUNE and Hyper-K in \cref{fig:sensitivity} by looking for time-integrated high energy neutrinos following \cite{Fiorillo:2022cdq, Brdar:2023tmi}.
+We observe that while for the intermediate mass region, the constraints from IceCube are comparable to that from DUNE and Hyper-K, at both low mass region $m_\phi \lesssim \unit[10]{MeV}$ and high mass region $m_\phi \gtrsim \unit[200]{MeV}$, IceCube can provide stronger constraints.
+This is the outcome we expect.
+For light $\phi$ case with negligible time delay, IceCube would observe early signals in a time window separated from that when most of SM flux contribution appears, as we show in the left panel of \cref{fig:hits_and_likelihood}, thus enhancing the reaches.
+On the high mass end, neutrino signals will arrive much later than the SM case, where a time window at late time can be considered to reduce the standard neutrino contaminations.
+
+Uncertainties on the analysis from different modeling SN explosions are minor, as studied in \cite{li2023old} and potential discrepancies between data and modeling are unresolved questions.
+Nevertheless, we point out that the discrepancy could be within $2\sigma$ level which will only change our exclusion limit by a small factor.
+We also provide the code used in this work so that the impact of SN modeling uncertainties on the sensitivity of neutrino telescopes may be evaluated in the future.
+
+In this work, we have demonstrated that neutrino telescope such as IceCube can provide unprecedented probes of new physics, such as Majoron neutrinos and sterile neutrinos with magnetic portal, via measuring Supernova time profiles to a window as short as $\mathcal{O}(0.01)$ s.
+Signatures outside the SM neutrino time window, including both early and delayed signals, can be effectively probed at neutrino telescope.
+This analysis can also be extended to probing new particles such as sterile neutrinos with mixing portal where the resulting time profile requires more dedicated studies as resonant conversions can happen.
+
+\begin{acknowledgments}
+We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching core collapse SN simulations in machine-readable form, and also for stimulating discussions.
+Y.-Y.
+L is supported by the NSF of China through Grant No.
+12305107, 12247103.
+\end{acknowledgments}

### 2024-02-21 paper/sections/supplements.tex

--- 2024-01-18 paper/sections/supplements.tex
@@
     The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
-The shaded regions are excluded by the energy loss constraints, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by   constraints on the energy release from SN explosion following \cite{PhysRevLett.128.221103}.
+The shaded regions are excluded by the energy loss constraints, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from SN explosion \cite{PhysRevLett.128.221103, Chauhan:2023sci, chauhan2024probing}.
+\yy{need to update the cyan shaded region as previously excluded using results in \cite{chauhan2024probing}.}
     }
@@
 We will abbreviate $d_\alpha \equiv d$ given that we assume flavor universal interaction.
-The dominant production channels for $N$ inside the SN are $\nu e^- \to \nu e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies.
+We consider the two production channels for $N$ inside the SN: $\nu e^- \to N e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies.
+We also point out by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside supernove, the limits we obtained are conservative.
 Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}.
-We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$sec, which overlaps with the standard burst time scale.
-We don't expect improvements over DUNE and Hyper-K.
-
-{\color{red} Check the bg for DUNE and Hyper-K is the atmospheric neutrino bg which should also contribute to our analysis? IceCube sees at}
+The limits from IceCube are shown in \cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from SN explosions \cite{PhysRevLett.128.221103,chauhan2024probing}.
+We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and is not expected to improve over DUNE and Hyper-K performance.

### 2024-03-04 main.tex
Updates from Overleaf

\documentclass[aps,twocolumn,prl,showpacs,showkeys,preprintnumbers,superscriptaddress,nobibnotes,floatfix,longbibliography,notitlepage,nofootinbib]{revtex4-2}

\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{comment}
\usepackage{bbold}
\usepackage[shortlabels]{enumitem}
\usepackage{color}
\usepackage{slashed}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{footnote}
\usepackage{lipsum}
\usepackage{multirow}
%\usepackage{longtable}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage{braket}
\usepackage{multirow}
\usepackage{physics}
\usepackage[normalem]{ulem}
\usepackage{url}
\usepackage{units}
\usepackage[normalem]{ulem}
\newcommand{\yy}[1]{\color{red}[YY:#1]\color{black}}
\newcommand{\YY}[1]{\color{red}#1\color{black}}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{lipsum}
\usepackage{lettrine}

\begin{document}

\preprint{USTC-ICTS/PCFT-24-07, APS/123-QED}
\bibliographystyle{apsrev4-1}
\title{
Supernovae Time Profiles as a Probe of New Physics at Neutrino Telescopes
}

\author{Jeff Lazar}
\email{jlazar@icecube.wisc.edu}
\affiliation{Department of Physics \& Laboratory for Particle Physics and Cosmology, Harvard University, Cambridge, MA 02138, USA}
\affiliation{Department of Physics \& Wisconsin IceCube Particle Astrophysics Center, University of Wisconsin-Madison, Madison, WI 53706, USA}
\author{Ying-Ying Li}
\email{yingyingli@ustc.edu.cn}
\affiliation{Peng Huanwu Center for Fundamental Theory, Hefei, Anhui 230026, China}
\affiliation{Interdisciplinary Center for Theoretical Study, University of Science and Technology of China, Hefei, Anhui 230026, China}
\author{Carlos A. Arg\"{u}elles}
\email{carguelles@g.harvard.edu}
\affiliation{Department of Physics \& Laboratory for Particle Physics and Cosmology, Harvard University, Cambridge, MA 02138, USA}
\author{Vedran Brdar}
\email{vedran.brdar@okstate.edu}
\affiliation{Department of Physics, Oklahoma State University, Stillwater, OK, 74078, USA}

%\date{\today}

\begin{abstract}
Neutrino telescopes, including IceCube, can detect galactic supernova events by observing the collective rise in photomultiplier count rates with a subsecond time resolution. 
Leveraging precise timing, we demonstrate for the first time the capability of neutrino telescopes to explore new weakly coupled states emitted from supernovae and subsequently decaying to neutrinos.
Our approach utilizes publicly available packages, \texttt{ASTERIA} and \texttt{SNEWPY}, for simulating detector responses and parametrizing neutrino fluxes originating from Standard Model and new physics. 
We present results for two beyond the Standard Model scenarios and introduce tool developed for testing a diverse range of new physics models.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{\textit{Introduction}}---
The Standard Model (SM) is a remarkable but incomplete theory. 
Puzzles such as the non-vanishing neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, seek explanations beyond the Standard Model (BSM).
There are also no firmly established clues on the energy scale at which the new particles should appear.
To this end, numerous BSM searches across a wide range of scales have been performed, from collider searches at high energies~\cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero~\cite{Baumann:2015rya}.
Core collapse supernovae (CCSNe) release most of their energy in neutrinos, offering unique opportunities to test BSM physics via neutrino interactions.
The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only CCSN observed in neutrinos---have already given tentative constraints on the energies that could be taken away by any light BSM particle copiously produced in the interior of a star.
Indeed, many different BSM scenarios models have been constrained in this way, see \textit{e.g.} Refs.~\cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.

If, additionally, BSM particles emitted from supernovae can decay to neutrinos en route to Earth, even stronger limits can be set, as shown, for instance, in Ref.~\cite{Fiorillo:2022cdq} for Majoron-like bosons and in Ref.~\cite{Brdar:2023tmi} for a realization featuring a neutrino magnetic moment portal.
Specifically, unlike neutrinos inside the supernova core, produced BSM states can stream out without further interactions.
Consequently, they exit with higher energies than neutrinos, typically around $\mathcal{O}(100)$~MeV.
Provided such particles decay to neutrinos, strong constraints can be set from the fact that neutrinos of $\mathcal{O}(100)$~MeV were not recorded from SN 1987A~\cite{Fiorillo:2022cdq, Brdar:2023tmi}.
Such strategies were utilized for neutrino experiments operating during the SN 1987A event. Sensitivity projections for  DUNE~\cite{DUNE:2015lol} and Hyper-Kamiokande~\cite{Hyper-Kamiokande:2018ofw} in light of anticipated galactic supernova event were also performed.

The IceCube Neutrino Observatory has pioneered the detection of neutrinos at $\mathcal{O}$(PeV) energies~\cite{IceCube:2014stg,IceCube:2018cha} and has identified several specific astrophysical neutrino sources~\cite{IceCube:2018cha,IceCube:2023ame,IceCube:2022der}.
IceCube is also expected to be able to detect the next galactic supernova~\cite{Kopke_2011}.
In fact, a search for MeV neutrinos from optically obscured galactic supernovae was recently performed in \cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm}.
In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise  within a certain time window, and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ seconds. 
In this letter, we demonstrate that such precise time resolution will play a crucial role in testing new physics from supernovae.

Once produced in supernovae, the BSM particles can be nonrelativistic and travel slowly, causing time delays for secondary neutrinos. However, it is also possible that new states are rather light, implying that they may even exit the supernova at earlier times with respect to certain flavors of SM neutrinos.
Such an early BSM signal, which to the best of our knowledge has not been previously considered, can, for instance, be induced by light BSM states produced from $\nu_e$ scattering inside the supernova; they would then subsequently decay to $\bar{\nu}_e$, which chiefly induces the signal at IceCube. 
This would happen at early stages of a supernova, around the neutralization burst, when $\nu_e$ are present and antineutrinos have not been produced yet.
Such novel timing patterns generically exist in models with new weakly interacting particles, such as the aforementioned Majoron model~\cite{Fiorillo:2022cdq} and the neutrino magnetic moment portal~\cite{Magill:2018jla,Brdar:2020quo}.
Via the timing measurement, we will show that neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association with forthcoming galactic supernova events.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{\textit{The Model}}---
Let us first consider the Majoron model, studied in Ref.~\cite{Fiorillo:2022cdq}, where supernova 1987A constraints were derived.
The relevant part of the Lagrangian reads
\begin{align}
\mathcal{L} \supset -g_{\alpha\beta} \nu_\alpha \nu_\beta \phi + \text{h.c.} - m_\phi \phi\phi^*\,,
\end{align}
where $\phi$ is the (pseudo)scalar, $m_\phi$ is the respective mass, and $g$ parametrizes interaction strength between $\phi$ and neutrinos. We assume flavor universal interaction and hence $g_{\alpha\beta}\equiv g_\phi \, \delta_{\alpha\beta}$. 
Majorons are produced from (anti)neutrino coalescence in the star and subsequently decay to a pair of (anti)neutrinos resulting in BSM (anti)neutrino flux emitted from the star.
The total decay width is given by $\Gamma_\phi = 3g^2 m_\phi/16 \pi$.

We will set supernova bounce time $t_{\rm bounce}$ as $t = 0$.
Using data from the simulation of $8.8 M_\odot$ progenitor star \cite{Huedepohl2010} and including effects of neutrino oscillations assuming normal mass ordering \cite{Dighe:1999bi}, we calculated standard neutrino fluxes at Earth. Following Ref.~\cite{Fiorillo:2022cdq}, we also calculated the flux of emitted Majorons.
At $t \leq \unit[0.05]{s}$, Majorons are mainly produced through $\nu_e$ and $\nu_x$ coalescence where $\nu_x$ includes (anti)neutrinos of $\tau$ and $\mu$ flavor. After $\unit[0.05]{s}$, the flux of Majorons decreases with the total flux of neutrinos of all flavors. Thus we found that the Majoron flux peaks around $t \sim \unit[0.05]{s}$. We further cross checked the agreement with Ref.~\cite{Fiorillo:2022cdq} by reproducing their bound from supernova energy loss.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/DecayGeometry.pdf}
    \caption{\textbf{The decay geometry for Majorons produced in SN.}}
    \label{fig:geometry}
\end{figure}
Very weakly coupled Majorons immediately stream out after the production.
On their way to Earth, Majorons of energy $E_\phi$ will travel at the speed of $\beta$ for a distance of $L_1$, then decay to (anti)neutrinos of energy $E_\nu$ at an emission angle $\cos\alpha = (2 E_\phi E_{\nu} - m^2_\phi)/(2E_{\nu}E_\phi\beta)$.
Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a supernova that is $D_{\rm SN}$ away (see the decay geometry in \cref{fig:geometry}).
The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a supernova to reach the Earth is given by
\cite{Jaeckel:2017tud}
\begin{align}
    \delta t = \left(\frac{L_1}{\beta}-L_1\right) + (L_1 + L_2 -D_{\rm SN})\,,
    \label{eq:deltatexa}
\end{align}
where we have split the contribution to $\delta t$ into two parts: the first part comes from the slow-moving Majorons before their decay, and the second part is due to the detour from the line-of-sight path at the given emission angle $\alpha$.

To get the characteristic value of $\delta t$, we can take $L_1 = L_\phi$ with $L_\phi = (E_\phi/m_\phi) \Gamma^{-1}_\phi \beta$ being the decay length of $\phi$.
As for the parameter regions we considered, $(D_{\rm SN} -D_{\rm SN} \cos\theta) \ll \unit[10^{-3}]{s}$, $\delta t$ can be approximated as
\begin{align}
    \delta t &\simeq L_\phi(\frac{1}{\beta} -1) + L_\phi(1-\cos\alpha) = \frac{8\pi}{3 E_{\nu}g_\phi^2}\,,
    \label{eq:deltat}
\end{align}
which is roughly independent of Majoron energy $E_\phi$.
%However, at small values of $E_\phi$, the main contribution to $\delta t$ comes from the first term due to the slow-moving Majorons, while at larger values of $E_\phi$, from the second term due to a larger detour given the increase of $L_\phi$ over the decrease of $(1-\cos\alpha)$.

We can obtain the flux of daughter $\nu$ by considering decays that occur only at $L_1\geq R^{\nu}_{\rm SN}$.
As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed is roughly the radius of the core, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
We will also limit our analysis to a maximal time window of $\unit[100]{s}$ after supernova bounce.
This time window is larger than typical values of time delay arising in the model.
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from SM production and two Majoron hypotheses}}.
    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
    }
    \label{fig:fluxes}
\end{figure}
We will consider a supernova event that happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}.
As $\bar{\nu}_e$ contribute chiefly to the signals at IceCube via inverse beta decay (IBD), we show in~\cref{fig:fluxes} the differential fluxes of daughter $\bar{\nu}_e$ at different times for two benchmark points in the Majoron model, in comparison to the SM $\bar{\nu}_e$ flux.
We expect the observed signal timing distribution at IceCube to follow these patterns of $\bar{\nu}_{e}$ flux.

From \cref{fig:fluxes}, we can observe that the energy of $\bar{\nu}_e$ from Majoron decay extends to $\unit[100]{MeV}$ and above for both benchmarks, as expected. 
Consider the light Majoron case in \cref{fig:fluxes}.
Majorons, generating neutrinos with $E_{\bar{\nu}_e} \geq \unit[150]{MeV}$, are nearly relativistic with the emission angle $\alpha$ close to zero.
The time delay can be estimated from the first term in \cref{eq:deltat} given by $\delta t \sim L_\phi (1/\beta -1)\lesssim \unit[0.01]{s}$.
With such a negligible time delay, the time dependence of the $\bar{\nu}_e$ flux is mainly inherited from that of the Majorons upon production, with larger fluxes at $t\leq \unit[0.05]{s}$.
Notice that such a $\bar{\nu}_e$ flux would arrive at the detector earlier than the peak of the SM $\bar{\nu}_e$ flux, which is around $t\simeq \unit[0.1]{s}$ (see \cref{fig:fluxes}), and it potentially leads to early signals at IceCube.
Following \cref{eq:deltat}, the time delay for $\bar{\nu}_e$ with energy $E_{\bar{\nu}_{e}} \sim \unit[10]{MeV}$ is typically $\gtrsim \unit[0.1]{s}$.
These $\bar{\nu}_e$ could be produced from Majorons with low energy of $\mathcal{O}(\unit[10]{MeV})$ or with high energies.
For the low-energy Majoron case, the time delay is mainly due to slow-moving Majorons, while for the high-energy case, it is mainly from the detour.
Such sizable time delays will shift the $\bar{\nu}_e$ peak flux to later times, in comparison to that of their mother Majorons, as exhibited in \cref{fig:fluxes}.

For the heavy Majoron case, the resulting $\bar{\nu}_e$ flux is larger at later times, manifesting the time delay from slowly moving Majorons.
For the heavy Majoron benchmark in \cref{fig:fluxes}, we can estimate that $\delta t \gtrsim \unit[10]{s}$ for $E_{\bar{\nu}_{e}}\sim \unit[200]{MeV}$ which is delayed compared to the peak of the SM $\bar{\nu}_e$ flux.
Compared to the light Majoron case, such a large time delay is a combination of a more slowly moving Majoron and a larger detour due to its large emission angle.

As $L_1\lesssim L_\phi$, the time spread of the flux is roughly given by the aforementioned characteristic value of time delay, which is $\unit[0.1]{s}$ ($\gtrsim\unit[10]{s}$) for the light (heavy) benchmark case.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
    \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
    The hit rate from the SM neutrino flux peaks at around 0.1~s, coinciding with the peak emission of $\bar{\nu}_{e}$ from the SN.
    The shaded regions correspond to the timing windows that give peak sensitivity to the particular model. These are the same benchmarks in the parameter space as in Fig.~\ref{fig:fluxes}.
    In the right panel, we show the test statistic as a function of the starting time and length of the window.
    The relatively broad distribution of high test-statistic values for the heavy Majoron benchmark ($m_\phi=200$ MeV) shows that this analysis technique does not require extremely precise reconstruction of the $t_{\mathrm{bounce}}$.
    }
    \label{fig:hits_and_likelihood}
\end{figure*}

\textbf{\textit{Detector Response and Statistical Treatment}}---The IceCube Neutrino Observatory comprises 5,160 light-detecting digital optical modules (DOMs) buried in a cubic kilometer of the deep, transparent Antarctic ice sheet.
When neutrinos interact within or near the detector, the charged by-products emit photons that the DOMs can detect.
The DOMs are arranged on 86 strings of 60 DOMs each, with an interstring distance of 125~m (70~m for the eight centermost strings).
This enables IceCube to resolve individual neutrinos with energies ranging between a few GeV and a few PeV.
The neutrinos produced by supernovae are far below this threshold and cannot be individually resolved; however, the immense number of neutrinos produced in a supernova increases the single-photon rate of the detector.
This dramatic increase in the rate of photons can be distinguished from the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic CCSNe events~\cite{Griswold:2023iwz}.

New physics will affect the development of a supernova and distort the temporal structure of the photon signal seen in the IceCube detector.
Thus, one may look for excess events in certain time intervals as evidence of this new physics.
In this work, we simulate the light curve produced by a standard supernova with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios mentioned previously; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for light curves of the same two benchmarks from \cref{fig:fluxes}.
Since more than 93\% of the photons detected in IceCube originate in IBD interactions, the SM-only event rate peaks at around 0.1~s.
BSM scenarios, on the other hand, can give rise to an early or delayed signal depending on the particulars of the model.
In essence, Majorons can be generated before the peak of the SM $\bar{\nu}_{e}$ flux, and as light Majorons can travel nearly relativistically, they can escape the supernovae with negligible time delay and then decay to an all-flavor flux of neutrinos, producing early $\bar{\nu}_{e}$ fluxes before the SM one.
The higher-mass Majorons, on the other hand, acquire a time delay from traveling sub-luminally and at a large detour, thus producing a later signal with sizable time delay.
We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different supernova scenarios and the thermal and radioactive noise in the DOMs.
This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, IBD of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$. In addition to photons produced in neutrino interactions, it also simulates photons from thermal noise in the IceCube PMTs and from radioactive decay in the pressure glass housing.
In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY}~\cite{SNEWS:2021ewj} package and, in particular, the \texttt{ParametrizedFlux} object to parametrize the flux with the ``pinching'' factor~\cite{Keil:2002in,SNEWS:2021ewj}.

With the number of hits in the detector from noise, SM-only scenarios, and BSM scenarios as a function of time, we can then quantify the probability of seeing a certain number of hits in a given time window with
\begin{equation}
    -2\Delta\mathrm{LLH} = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right],
    % -2\Delta\mathrm{LLH}(t_{\mathrm{start}}, \Delta t) = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right].
\end{equation}
where $N_{\mathrm{obs.}}$ is the number of photons seen in the detector in the given time and $N_{\mathrm{exp.}}$ is the number of photons expected from a particular BSM hypothesis. For each BSM hypothesis, we then select the time range that maximizes the test statistic and use that maximal test statistic value. The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}, which is around $\unit[0.1]{s}$ ($\unit[10]{s}$) for the light (heavy) benchmark case, consistent with its time spread of the produced $\bar{\nu}_e$ flux.

In the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}, we show the test statistic as a function of the time at which the time range begins, $t_{\mathrm{start}}$, and the duration of the time range, $\Delta t$, for an example BSM hypothesis. The distribution of test-statistic values is not sharply peaked in time, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$ \cite{Halzen_2009}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{\textit{Results and Discussions}}---
\begin{figure}[t!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/majoran_sensitivity}
    \caption{\textbf{\textit{Exclusion sensitivities for the Majoron case.}}
    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
    Additionally, we also show the reaches by supernova cooling (blue) and by the lack of observation of high-energy neutrinos from SN1987A (grey). %\cite{Fiorillo:2022cdq}, with the width of the shading region quantifying uncertainties from supernova modeling.
    }
    \label{fig:sensitivity}
\end{figure} 
Following our strategies above, we obtain the expected exclusion limits for various BSM scenarios for no observed excess of hits on top of background noise and standard neutrino flux.
The expected exclusion limits are presented in \cref{fig:sensitivity} for the Majoron case. To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement (blue band), and non-observation of high-energy supernova neutrinos from SN 1987A (gray band) are also shown in \cref{fig:sensitivity} for the Majoron case. With future supernova explosions, IceCube can improve existing limits by one order of magnitude. 
Moreover, while existing limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide a stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.

We also present the estimated reaches of DUNE and Hyper-Kamiokande in \cref{fig:sensitivity} by looking for time-integrated high-energy neutrinos following Refs.~\cite{Fiorillo:2022cdq, Brdar:2023tmi}.
While the constraints from IceCube for the intermediate mass region are comparable to that from DUNE and Hyper-Kamiokande, we observe that for both low-mass region $m_\phi \lesssim \unit[10]{MeV}$ and high-mass region $m_\phi \gtrsim \unit[200]{MeV}$, IceCube can provide stronger constraints.
This is the outcome we expect.
For light $\phi$ case with negligible time delay, IceCube would observe early signals in a time window separated from that when most of the SM flux contribution appears, as we show in the left panel of \cref{fig:hits_and_likelihood}, thus enhancing the reaches. On the high mass end, neutrino signals will arrive much later than the SM case, where a time window at late time can be considered to reduce the standard neutrino contaminations.

There are existing uncertainties from different modeling of supernova explosions (see e.g. Ref.~\cite{li2023old}) as well as discrepancies between SN 1987A neutrino data and modeling. Nevertheless, we point out that even the uncertainties of around $2\sigma$  will only change our exclusion limits by a small factor.
We make the code used in this work publicly available so that the impact of supernova modeling uncertainties on the sensitivity of neutrino telescopes to BSM scenarios can be further explored.

\textbf{\textit{Summary}}---
In this letter, we have demonstrated that neutrino telescopes such as IceCube can provide unprecedented probes of new physics, such as Majoron-like bosons and neutrino magnetic moment portal, by measuring supernova time profiles to a window as short as $\mathcal{O}(0.01)$ s. Specifically, signatures outside the SM neutrino time window, including both early and delayed signals, can be effectively probed by neutrino telescopes. This analysis can be extended to test other BSM realizations including, but not limited to, sterile neutrinos with a mixing portal. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textit{Acknowledgements}---
We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching CCSNe simulations (available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/}) in machine-readable form, and also for stimulating discussions. Y.-Y. L is supported by the NSF of China through Grant No. 12305107, 12247103.
CAA are supported by the Faculty of Arts and Sciences of Harvard University, the National Science Foundation (NSF), the NSF AI Institute for Artificial Intelligence and Fundamental Interactions (IAIFI), the Research Corporation for Science Advancement, 
and the David \& Lucile Packard Foundation.
CAA and JL were partially supported by the Alfred P. Sloan Foundation for part of this work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{ic_sn_hnl}

\newpage
\onecolumngrid
\appendix

\ifx \standalonesupplemental\undefined
\setcounter{page}{1}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{equation}{0}
\fi

\renewcommand{\thepage}{Supplemental Methods and Tables -- S\arabic{page}}
\renewcommand{\figurename}{SUPPL. FIG.}
\renewcommand{\tablename}{SUPPL. TABLE}

\renewcommand{\theequation}{A\arabic{equation}}

\section{Supplemental Methods and Tables}

\section{Appendix A: Dipole Magnetic Moment Portal}
\begin{figure}[hb!]
    \centering
    \includegraphics[width=0.47\textwidth]{figures/magnetic_moment_sensitivity}
    \caption{\textbf{\textit{Exclusion sensitivities for the magnetic moment case.}}
    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE. The shaded regions are excluded by the energy loss constraints, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from supernova explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.
    }
    \label{fig:magnetic_moment_sensitivity}
\end{figure}
Here we also present results for active-to-sterile neutrino transition magnetic moment described by \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
\begin{align}
    \mathcal{L} \supset \sum_\alpha d_\alpha \bar{N}\sigma_{\mu\nu} \nu^{\alpha} F^{\mu\nu}-\frac{M_N}{2} \bar{N}^c N + \text{h.c.}\,,
    \label{eq:Lag}
\end{align}
where $\nu^{\alpha}$ and $N$ represent active and sterile neutrinos, respectively. Further, $F^{\mu\nu}$ is the field strength tensor of the electromagnetic field, $d_\alpha$ is the dimensionful coefficient of this dimension-5 term and $M_N$ is sterile neutrino mass.  We assume flavor universal interaction $d_\alpha \equiv d$. We consider the two production channels for $N$ inside the SN: $\nu e^- \to N e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies. Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}. The limits from IceCube are shown in \cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from low-energy supernova explosions (SNIIP) \cite{PhysRevLett.128.221103, chauhan2024probing}. We also point out that by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside SN, the limits we obtained are conservative relative to the SNIIP region taken from \cite{chauhan2024probing}. We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over DUNE and Hyper-Kamiokande.

\end{document}

### 2024-03-04 setup.py

@@ -1,53 +1,0 @@
-import io
-import os
-from setuptools import setup, find_packages
-
-NAME = "nutel_BSM"
-DESCRIPTION = (
-    "Code for aiding in calculating neutrino telescope responses to BSM fluxes"
-)
-MAINTAINER = "Jeff Lazar"
-MAINTAINER_EMAIL = "jlazar@icecube.wisc.edu"
-URL = "https://github.com/jlazar17/nutel_vsm"
-LICENSE = "LGPL3"
-
-here = os.path.abspath(os.path.dirname(__file__))
-
-def read(path, encoding="utf-8"):
-    with io.open(path, encoding=encoding) as f:
-        content = f.read()
-    return content
-
-def get_install_requirements(path):
-    content = read(path)
-    requirements = [
-        req for req in content.split("\n") if req != "" and not req.startswith("#")
-    ]
-    return requirements
-
-NSTALL_REQUIRES = get_install_requirements(os.path.join(here, "requirements.txt"))
-
-setup(
-    name=NAME,
-    #version=VERSION,
-    description=DESCRIPTION,
-    #long_description=LONG_DESCRIPTION,
-    #long_description_content_type="text/markdown",
-    url=URL,
-    author=MAINTAINER,
-    author_email=MAINTAINER_EMAIL,
-    license=LICENSE,
-    classifiers=[
-        "Development Status :: 4 - Beta",
-        "Environment :: Console",
-        "Intended Audience :: Science/Research",
-        "Topic :: Scientific/Engineering",
-        "License :: OSI Approved :: GNU Lesser General Public License v3 (LGPLv3)",
-        "License :: OSI Approved :: GNU Lesser General Public License v3 or later (LGPLv3+)",
-        "Programming Language :: Python",
-        "Programming Language :: Python :: 3",
-    ],
-    packages=find_packages(),
-    install_requires=INSTALL_REQUIRES,
-    setup_requires=["setuptools>=34.4.0"],
-)

### 2024-03-04 sne_bsm/__init__.py

@@ -1,2 +1,0 @@
-from .units import units
-from .flux import ParameterizedFlux, parameterized_flux_from_files

### 2024-03-04 sne_bsm/compute_hits.py

@@ -1,17 +1,0 @@
-import numpy as np
-
-from tqdm.notebook import tqdm
-
-import os
-if "ASTERIA" not in os.environ.keys():
-    raise RuntimeError(
-        "'ASTERIA' not in os.environ.keys"
-    )
-os.environ["ASTERIA"] = "/Users/jlazar/research/ASTERIA"
-
-import astropy.units as u
-
-from snewpy.models import ccsn
-from asteria.simulation import Simulation
-
-from ic_sn_hnl import units, ParameterizedFlux

### 2024-03-04 sne_bsm/flux/__init__.py

@@ -1,1 +1,0 @@
-from .parametrize_flux import ParameterizedFlux, parameterized_flux_from_files

### 2024-03-04 sne_bsm/flux/flux.py

@@ -1,26 +1,0 @@
-import numpy as np
-
-from abc import ABC
-
-from ..units import units
-
-class Flux(ABC):
-    """Base class for fluxes"""
-
-    def __init__(self):
-        pass
-
-    def get_flux(self, t: float, enu: float, nutype: int) -> float:
-        """
-        Returns the flux at a certain energy at a certain point
-        in time
-        """
-        pass
-
-    def get_hits(
-        self,
-        tmin=units["second"],
-        tmax=20*units["second"],
-        dt=0.01*units["second"]
-    ) -> np.ndarray:
-        pass

### 2024-03-04 sne_bsm/flux/parametrize_flux.py

@@ -1,583 +1,0 @@
-import numpy as np
-import h5py as h5
-import os
-
-from tqdm import tqdm
-from dataclasses import dataclass
-from scipy.integrate import quad
-from scipy.interpolate import interp1d
-from scipy.special import gamma
-from asteria.simulation import Simulation
-
-from .flux import Flux
-from .sanitize_flux import sanitize_flux
-from ..units import units
-
-from typing import Tuple, List
-
-@dataclass
-class Params:
-    L: float
-    e_exp: float
-    rms: float
-    alpha: float
-
-    def __add__(self, other):
-        if not(isinstance(self, Params) and isinstance(other, Params)):
-            raise ValueError()
-        return Params(
-            self.L + other.L,
-            self.e_exp + other.e_exp,
-            self.rms + other.rms,
-            self.alpha + other.alpha
-        )
-
-    def __sub__(self, other):
-        if not(isinstance(self, Params) and isinstance(other, Params)):
-            raise ValueError()
-        return Params(
-            self.L - other.L,
-            self.e_exp - other.e_exp,
-            self.rms - other.rms,
-            self.alpha - other.alpha
-        )
-
-    def __rmul__(self, other):
-        return Params(
-            other * self.L,
-            other * self.e_exp,
-            other * self.rms,
-            other * self.alpha,
-        )
-
-    def __mul__(self, other):
-        return Params(
-            other * self.L,
-            other * self.e_exp,
-            other * self.rms,
-            other * self.alpha,
-        )
-
-
-def parameterized_flux_from_files(
-    nuefile: str,
-    nuebarfile: str,
-    nuxfile: str,
-    dist: float,
-    thin=1,
-    track=True
-):
-    nuearr = massage_infile(nuefile)
-    nuebararr = massage_infile(nuebarfile)
-    nuxarr = massage_infile(nuxfile)
-    _validate_fluxes(nuearr, nuebararr, nuxarr)
-    params = parameterize(nuearr, nuebararr, nuxarr, thin=thin, track=track)
-    return ParameterizedFlux(params, dist)
- 
-def parameterized_flux_from_h5(
-    group: h5.Group,
-    dist: float,
-    thin: int=1,
-    track: bool=True
-):
-    times = group["times"][::thin]
-    energies = group["energies"][:]
-    fluxes = group["fluxes"][::thin, :, :]
-    params = []
-    itr = enumerate(times)
-    if track:
-        itr = enumerate(tqdm(times))
-    for idx, time in itr:
[…]

### 2024-03-04 sne_bsm/flux/sanitize_flux.py

@@ -1,44 +1,0 @@
-import numpy as np
-
-def find_first_spike(arr: np.ndarray, thresh=1e-10):
-
-    if len(arr)==0:
-        return 0
-    
-    if arr[0]==0 or arr[-1]==0:
-        raise ValueError("Array cannot start with zero")
-    
-    for idx, (v1, v2) in enumerate(zip(arr, arr[1:])):
-        if v2==0:
-            continue
-        if v1 / v2 < thresh:
-            return idx + 1
-    return 0
-
-def argtrim_zeros(arr: np.ndarray):
-    l, r = 0, len(arr)
-    
-    # Catch length 0 arrays
-    if r==0:
-        return l, r
-    
-    while arr[l]==0:
-        l += 1
-        # Catch arrays that are full 0s
-        if l==len(arr):
-            return l, r
-    
-    while arr[r-1]==0:
-        r -= 1
-        
-    return l, r
-
-def sanitize_flux(energies: np.ndarray, flux: np.ndarray):
-    l, r = argtrim_zeros(flux)
-    flux = flux[l:r]
-    energies = energies[l:r]
-
-    idx = find_first_spike(flux)
-    flux = flux[idx:]
-    energies = energies[idx:]
-    return energies, flux

### 2024-03-04 sne_bsm/likelihood.py

@@ -1,31 +1,0 @@
-import numpy as np
-
-from .units import units
-
-TMAX = 25 * units["second"]
-TMIN = 0 * units["second"]
-TMINS = np.linspace(TMIN, TMAX, 1001)
-DTS = np.linspace(0.0, 25, 250) * units["second"]
-
-def find_significance_matrix(sig_hits, sm_hits, bg_hits, times, tmins=None, dts=None):
-    if tmins is None:
-        tmins = TMINS
-    if dts is None:
-        dts = DTS
-    significance = np.full(tmins.shape + dts.shape, np.nan)
-
-    for idx, tmin in enumerate(tmins):
-        for jdx, dt in enumerate(dts):
-            m = np.logical_and(tmin < times, times < tmin+dt)
-            if not m.sum():
-                continue
-            significance[idx, jdx] = likelihood(sig_hits[m], sm_hits[m], bg_hits[m])
-    return significance, tmins, dts
-
-def likelihood(sig_hits, sm_hits, bg_hits):
-    n_obs = (bg_hits + sm_hits).sum()
-    n_exp = (sig_hits + bg_hits + sm_hits).sum()
-    llh = 2 * (n_exp - n_obs)
-    if n_obs > 0:
-        llh += 2 * n_obs * np.log(n_obs / n_exp)
-    return llh

### 2024-03-04 sne_bsm/units.py

@@ -1,33 +1,0 @@
-from collections import namedtuple
-
-_eV = 1.0
-_c = 1.0
-_hbar = 1.0
-_m = 1.0
-
-Units = namedtuple(
-    "Units",
-    "eV c hbar MeV erg GeV second m cm kpc"
-)
-
-class StringUnits(Units):
-    def __init__(self, *args, **kwargs):
-        super().__init__()
-        
-    def __getitem__(self, key):
-        if isinstance(key, str):
-            return getattr(self, key)
-        return super().__getitem__(key)
-
-units = StringUnits(
-    eV = _eV,
-    c = _c,
-    hbar = _hbar,
-    m = _m,
-    MeV = 1e6 * _eV,
-    erg = 624_151.0 * 1e6 * _eV,
-    GeV = 1e9 * _eV,
-    second = _hbar / (6.582119569e-16 * _eV),
-    cm = 0.01 * _m,
-    kpc = 3.086e19 * _m
-)

### 2024-03-04 sne_bsm/__init__.py
Rescue

@@ -1,0 +1,2 @@
+from .units import units
+from .flux import ParameterizedFlux, parameterized_flux_from_h5, deserialize

### 2024-03-04 sne_bsm/flux/__init__.py

@@ -1,0 +1,1 @@
+from .parametrize_flux import ParameterizedFlux, parameterized_flux_from_h5, deserialize

### 2024-03-04 sne_bsm/flux/parametrize_flux.py

@@ -1,0 +1,583 @@
+import numpy as np
+import h5py as h5
+import os
+
+from tqdm import tqdm
+from dataclasses import dataclass
+from scipy.integrate import quad
+from scipy.interpolate import interp1d
+from scipy.special import gamma
+from asteria.simulation import Simulation
+
+from .flux import Flux
+from .sanitize_flux import sanitize_flux
+from ..units import units
+
+from typing import Tuple, List
+
+@dataclass
+class Params:
+    L: float
+    e_exp: float
+    rms: float
+    alpha: float
+
+    def __add__(self, other):
+        if not(isinstance(self, Params) and isinstance(other, Params)):
+            raise ValueError()
+        return Params(
+            self.L + other.L,
+            self.e_exp + other.e_exp,
+            self.rms + other.rms,
+            self.alpha + other.alpha
+        )
+
+    def __sub__(self, other):
+        if not(isinstance(self, Params) and isinstance(other, Params)):
+            raise ValueError()
+        return Params(
+            self.L - other.L,
+            self.e_exp - other.e_exp,
+            self.rms - other.rms,
+            self.alpha - other.alpha
+        )
+
+    def __rmul__(self, other):
+        return Params(
+            other * self.L,
+            other * self.e_exp,
+            other * self.rms,
+            other * self.alpha,
+        )
+
+    def __mul__(self, other):
+        return Params(
+            other * self.L,
+            other * self.e_exp,
+            other * self.rms,
+            other * self.alpha,
+        )
+
+
+def parameterized_flux_from_files(
+    nuefile: str,
+    nuebarfile: str,
+    nuxfile: str,
+    dist: float,
+    thin=1,
+    track=True
+):
+    nuearr = massage_infile(nuefile)
+    nuebararr = massage_infile(nuebarfile)
+    nuxarr = massage_infile(nuxfile)
+    _validate_fluxes(nuearr, nuebararr, nuxarr)
+    params = parameterize(nuearr, nuebararr, nuxarr, thin=thin, track=track)
+    return ParameterizedFlux(params, dist)
+ 
+def parameterized_flux_from_h5(
+    group: h5.Group,
+    dist: float,
+    thin: int=1,
+    track: bool=True
+):
+    times = group["times"][::thin]
+    energies = group["energies"][:]
+    fluxes = group["fluxes"][::thin, :, :]
+    params = []
+    itr = enumerate(times)
+    if track:
+        itr = enumerate(tqdm(times))
+    for idx, time in itr:
[…]

### 2024-03-04 sne_bsm/likelihood.py

@@ -1,0 +1,31 @@
+import numpy as np
+
+from .units import units
+
+TMAX = 25 * units["second"]
+TMIN = 0 * units["second"]
+TMINS = np.linspace(TMIN, TMAX, 1001)
+DTS = np.linspace(0.0, 25, 250) * units["second"]
+
+def find_significance_matrix(sig_hits, sm_hits, bg_hits, times, tmins=None, dts=None):
+    if tmins is None:
+        tmins = TMINS
+    if dts is None:
+        dts = DTS
+    significance = np.full(tmins.shape + dts.shape, np.nan)
+
+    for idx, tmin in enumerate(tmins):
+        for jdx, dt in enumerate(dts):
+            m = np.logical_and(tmin < times, times < tmin+dt)
+            if not m.sum():
+                continue
+            significance[idx, jdx] = likelihood(sig_hits[m], sm_hits[m], bg_hits[m])
+    return significance, tmins, dts
+
+def likelihood(sig_hits, sm_hits, bg_hits):
+    n_obs = (bg_hits + sm_hits).sum()
+    n_exp = (sig_hits + bg_hits + sm_hits).sum()
+    llh = 2 * (n_exp - n_obs)
+    if n_obs > 0:
+        llh += 2 * n_obs * np.log(n_obs / n_exp)
+    return llh

### 2024-03-04 sne_bsm/units.py

@@ -1,0 +1,33 @@
+from collections import namedtuple
+
+_eV = 1.0
+_c = 1.0
+_hbar = 1.0
+_m = 1.0
+
+Units = namedtuple(
+    "Units",
+    "eV c hbar MeV erg GeV second m cm kpc"
+)
+
+class StringUnits(Units):
+    def __init__(self, *args, **kwargs):
+        super().__init__()
+        
+    def __getitem__(self, key):
+        if isinstance(key, str):
+            return getattr(self, key)
+        return super().__getitem__(key)
+
+units = StringUnits(
+    eV = _eV,
+    c = _c,
+    hbar = _hbar,
+    m = _m,
+    MeV = 1e6 * _eV,
+    erg = 624_151.0 * 1e6 * _eV,
+    GeV = 1e9 * _eV,
+    second = _hbar / (6.582119569e-16 * _eV),
+    cm = 0.01 * _m,
+    kpc = 3.086e19 * _m
+)

### 2024-03-06 paper/main.tex
Updates from Overleaf

@@
 \usepackage{braket}
-\usepackage[compat=1.1.0]{tikz-feynman}
 \usepackage{multirow}
 \usepackage{physics}
-\usepackage{feynmp-auto}
 \usepackage[normalem]{ulem}
@@
 \newcommand{\yy}[1]{\color{red}[YY:#1]\color{black}}
+\newcommand{\YY}[1]{\color{red}#1\color{black}}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+\usepackage{lipsum}
+\usepackage{lettrine}
 
-\input{sections/packages}
 \begin{document}
 
-\input{paper/sections/preamble}
-\input{paper/sections/introduction}
-\input{paper/sections/model}
-\input{paper/sections/detector_response}
-\input{paper/sections/stats}
-\input{paper/`sections/conclusion}
+\preprint{USTC-ICTS/PCFT-24-07, APS/123-QED}
+\bibliographystyle{apsrev4-1}
+\title{
+Supernovae Time Profiles as a Probe of New Physics at Neutrino Telescopes
+}
+
+\author{Jeff Lazar}
+\email{jlazar@icecube.wisc.edu}
+\affiliation{Department of Physics \& Laboratory for Particle Physics and Cosmology, Harvard University, Cambridge, MA 02138, USA}
+\affiliation{Department of Physics \& Wisconsin IceCube Particle Astrophysics Center, University of Wisconsin-Madison, Madison, WI 53706, USA}
+\author{Ying-Ying Li}
+\email{yingyingli@ustc.edu.cn}
+\affiliation{Peng Huanwu Center for Fundamental Theory, Hefei, Anhui 230026, China}
+\affiliation{Interdisciplinary Center for Theoretical Study, University of Science and Technology of China, Hefei, Anhui 230026, China}
+\author{Carlos A. Arg\"{u}elles}
+\email{carguelles@g.harvard.edu}
+\affiliation{Department of Physics \& Laboratory for Particle Physics and Cosmology, Harvard University, Cambridge, MA 02138, USA}
+\author{Vedran Brdar}
+\email{vedran.brdar@okstate.edu}
+\affiliation{Department of Physics, Oklahoma State University, Stillwater, OK, 74078, USA}
+
+%\date{\today}
+
+\begin{abstract}
+Neutrino telescopes, including IceCube, can detect galactic supernova events by observing the collective rise in photomultiplier count rates with a subsecond time resolution. 
+Leveraging precise timing, we demonstrate for the first time the capability of neutrino telescopes to explore new weakly coupled states emitted from supernovae and subsequently decaying to neutrinos.
+Our approach utilizes publicly available packages, \texttt{ASTERIA} and \texttt{SNEWPY}, for simulating detector responses and parametrizing neutrino fluxes originating from Standard Model and new physics.
+We present results for two beyond the Standard Model scenarios and introduce tool developed for testing a diverse range of new physics models.
+\end{abstract}
+
+\maketitle
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textbf{\textit{Introduction}}---
+The Standard Model (SM) is a remarkable but incomplete theory. 
+Puzzles such as the non-vanishing neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, seek explanations beyond the Standard Model (BSM).
+There are also no firmly established clues on the energy scale at which the new particles should appear.
+To this end, numerous BSM searches across a wide range of scales have been performed, from collider searches at high energies~\cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero~\cite{Baumann:2015rya}.
+Core collapse supernovae (CCSNe) release most of their energy in neutrinos, offering unique opportunities to test BSM physics via neutrino interactions.
+The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only CCSN observed in neutrinos---have already given tentative constraints on the energies that could be taken away by any light BSM particle copiously produced in the interior of a star.
+Indeed, many different BSM scenarios models have been constrained in this way, see \textit{e.g.} Refs.~\cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.
+
+If, additionally, BSM particles emitted from supernovae can decay to neutrinos en route to Earth, even stronger limits can be set, as shown, for instance, in Ref.~\cite{Fiorillo:2022cdq} for Majoron-like bosons and in Ref.~\cite{Brdar:2023tmi} for a realization featuring a neutrino magnetic moment portal.
+Specifically, unlike neutrinos inside the supernova core, produced BSM states can stream out without further interactions.
+Consequently, they exit with higher energies than neutrinos, typically around $\mathcal{O}(100)$~MeV.
+Provided such particles decay to neutrinos, strong constraints can be set from the fact that neutrinos of $\mathcal{O}(100)$~MeV were not recorded from SN 1987A~\cite{Fiorillo:2022cdq, Brdar:2023tmi}.
+Such strategies were utilized for neutrino experiments operating during the SN 1987A event.
+Sensitivity projections for  DUNE~\cite{DUNE:2015lol} and Hyper-Kamiokande~\cite{Hyper-Kamiokande:2018ofw} in light of anticipated galactic supernova event were also performed.
+
+The IceCube Neutrino Observatory has pioneered the detection of neutrinos at $\mathcal{O}$(PeV) energies~\cite{IceCube:2014stg,IceCube:2018cha} and has identified several specific astrophysical neutrino sources~\cite{IceCube:2018cha,IceCube:2023ame,IceCube:2022der}.
+IceCube is also expected to be able to detect the next galactic supernova~\cite{Kopke_2011}.
+In fact, a search for MeV neutrinos from optically obscured galactic supernovae was recently performed in \cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm}.
+In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise  within a certain time window, and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ seconds.
+In this letter, we demonstrate that such precise time resolution will play a crucial role in testing new physics from supernovae.
+
+Once produced in supernovae, the BSM particles can be nonrelativistic and travel slowly, causing time delays for secondary neutrinos.
+However, it is also possible that new states are rather light, implying that they may even exit the supernova at earlier times with respect to certain flavors of SM neutrinos.
+Such an early BSM signal, which to the best of our knowledge has not been previously considered, can, for instance, be induced by light BSM states produced from $\nu_e$ scattering inside the supernova; they would then subsequently decay to $\bar{\nu}_e$, which chiefly induces the signal at IceCube.
+This would happen at early stages of a supernova, around the neutralization burst, when $\nu_e$ are present and antineutrinos have not been produced yet.
+Such novel timing patterns generically exist in models with new weakly interacting particles, such as the aforementioned Majoron model~\cite{Fiorillo:2022cdq} and the neutrino magnetic moment portal~\cite{Magill:2018jla,Brdar:2020quo}.
+Via the timing measurement, we will show that neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association with forthcoming galactic supernova events.\\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textbf{\textit{The Model}}---
+Let us first consider the Majoron model, studied in Ref.~\cite{Fiorillo:2022cdq}, where supernova 1987A constraints were derived.
+The relevant part of the Lagrangian reads
+\begin{align}
+\mathcal{L} \supset -g_{\alpha\beta} \nu_\alpha \nu_\beta \phi + \text{h.c.} - m_\phi \phi\phi^*\,,
+\end{align}
+where $\phi$ is the (pseudo)scalar, $m_\phi$ is the respective mass, and $g$ parametrizes interaction strength between $\phi$ and neutrinos.
+We assume flavor universal interaction and hence $g_{\alpha\beta}\equiv g_\phi \, \delta_{\alpha\beta}$.
+Majorons are produced from (anti)neutrino coalescence in the star and subsequently decay to a pair of (anti)neutrinos resulting in BSM (anti)neutrino flux emitted from the star.
+The total decay width is given by $\Gamma_\phi = 3g^2 m_\phi/16 \pi$.
+
+We will set supernova bounce time $t_{\rm bounce}$ as $t = 0$.
+Using data from the simulation of $8.8 M_\odot$ progenitor star \cite{Huedepohl2010} and including effects of neutrino oscillations assuming normal mass ordering \cite{Dighe:1999bi}, we calculated standard neutrino fluxes at Earth.
+Following Ref.~\cite{Fiorillo:2022cdq}, we also calculated the flux of emitted Majorons.
+At $t \leq \unit[0.05]{s}$, Majorons are mainly produced through $\nu_e$ and $\nu_x$ coalescence where $\nu_x$ includes (anti)neutrinos of $\tau$ and $\mu$ flavor.
+After $\unit[0.05]{s}$, the flux of Majorons decreases with the total flux of neutrinos of all flavors.
+Thus we found that the Majoron flux peaks around $t \sim \unit[0.05]{s}$.
+We further cross checked the agreement with Ref.~\cite{Fiorillo:2022cdq} by reproducing their bound from supernova energy loss.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.47\textwidth]{figures/DecayGeometry.pdf}
+    \caption{\textbf{The decay geometry for Majorons produced in SN.}}
+    \label{fig:geometry}
+\end{figure}
+Very weakly coupled Majorons immediately stream out after the production.
+On their way to Earth, Majorons of energy $E_\phi$ will travel at the speed of $\beta$ for a distance of $L_1$, then decay to (anti)neutrinos of energy $E_\nu$ at an emission angle $\cos\alpha = (2 E_\phi E_{\nu} - m^2_\phi)/(2E_{\nu}E_\phi\beta)$.
+Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a supernova that is $D_{\rm SN}$ away (see the decay geometry in \cref{fig:geometry}).
+The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a supernova to reach the Earth is given by
+\cite{Jaeckel:2017tud}
+\begin{align}
+    \delta t = \left(\frac{L_1}{\beta}-L_1\right) + (L_1 + L_2 -D_{\rm SN})\,,
+    \label{eq:deltatexa}
+\end{align}
+where we have split the contribution to $\delta t$ into two parts: the first part comes from the slow-moving Majorons before their decay, and the second part is due to the detour from the line-of-sight path at the given emission angle $\alpha$.
+
+To get the characteristic value of $\delta t$, we can take $L_1 = L_\phi$ with $L_\phi = (E_\phi/m_\phi) \Gamma^{-1}_\phi \beta$ being the decay length of $\phi$.
+As for the parameter regions we considered, $(D_{\rm SN} -D_{\rm SN} \cos\theta) \ll \unit[10^{-3}]{s}$, $\delta t$ can be approximated as
+\begin{align}
+    \delta t &\simeq L_\phi\left(\frac{1}{\beta} -1\right) + L_\phi(1-\cos\alpha) = \frac{8\pi}{3 E_{\nu}g_\phi^2}\,,
+    \label{eq:deltat}
+\end{align}
+which is roughly independent of Majoron energy $E_\phi$.
+%However, at small values of $E_\phi$, the main contribution to $\delta t$ comes from the first term due to the slow-moving Majorons, while at larger values of $E_\phi$, from the second term due to a larger detour given the increase of $L_\phi$ over the decrease of $(1-\cos\alpha)$.
+
+We can obtain the flux of daughter $\nu$ by considering decays that occur only at $L_1\geq R^{\nu}_{\rm SN}$.
+As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed is roughly the radius of the core, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
+We will also limit our analysis to a maximal time window of $\unit[100]{s}$ after supernova bounce.
+This time window is larger than typical values of time delay arising in the model.
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
+    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from SM production and two Majoron hypotheses}}.
+    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
+    }
+    \label{fig:fluxes}
+\end{figure}
+We will consider a supernova event that happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}.
+As $\bar{\nu}_e$ contribute chiefly to the signals at IceCube via inverse beta decay (IBD), we show in~\cref{fig:fluxes} the differential fluxes of daughter $\bar{\nu}_e$ at different times for two benchmark points in the Majoron model, in comparison to the SM $\bar{\nu}_e$ flux.
+We expect the observed signal timing distribution at IceCube to follow these patterns of $\bar{\nu}_{e}$ flux.
+
+From \cref{fig:fluxes}, we can observe that the energy of $\bar{\nu}_e$ from Majoron decay extends to $\unit[100]{MeV}$ and above for both benchmarks, as expected. 
+Consider the light Majoron case in \cref{fig:fluxes}.
+Majorons, generating neutrinos with $E_{\bar{\nu}_e} \geq \unit[150]{MeV}$, are nearly relativistic with the emission angle $\alpha$ close to zero.
+The time delay can be estimated from the first term in \cref{eq:deltat} given by $\delta t \sim L_\phi (1/\beta -1)\lesssim \unit[0.01]{s}$.
+With such a negligible time delay, the time dependence of the $\bar{\nu}_e$ flux is mainly inherited from that of the Majorons upon production, with larger fluxes at $t\leq \unit[0.05]{s}$.
+Notice that such a $\bar{\nu}_e$ flux would arrive at the detector earlier than the peak of the SM $\bar{\nu}_e$ flux, which is around $t\simeq \unit[0.1]{s}$ (see \cref{fig:fluxes}), and it potentially leads to early signals at IceCube.
+Following \cref{eq:deltat}, the time delay for $\bar{\nu}_e$ with energy $E_{\bar{\nu}_{e}} \sim \unit[10]{MeV}$ is typically $\gtrsim \unit[0.1]{s}$.
+These $\bar{\nu}_e$ could be produced from Majorons with low energy of $\mathcal{O}(\unit[10]{MeV})$ or with high energies.
+For the low-energy Majoron case, the time delay is mainly due to slow-moving Majorons, while for the high-energy case, it is mainly from the detour.
+Such sizable time delays will shift the $\bar{\nu}_e$ peak flux to later times, in comparison to that of their mother Majorons, as exhibited in \cref{fig:fluxes}.
+
+For the heavy Majoron case, the resulting $\bar{\nu}_e$ flux is larger at later times, manifesting the time delay from slowly moving Majorons.
+For the heavy Majoron benchmark in \cref{fig:fluxes}, we can estimate that $\delta t \gtrsim \unit[10]{s}$ for $E_{\bar{\nu}_{e}}\sim \unit[200]{MeV}$ which is delayed compared to the peak of the SM $\bar{\nu}_e$ flux.
+Compared to the light Majoron case, such a large time delay is a combination of a more slowly moving Majoron and a larger detour due to its large emission angle.
+
+As $L_1\lesssim L_\phi$, the time spread of the flux is roughly given by the aforementioned characteristic value of time delay, which is $\unit[0.1]{s}$ ($\gtrsim\unit[10]{s}$) for the light (heavy) benchmark case.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
+    \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
+    The hit rate from the SM neutrino flux peaks at around 0.1~s, coinciding with the peak emission of $\bar{\nu}_{e}$ from the SN.
+    The shaded regions correspond to the timing windows that give peak sensitivity to the particular model. These are the same benchmarks in the parameter space as in Fig.~\ref{fig:fluxes}.
+    In the right panel, we show the test statistic as a function of the starting time and length of the window.
+    The relatively broad distribution of high test-statistic values for the heavy Majoron benchmark ($m_\phi=200$ MeV) shows that this analysis technique does not require extremely precise reconstruction of the $t_{\mathrm{bounce}}$.
+    }
+    \label{fig:hits_and_likelihood}
+\end{figure*}
+
+\textbf{\textit{Detector Response and Statistical Treatment}}---The IceCube Neutrino Observatory comprises 5,160 light-detecting digital optical modules (DOMs) buried in a cubic kilometer of the deep, transparent Antarctic ice sheet.
+When neutrinos interact within or near the detector, the charged by-products emit photons that the DOMs can detect.
+The DOMs are arranged on 86 strings of 60 DOMs each, with an interstring distance of 125~m (70~m for the eight centermost strings).
+This enables IceCube to resolve individual neutrinos with energies ranging between a few GeV and a few PeV.
+The neutrinos produced by supernovae are far below this threshold and cannot be individually resolved; however, the immense number of neutrinos produced in a supernova increases the single-photon rate of the detector.
+This dramatic increase in the rate of photons can be distinguished from the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic CCSNe events~\cite{Griswold:2023iwz}.
+
+New physics will affect the development of a supernova and distort the temporal structure of the photon signal seen in the IceCube detector.
+Thus, one may look for excess events in certain time intervals as evidence of this new physics.
+In this work, we simulate the light curve produced by a standard supernova with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios mentioned previously; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for light curves of the same two benchmarks from \cref{fig:fluxes}.
+Since more than 93\% of the photons detected in IceCube originate in IBD interactions, the SM-only event rate peaks at around 0.1~s.
+BSM scenarios, on the other hand, can give rise to an early or delayed signal depending on the particulars of the model.
+In essence, Majorons can be generated before the peak of the SM $\bar{\nu}_{e}$ flux, and as light Majorons can travel nearly relativistically, they can escape the supernovae with negligible time delay and then decay to an all-flavor flux of neutrinos, producing early $\bar{\nu}_{e}$ fluxes before the SM one.
+The higher-mass Majorons, on the other hand, acquire a time delay from traveling sub-luminally and at a large detour, thus producing a later signal with sizable time delay.
+We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different supernova scenarios and the thermal and radioactive noise in the DOMs.
+This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, IBD of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$.
+In addition to photons produced in neutrino interactions, it also simulates photons from thermal noise in the IceCube PMTs and from radioactive decay in the pressure glass housing.
+In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY}~\cite{SNEWS:2021ewj} package and, in particular, the \texttt{ParametrizedFlux} object to parametrize the flux with the ``pinching'' factor~\cite{Keil:2002in,SNEWS:2021ewj}.
+
+With the number of hits in the detector from noise, SM-only scenarios, and BSM scenarios as a function of time, we can then quantify the probability of seeing a certain number of hits in a given time window with
+\begin{equation}
+    -2\Delta\mathrm{LLH} = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right],
+    % -2\Delta\mathrm{LLH}(t_{\mathrm{start}}, \Delta t) = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right].
+\end{equation}
+where $N_{\mathrm{obs.}}$ is the number of photons seen in the detector in the given time and $N_{\mathrm{exp.}}$ is the number of photons expected from a particular BSM hypothesis.
+For each BSM hypothesis, we then select the time range that maximizes the test statistic and use that maximal test statistic value.
+The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}, which is around $\unit[0.1]{s}$ ($\unit[10]{s}$) for the light (heavy) benchmark case, consistent with its time spread of the produced $\bar{\nu}_e$ flux.
+
+In the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}, we show the test statistic as a function of the time at which the time range begins, $t_{\mathrm{start}}$, and the duration of the time range, $\Delta t$, for an example BSM hypothesis.
+The distribution of test-statistic values is not sharply peaked in time, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$ \cite{Halzen_2009}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textbf{\textit{Results and Discussions}}---
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.47\textwidth]{figures/majoran_sensitivity}
+    \caption{\textbf{\textit{Exclusion sensitivities for the Majoron case.}}
+    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
+    Additionally, we also show the reaches by supernova cooling (blue) and by the lack of observation of high-energy neutrinos from SN1987A (grey).
+%\cite{Fiorillo:2022cdq}, with the width of the shading region quantifying uncertainties from supernova modeling.
+    }
+    \label{fig:sensitivity}
+\end{figure} 
+Following our strategies above, we obtain the expected exclusion limits for various BSM scenarios for no observed excess of hits on top of background noise and standard neutrino flux.
+The expected exclusion limits are presented in \cref{fig:sensitivity} for the Majoron case.
+To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
+Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement (blue band), and non-observation of high-energy supernova neutrinos from SN 1987A (gray band) are also shown in \cref{fig:sensitivity} for the Majoron case.
+With future supernova explosions, IceCube can improve existing limits by one order of magnitude.
+Moreover, while existing limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide a stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.
+
+We also present the estimated reaches of DUNE and Hyper-Kamiokande in \cref{fig:sensitivity} by looking for time-integrated high-energy neutrinos following Refs.~\cite{Fiorillo:2022cdq, Brdar:2023tmi}.
+While the constraints from IceCube for the intermediate mass region are comparable to that from DUNE and Hyper-Kamiokande, we observe that for both low-mass region $m_\phi \lesssim \unit[10]{MeV}$ and high-mass region $m_\phi \gtrsim \unit[200]{MeV}$, IceCube can provide stronger constraints.
+This is the outcome we expect.
+For light $\phi$ case with negligible time delay, IceCube would observe early signals in a time window separated from that when most of the SM flux contribution appears, as we show in the left panel of \cref{fig:hits_and_likelihood}, thus enhancing the reaches.
+On the high mass end, neutrino signals will arrive much later than the SM case, where a time window at late time can be considered to reduce the standard neutrino contaminations.
+
+There are existing uncertainties from different modeling of supernova explosions (see e.g.
+Ref.~\cite{li2023old}) as well as discrepancies between SN 1987A neutrino data and modeling.
+Nevertheless, we point out that even the uncertainties of around $2\sigma$  will only change our exclusion limits by a small factor.
+We make the code used in this work publicly available so that the impact of supernova modeling uncertainties on the sensitivity of neutrino telescopes to BSM scenarios can be further explored.
+
+\textbf{\textit{Summary}}---
+In this letter, we have demonstrated that neutrino telescopes such as IceCube can provide unprecedented probes of new physics, such as Majoron-like bosons and neutrino magnetic moment portal, by measuring supernova time profiles to a window as short as $\mathcal{O}(0.01)$ s.
+Specifically, signatures outside the SM neutrino time window, including both early and delayed signals, can be effectively probed by neutrino telescopes.
+This analysis can be extended to test other BSM realizations including, but not limited to, sterile neutrinos with a mixing portal.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\textit{Acknowledgements}---
+We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching CCSNe simulations (available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/}) in machine-readable form, and also for stimulating discussions.
+Y.-Y.
+L is supported by the NSF of China through Grant No.
+12305107, 12247103.
+CAA are supported by the Faculty of Arts and Sciences of Harvard University, the National Science Foundation (NSF), the NSF AI Institute for Artificial Intelligence and Fundamental Interactions (IAIFI), the Research Corporation for Science Advancement,
+and the David \& Lucile Packard Foundation.
+CAA and JL were partially supported by the Alfred P. Sloan Foundation for part of this work.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\newpage
+\onecolumngrid
+\appendix
+
+\ifx \standalonesupplemental\undefined
+\setcounter{page}{1}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+\setcounter{equation}{0}
+\fi
+
+\renewcommand{\thepage}{Supplemental Methods and Tables -- S\arabic{page}}
+\renewcommand{\figurename}{SUPPL. FIG.}
+\renewcommand{\tablename}{SUPPL. TABLE}
+
+\renewcommand{\theequation}{A\arabic{equation}}
+
+\section{Supplemental Methods and Tables}
+
+\section{Appendix A: Dipole Magnetic Moment Portal}
+\begin{figure}[hb!]
+    \centering
+    \includegraphics[width=0.47\textwidth]{figures/magnetic_moment_sensitivity}
+    \caption{\textbf{\textit{Exclusion sensitivities for the magnetic moment case.}}
+    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
+The shaded regions are excluded by the energy loss constraints, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from supernova explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.
+    }
+    \label{fig:magnetic_moment_sensitivity}
+\end{figure}
+Here we also present results for active-to-sterile neutrino transition magnetic moment described by \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
+\begin{align}
+    \mathcal{L} \supset \sum_\alpha d_\alpha \bar{N}\sigma_{\mu\nu} \nu^{\alpha} F^{\mu\nu}-\frac{M_N}{2} \bar{N}^c N + \text{h.c.}\,,
+    \label{eq:Lag}
+\end{align}
+where $\nu^{\alpha}$ and $N$ represent active and sterile neutrinos, respectively.
+Further, $F^{\mu\nu}$ is the field strength tensor of the electromagnetic field, $d_\alpha$ is the dimensionful coefficient of this dimension-5 term and $M_N$ is sterile neutrino mass.
+We assume flavor universal interaction $d_\alpha \equiv d$.
+We consider the two production channels for $N$ inside the SN: $\nu e^- \to N e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies.
+Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}.
+The limits from IceCube are shown in \cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from low-energy supernova explosions (SNIIP) \cite{PhysRevLett.128.221103, chauhan2024probing}.
+We also point out that by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside SN, the limits we obtained are conservative relative to the SNIIP region taken from \cite{chauhan2024probing}.
+We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over DUNE and Hyper-Kamiokande.
+
 \end{document}
-
-% Outline
-- Introduction: 
-- Detector response
-  - What kind of noise, Standard neutrino
-  - Atm. background reduction ?
-- SNEWPY treatment for general models the pipeline etc.
-  - The two models that we have condsidered Lagrangians
-  - fluxes and results for them
-- Conclusion
-  - IC is useful for SN
-  - Use our software

### 2024-03-07 paper/main.tex

@@
 The Standard Model (SM) is a remarkable but incomplete theory. 
-Puzzles such as the non-vanishing neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, seek explanations beyond the Standard Model (BSM).
+Puzzles such as the non-vanishing neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, seek explanations beyond the SM (BSM).
 There are also no firmly established clues on the energy scale at which the new particles should appear.
 To this end, numerous BSM searches across a wide range of scales have been performed, from collider searches at high energies~\cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero~\cite{Baumann:2015rya}.
-Core collapse supernovae (CCSNe) release most of their energy in neutrinos, offering unique opportunities to test BSM physics via neutrino interactions.
-The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only CCSN observed in neutrinos---have already given tentative constraints on the energies that could be taken away by any light BSM particle copiously produced in the interior of a star.
+Supernovae release most of their energy in neutrinos, offering unique opportunities to test BSM physics via neutrino interactions.
+The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only supernova observed in neutrinos---have already given tentative constraints on the energies that could be taken away by any light BSM particle copiously produced in the interior of a star.
 Indeed, many different BSM scenarios models have been constrained in this way, see \textit{e.g.} Refs.~\cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.
@@
 Sensitivity projections for  DUNE~\cite{DUNE:2015lol} and Hyper-Kamiokande~\cite{Hyper-Kamiokande:2018ofw} in light of anticipated galactic supernova event were also performed.
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.47\textwidth]{figures/Supernova_Diagram_Draft-1.pdf}
+    \caption{\textbf{The decay geometry for Majorons produced in SN.}}
+    \label{fig:geometry}
+\end{figure}
 
@@
 
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
+    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from SM production and two Majoron hypotheses}}.
+    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
+    }
+    \label{fig:fluxes}
+\end{figure}
+
 We will set supernova bounce time $t_{\rm bounce}$ as $t = 0$.
@@
 
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.47\textwidth]{figures/DecayGeometry.pdf}
-    \caption{\textbf{The decay geometry for Majorons produced in SN.}}
-    \label{fig:geometry}
-\end{figure}
 Very weakly coupled Majorons immediately stream out after the production.
@@
 
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
+    \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
+    The hit rate from the SM neutrino flux peaks at around 0.1~s, coinciding with the peak emission of $\bar{\nu}_{e}$ from the SN.
+    The shaded regions correspond to the timing windows that give peak sensitivity to the particular model. These are the same benchmarks in the parameter space as in Fig.~\ref{fig:fluxes}.
+    In the right panel, we show the test statistic as a function of the starting time and length of the window.
+    The relatively broad distribution of high test-statistic values for the heavy Majoron benchmark ($m_\phi=200$ MeV) shows that this analysis technique does not require extremely precise reconstruction of the $t_{\mathrm{bounce}}$.
+    }
+    \label{fig:hits_and_likelihood}
+\end{figure*}
+
 We can obtain the flux of daughter $\nu$ by considering decays that occur only at $L_1\geq R^{\nu}_{\rm SN}$.
@@
 This time window is larger than typical values of time delay arising in the model.
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
-    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from SM production and two Majoron hypotheses}}.
-    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
-    }
-    \label{fig:fluxes}
-\end{figure}
+
 We will consider a supernova event that happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}.
@@
 
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=0.95\textwidth]{figures/hits_and_likelihood.pdf}
-    \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
-    The hit rate from the SM neutrino flux peaks at around 0.1~s, coinciding with the peak emission of $\bar{\nu}_{e}$ from the SN.
-    The shaded regions correspond to the timing windows that give peak sensitivity to the particular model. These are the same benchmarks in the parameter space as in Fig.~\ref{fig:fluxes}.
-    In the right panel, we show the test statistic as a function of the starting time and length of the window.
-    The relatively broad distribution of high test-statistic values for the heavy Majoron benchmark ($m_\phi=200$ MeV) shows that this analysis technique does not require extremely precise reconstruction of the $t_{\mathrm{bounce}}$.
-    }
-    \label{fig:hits_and_likelihood}
-\end{figure*}
-
 \textbf{\textit{Detector Response and Statistical Treatment}}---The IceCube Neutrino Observatory comprises 5,160 light-detecting digital optical modules (DOMs) buried in a cubic kilometer of the deep, transparent Antarctic ice sheet.
-When neutrinos interact within or near the detector, the charged by-products emit photons that the DOMs can detect.
 The DOMs are arranged on 86 strings of 60 DOMs each, with an interstring distance of 125~m (70~m for the eight centermost strings).
+These DOMs detect the photons emitted by the charged byproducts of a neutrino interaction in or near the instrumented volumen.
 This enables IceCube to resolve individual neutrinos with energies ranging between a few GeV and a few PeV.
 The neutrinos produced by supernovae are far below this threshold and cannot be individually resolved; however, the immense number of neutrinos produced in a supernova increases the single-photon rate of the detector.
-This dramatic increase in the rate of photons can be distinguished from the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic CCSNe events~\cite{Griswold:2023iwz}.
+This dramatic increase in the rate of photons can be distinguished from the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic supernovae events~\cite{Griswold:2023iwz}.
 
@@
 In this work, we simulate the light curve produced by a standard supernova with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios mentioned previously; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for light curves of the same two benchmarks from \cref{fig:fluxes}.
+
 Since more than 93\% of the photons detected in IceCube originate in IBD interactions, the SM-only event rate peaks at around 0.1~s.
@@
 In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY}~\cite{SNEWS:2021ewj} package and, in particular, the \texttt{ParametrizedFlux} object to parametrize the flux with the ``pinching'' factor~\cite{Keil:2002in,SNEWS:2021ewj}.
+
+Since each DOM only sees photons originating from within a sphere of radius $\sim 5.2$~m~\cite{IceCube:2011cwc}, each module can be treated independently if the intermodule spacing is $\gtrsim10.4$~m.
+This criteria will be met in IceCube-Gen2~\cite{IceCube-Gen2:2020qha}, and thus, we should expect the total number of hits to scale like the effective photocathode area, \textit{i.e.}:
+$$
+A_{\mathrm{eff}}^{\mathrm{PC}} = \sum_{i} \varepsilon_{i} A_{i}^{\mathrm{PC}},
+$$
+where $\varepsilon_{i}$ and $A_{i}^{\mathrm{PC}}$ are the quantum efficiency and photocathode area of a PMT and the sum runs over all PMTs in the detector.
+Using this method, we rescale the results from the simulation from IceCube to IceCube-Gen2 in order to estimate IceCube-Gen2's sensitivity.
 
@@
     \caption{\textbf{\textit{Exclusion sensitivities for the Majoron case.}}
-    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
+    The lines on this plot show the exclusion sensitivity for IceCube, IceCube Gen-2, Hyper-Kamiokande and DUNE.
+    The sensitivities shown as solid lines are computed from this work, whereas the dashed lines have been previously computed in~\cite{Brdar:2023tmi}.
     Additionally, we also show the reaches by supernova cooling (blue) and by the lack of observation of high-energy neutrinos from SN1987A (grey).
@@
 \textit{Acknowledgements}---
-We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching CCSNe simulations (available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/}) in machine-readable form, and also for stimulating discussions.
+We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching supernovae simulations (available at \url{https://wwwmpa.mpa-garching.mpg.de/supernovaarchive/}) in machine-readable form, and also for stimulating discussions.
 Y.-Y.
@@
     \caption{\textbf{\textit{Exclusion sensitivities for the magnetic moment case.}}
-    The lines on this plot show the exclusion sensitivity for IceCube, and two next-generation neutrino experiments, Hyper-Kamiokande and DUNE.
+    The lines on this plot show the exclusion sensitivity for IceCube, IceCube-Gen2, Hyper-Kamiokande and DUNE. 
+    Sensitivities indicated by solid lines are newly computed in this work, whereas those shown by dashed lines have been previously computed in~\cite{Brdar:2023tmi}
     The shaded regions are excluded by the energy loss constraints, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from supernova explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.

### 2024-03-08 paper/main.tex

@@
 Our approach utilizes publicly available packages, \texttt{ASTERIA} and \texttt{SNEWPY}, for simulating detector responses and parametrizing neutrino fluxes originating from Standard Model and new physics.
-We present results for two beyond the Standard Model scenarios and introduce tool developed for testing a diverse range of new physics models.
+We present results for two beyond the Standard Model scenarios and introduce the tool developed for testing a diverse range of new physics models.
 \end{abstract}
@@
     \includegraphics[width=0.47\textwidth]{figures/Supernova_Diagram_Draft-1.pdf}
-    \caption{\textbf{The decay geometry for Majorons produced in SN.}}
+    \caption{\textbf{The decay geometry for Majorons produced in supernova.}}
     \label{fig:geometry}
@@
 
+We will consider a supernova event that happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}.
 To get the characteristic value of $\delta t$, we can take $L_1 = L_\phi$ with $L_\phi = (E_\phi/m_\phi) \Gamma^{-1}_\phi \beta$ being the decay length of $\phi$.
@@
     The shaded regions correspond to the timing windows that give peak sensitivity to the particular model. These are the same benchmarks in the parameter space as in Fig.~\ref{fig:fluxes}.
-    In the right panel, we show the test statistic as a function of the starting time and length of the window.
-    The relatively broad distribution of high test-statistic values for the heavy Majoron benchmark ($m_\phi=200$ MeV) shows that this analysis technique does not require extremely precise reconstruction of the $t_{\mathrm{bounce}}$.
+    In the right panel, we show the test statistic as a function of the starting time and length of the window for the heavy Majoron benchmark ($m_\phi=200$ MeV).
+    The relatively broad distribution of high test-statistic values shows that this analysis technique does not require extremely precise reconstruction of the $t_{\mathrm{bounce}}$.
     }
@@
 
-We will consider a supernova event that happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}.
 As $\bar{\nu}_e$ contribute chiefly to the signals at IceCube via inverse beta decay (IBD), we show in~\cref{fig:fluxes} the differential fluxes of daughter $\bar{\nu}_e$ at different times for two benchmark points in the Majoron model, in comparison to the SM $\bar{\nu}_e$ flux.
@@
     The lines on this plot show the exclusion sensitivity for IceCube, IceCube Gen-2, Hyper-Kamiokande and DUNE.
-    The sensitivities shown as solid lines are computed from this work, whereas the dashed lines have been previously computed in~\cite{Brdar:2023tmi}.
-    Additionally, we also show the reaches by supernova cooling (blue) and by the lack of observation of high-energy neutrinos from SN1987A (grey).
+    %The sensitivities shown as solid lines are computed from this work, whereas the dashed lines are computed following~\cite{Brdar:2023tmi}.
+    Additionally, we also show the reaches by supernova cooling and by the lack of observation of high-energy neutrinos from SN1987A as black lines.
 %\cite{Fiorillo:2022cdq}, with the width of the shading region quantifying uncertainties from supernova modeling.
@@
 \end{figure} 
-Following our strategies above, we obtain the expected exclusion limits for various BSM scenarios for no observed excess of hits on top of background noise and standard neutrino flux.
-The expected exclusion limits are presented in \cref{fig:sensitivity} for the Majoron case.
+Following our strategies above, we obtain the expected exclusion limits for various BSM scenarios from no observed excess of hits on top of background noise and standard neutrino flux.
+The expected exclusion limits are presented in \cref{fig:sensitivity} for the Majoron case considering both IceCube and IceCube-Gen2.
 To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
-Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement (blue band), and non-observation of high-energy supernova neutrinos from SN 1987A (gray band) are also shown in \cref{fig:sensitivity} for the Majoron case.
-With future supernova explosions, IceCube can improve existing limits by one order of magnitude.
-Moreover, while existing limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide a stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.
+Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement, and non-observation of high-energy supernova neutrinos from SN 1987A are also shown in \cref{fig:sensitivity} for the Majoron case.
+With future supernova explosions, IceCube can improve current limits by one order of magnitude.
+Moreover, while current limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide a stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.
 
@@
 CAA and JL were partially supported by the Alfred P. Sloan Foundation for part of this work.
+JL acknowledges support from the Belgian American Educational Foundation.
 
@@
     \caption{\textbf{\textit{Exclusion sensitivities for the magnetic moment case.}}
-    The lines on this plot show the exclusion sensitivity for IceCube, IceCube-Gen2, Hyper-Kamiokande and DUNE. 
-    Sensitivities indicated by solid lines are newly computed in this work, whereas those shown by dashed lines have been previously computed in~\cite{Brdar:2023tmi}
-    The shaded regions are excluded by the energy loss constraints, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from supernova explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.
+    The lines on this plot show the exclusion sensitivity for IceCube, IceCube-Gen2, and the limits computed in \cite{Brdar:2023tmi} for Hyper-Kamiokande and DUNE. 
+    %Sensitivities indicated by solid lines are newly computed in this work, whereas those shown by dashed lines have been previously computed in~\cite{Brdar:2023tmi}
+    The shaded regions are excluded by the combination of energy loss requirement, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from supernova explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.
     }
@@
 Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}.
-The limits from IceCube are shown in \cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from low-energy supernova explosions (SNIIP) \cite{PhysRevLett.128.221103, chauhan2024probing}.
+The limits from IceCube are shown in SUPPL.\cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from low-energy supernova explosions (SNIIP) \cite{PhysRevLett.128.221103, chauhan2024probing}.
 We also point out that by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside SN, the limits we obtained are conservative relative to the SNIIP region taken from \cite{chauhan2024probing}.
-We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over DUNE and Hyper-Kamiokande.
+We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over the limits computed in \cite{Brdar:2023tmi} for DUNE and Hyper-Kamiokande.
 

### 2024-03-13 paper/main.tex
Updates from Overleaf

@@
 To this end, numerous BSM searches across a wide range of scales have been performed, from collider searches at high energies~\cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero~\cite{Baumann:2015rya}.
-Supernovae release most of their energy in neutrinos, offering unique opportunities to test BSM physics via neutrino interactions.
-The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only supernova observed in neutrinos---have already given tentative constraints on the energies that could be taken away by any light BSM particle copiously produced in the interior of a star.
-Indeed, many different BSM scenarios models have been constrained in this way, see \textit{e.g.} Refs.~\cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.
 
-If, additionally, BSM particles emitted from supernovae can decay to neutrinos en route to Earth, even stronger limits can be set, as shown, for instance, in Ref.~\cite{Fiorillo:2022cdq} for Majoron-like bosons and in Ref.~\cite{Brdar:2023tmi} for a realization featuring a neutrino magnetic moment portal.
-Specifically, unlike neutrinos inside the supernova core, produced BSM states can stream out without further interactions.
+Supernovae (SNe) release most of their energy in neutrinos, offering unique opportunities to test BSM physics via neutrino interactions.
+The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only SN observed in neutrinos---have already given tentative constraints on the energies that could be taken away by any light BSM particle copiously produced in the interior of a star.
+Indeed, many different BSM scenarios have been constrained in this way, see \textit{e.g.} Refs.~\cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.
+If, additionally, BSM particles emitted from SNe can decay to neutrinos en route to Earth, even stronger limits can be set, as shown, for instance, in Ref.~\cite{Fiorillo:2022cdq} for Majoron-like bosons and in Ref.~\cite{Brdar:2023tmi} for a realization featuring a neutrino magnetic moment portal.
+Specifically, unlike neutrinos inside the SN core, produced BSM states can stream out without further interactions.
 Consequently, they exit with higher energies than neutrinos, typically around $\mathcal{O}(100)$~MeV.
@@
 Such strategies were utilized for neutrino experiments operating during the SN 1987A event.
-Sensitivity projections for  DUNE~\cite{DUNE:2015lol} and Hyper-Kamiokande~\cite{Hyper-Kamiokande:2018ofw} in light of anticipated galactic supernova event were also performed.
-
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.47\textwidth]{figures/Supernova_Diagram_Draft-1.pdf}
-    \caption{\textbf{The decay geometry for Majorons produced in supernova.}}
-    \label{fig:geometry}
-\end{figure}
+Sensitivity projections for  DUNE~\cite{DUNE:2015lol} and Hyper-Kamiokande~\cite{Hyper-Kamiokande:2018ofw} in light of anticipated galactic SN event were also performed.
 
 The IceCube Neutrino Observatory has pioneered the detection of neutrinos at $\mathcal{O}$(PeV) energies~\cite{IceCube:2014stg,IceCube:2018cha} and has identified several specific astrophysical neutrino sources~\cite{IceCube:2018cha,IceCube:2023ame,IceCube:2022der}.
-IceCube is also expected to be able to detect the next galactic supernova~\cite{Kopke_2011}.
-In fact, a search for MeV neutrinos from optically obscured galactic supernovae was recently performed in \cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm}.
+IceCube is also expected to be able to detect the next galactic SN~\cite{Kopke_2011}.
+In fact, a search for MeV neutrinos from optically obscured galactic SNe was recently performed in \cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm}.
 In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise  within a certain time window, and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ seconds.
-In this letter, we demonstrate that such precise time resolution will play a crucial role in testing new physics from supernovae.
+In this Letter, we will demonstrate that such precise time resolution will play a crucial role in testing new physics from SNe.
 
-Once produced in supernovae, the BSM particles can be nonrelativistic and travel slowly, causing time delays for secondary neutrinos.
-However, it is also possible that new states are rather light, implying that they may even exit the supernova at earlier times with respect to certain flavors of SM neutrinos.
-Such an early BSM signal, which to the best of our knowledge has not been previously considered, can, for instance, be induced by light BSM states produced from $\nu_e$ scattering inside the supernova; they would then subsequently decay to $\bar{\nu}_e$, which chiefly induces the signal at IceCube.
-This would happen at early stages of a supernova, around the neutralization burst, when $\nu_e$ are present and antineutrinos have not been produced yet.
+Once produced in SNe, the BSM particles can be nonrelativistic and travel slowly, causing time delays for secondary neutrinos.
+However, it is also possible that new states are rather light, implying that they may even exit the SN at earlier times with respect to certain flavors of SM neutrinos.
+Such an early BSM signal, which to the best of our knowledge has not been previously considered, can, for instance, be induced by light BSM states produced from $\nu_e$ scattering inside the SN; they would then subsequently decay to $\bar{\nu}_e$, which chiefly induces the signal at IceCube.
+This would happen at early stages of a SN, around the neutralization burst, when $\nu_e$ are present and antineutrinos have not been produced yet.
 Such novel timing patterns generically exist in models with new weakly interacting particles, such as the aforementioned Majoron model~\cite{Fiorillo:2022cdq} and the neutrino magnetic moment portal~\cite{Magill:2018jla,Brdar:2020quo}.
-Via the timing measurement, we will show that neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association with forthcoming galactic supernova events.\\
+
+In this work we will show that, by using the timing measurements, neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association with forthcoming galactic SN events.\\
+%Via the timing measurement, we will show that neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association with forthcoming galactic SN events.\\
 
@@
 \textbf{\textit{The Model}}---
-Let us first consider the Majoron model, studied in Ref.~\cite{Fiorillo:2022cdq}, where supernova 1987A constraints were derived.
+Let us first consider the Majoron model, studied in Ref.~\cite{Fiorillo:2022cdq}, where SN 1987A constraints were derived.
 The relevant part of the Lagrangian reads
@@
 
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
-    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from SM production and two Majoron hypotheses}}.
-    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
-    }
-    \label{fig:fluxes}
-\end{figure}
-
-We will set supernova bounce time $t_{\rm bounce}$ as $t = 0$.
+We will set SN bounce time $t_{\rm bounce}$ as $t = 0$.
 Using data from the simulation of $8.8 M_\odot$ progenitor star \cite{Huedepohl2010} and including effects of neutrino oscillations assuming normal mass ordering \cite{Dighe:1999bi}, we calculated standard neutrino fluxes at Earth.
@@
 Thus we found that the Majoron flux peaks around $t \sim \unit[0.05]{s}$.
-We further cross checked the agreement with Ref.~\cite{Fiorillo:2022cdq} by reproducing their bound from supernova energy loss.
+We further cross checked the agreement with Ref.~\cite{Fiorillo:2022cdq} by reproducing their bound from SN energy loss.
 
-Very weakly coupled Majorons immediately stream out after the production.
+\begin{figure}[t!]
+\vspace{0.27cm}
+    \centering
+    \includegraphics[width=0.48\textwidth]{figures/Supernova_Diagram_Draft-2}
+    \caption{\textbf{The decay geometry for Majorons produced in supernova.}}
+    \label{fig:geometry}
+\end{figure}
+
+Very weakly coupled Majorons immediately stream out after being produced inside the star.
 On their way to Earth, Majorons of energy $E_\phi$ will travel at the speed of $\beta$ for a distance of $L_1$, then decay to (anti)neutrinos of energy $E_\nu$ at an emission angle $\cos\alpha = (2 E_\phi E_{\nu} - m^2_\phi)/(2E_{\nu}E_\phi\beta)$.
-Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a supernova that is $D_{\rm SN}$ away (see the decay geometry in \cref{fig:geometry}).
-The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a supernova to reach the Earth is given by
+Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a SN that is $D_{\rm SN}$ away (see the decay geometry in \cref{fig:geometry}).
+The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a SN to reach the Earth is given by
 \cite{Jaeckel:2017tud}
@@
 
-We will consider a supernova event that happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}.
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.47\textwidth]{figures/majoran_fluxes.pdf}
+    \caption{\textit{\textbf{Flux of $\bar{\nu}_{e}$ from SM production and two Majoron hypotheses at Earth}}.
+    We choose the parameters $g_\phi = 10^{-10.2}$ and $g_\phi = 10^{-11.8}$ for $m_\phi = \unit[1]{MeV}$ and $m_\phi = \unit[200]{MeV}$, respectively.
+    }
+    \label{fig:fluxes}
+\end{figure}
+
+We will consider a SN event that happens in the galaxy at a distance $D_{\rm SN}=\unit[10]{kpc}$, which is not unlikely~\cite{Reed:2005en,Rozwadowska:2020nab}.
 To get the characteristic value of $\delta t$, we can take $L_1 = L_\phi$ with $L_\phi = (E_\phi/m_\phi) \Gamma^{-1}_\phi \beta$ being the decay length of $\phi$.
@@
 which is roughly independent of Majoron energy $E_\phi$.
-%However, at small values of $E_\phi$, the main contribution to $\delta t$ comes from the first term due to the slow-moving Majorons, while at larger values of $E_\phi$, from the second term due to a larger detour given the increase of $L_\phi$ over the decrease of $(1-\cos\alpha)$.
 
@@
     \caption{\textbf{\textit{Timing profile of hits and test statistic as a function of the timing window.}}
-    The hit rate from the SM neutrino flux peaks at around 0.1~s, coinciding with the peak emission of $\bar{\nu}_{e}$ from the SN.
-    The shaded regions correspond to the timing windows that give peak sensitivity to the particular model. These are the same benchmarks in the parameter space as in Fig.~\ref{fig:fluxes}.
+    In the left panel, we show the hit rate from the SM neutrino flux which peaks at around 0.1~s, coinciding with the peak emission of $\bar{\nu}_{e}$ from the SN.
+The shaded regions correspond to the timing windows that give peak sensitivity to the particular model.
+These are the same benchmarks in the parameter space as in Fig.~\ref{fig:fluxes}.
     In the right panel, we show the test statistic as a function of the starting time and length of the window for the heavy Majoron benchmark ($m_\phi=200$ MeV).
@@
 As the smallest decay distance beyond which the daughter neutrino can escape the explosion unperturbed is roughly the radius of the core, we take $R^{\nu}_{\rm SN} = \unit[30]{km}$.
-We will also limit our analysis to a maximal time window of $\unit[100]{s}$ after supernova bounce.
+We will also limit our analysis to a maximal time window of $\unit[100]{s}$ after SN bounce.
 This time window is larger than typical values of time delay arising in the model.
@@
 The DOMs are arranged on 86 strings of 60 DOMs each, with an interstring distance of 125~m (70~m for the eight centermost strings).
-These DOMs detect the photons emitted by the charged byproducts of a neutrino interaction in or near the instrumented volumen.
+These DOMs detect the photons emitted by the charged byproducts of a neutrino interaction in or near the instrumented volume.
 This enables IceCube to resolve individual neutrinos with energies ranging between a few GeV and a few PeV.
-The neutrinos produced by supernovae are far below this threshold and cannot be individually resolved; however, the immense number of neutrinos produced in a supernova increases the single-photon rate of the detector.
-This dramatic increase in the rate of photons can be distinguished from the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic supernovae events~\cite{Griswold:2023iwz}.
+The neutrinos produced by SNe are far below this threshold and cannot be individually resolved; however, the immense number of neutrinos produced in a SN increases the single-photon rate of the detector.
+This dramatic increase in the rate of photons can be distinguished from the background caused by dark noise and radioactive activity in the DOM glass to enable the detection of galactic SN events~\cite{Griswold:2023iwz}.
 
-New physics will affect the development of a supernova and distort the temporal structure of the photon signal seen in the IceCube detector.
+New physics will affect the development of a SN and distort the temporal structure of the photon signal seen in the IceCube detector.
 Thus, one may look for excess events in certain time intervals as evidence of this new physics.
-In this work, we simulate the light curve produced by a standard supernova with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios mentioned previously; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for light curves of the same two benchmarks from \cref{fig:fluxes}.
+In this work, we simulate the light curve produced by a standard SN with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios mentioned previously; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for light curves of the same two benchmarks from \cref{fig:fluxes}.
 
@@
 BSM scenarios, on the other hand, can give rise to an early or delayed signal depending on the particulars of the model.
-In essence, Majorons can be generated before the peak of the SM $\bar{\nu}_{e}$ flux, and as light Majorons can travel nearly relativistically, they can escape the supernovae with negligible time delay and then decay to an all-flavor flux of neutrinos, producing early $\bar{\nu}_{e}$ fluxes before the SM one.
+In essence, Majorons can be generated before the peak of the SM $\bar{\nu}_{e}$ flux, and as light Majorons can travel nearly relativistically, they can escape the SNe with negligible time delay and then decay to an all-flavor flux of neutrinos, producing early $\bar{\nu}_{e}$ fluxes before the SM one.
 The higher-mass Majorons, on the other hand, acquire a time delay from traveling sub-luminally and at a large detour, thus producing a later signal with sizable time delay.
-We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different supernova scenarios and the thermal and radioactive noise in the DOMs.
+We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different SN scenarios and the thermal and radioactive noise in the DOMs.
 This package simulates light yields from coherent $\nu_{e}$ scattering off electrons in the ice, IBD of $\bar{\nu}_{e}$ on nuclei in the ice, and charged- and neutral-current interactions for $\nu_{\alpha}$.
-In addition to photons produced in neutrino interactions, it also simulates photons from thermal noise in the IceCube PMTs and from radioactive decay in the pressure glass housing.
+In addition to photons produced in neutrino interactions, it also simulates photons from thermal noise in the IceCube photomultipliers (PMTs) and from radioactive decay in the pressure glass housing.
 In order to interface with \texttt{ASTERIA}, we use the \texttt{SNEWPY}~\cite{SNEWS:2021ewj} package and, in particular, the \texttt{ParametrizedFlux} object to parametrize the flux with the ``pinching'' factor~\cite{Keil:2002in,SNEWS:2021ewj}.
@@
     \caption{\textbf{\textit{Exclusion sensitivities for the Majoron case.}}
-    The lines on this plot show the exclusion sensitivity for IceCube, IceCube Gen-2, Hyper-Kamiokande and DUNE.
-    %The sensitivities shown as solid lines are computed from this work, whereas the dashed lines are computed following~\cite{Brdar:2023tmi}.
-    Additionally, we also show the reaches by supernova cooling and by the lack of observation of high-energy neutrinos from SN1987A as black lines.
-%\cite{Fiorillo:2022cdq}, with the width of the shading region quantifying uncertainties from supernova modeling.
+    The lines on this plot show the exclusion sensitivity for IceCube, IceCube Gen-2, Hyper-Kamiokande and DUNE at $2\sigma$ CL.
+    Additionally, we also show the reaches by SN cooling and by the lack of observation of high-energy neutrinos from SN1987A as black lines. 
+    The sensitivities shown by the dashed line is obtained following~\cite{Brdar:2023tmi} with time-integrated data.
     }
@@
 To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
-Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement, and non-observation of high-energy supernova neutrinos from SN 1987A are also shown in \cref{fig:sensitivity} for the Majoron case.
-With future supernova explosions, IceCube can improve current limits by one order of magnitude.
+Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement, and non-observation of high-energy SN neutrinos from SN 1987A are also shown in \cref{fig:sensitivity} for the Majoron case.
+With future SN explosions, IceCube can improve current limits by one order of magnitude.
 Moreover, while current limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide a stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.
@@
 
-There are existing uncertainties from different modeling of supernova explosions (see e.g.
+There are existing uncertainties from different modeling of SN explosions (see e.g.
 Ref.~\cite{li2023old}) as well as discrepancies between SN 1987A neutrino data and modeling.
 Nevertheless, we point out that even the uncertainties of around $2\sigma$  will only change our exclusion limits by a small factor.
-We make the code used in this work publicly available so that the impact of supernova modeling uncertainties on the sensitivity of neutrino telescopes to BSM scenarios can be further explored.
+We make the code used in this work publicly available so that the impact of SN modeling uncertainties on the sensitivity of neutrino telescopes to BSM scenarios can be further explored.
 
 \textbf{\textit{Summary}}---
-In this letter, we have demonstrated that neutrino telescopes such as IceCube can provide unprecedented probes of new physics, such as Majoron-like bosons and neutrino magnetic moment portal, by measuring supernova time profiles to a window as short as $\mathcal{O}(0.01)$ s.
+In this Letter, we have demonstrated that neutrino telescopes such as IceCube can provide unprecedented probes of new physics, such as Majoron-like bosons and neutrino magnetic moment portal, by measuring SN time profiles to a window as short as $\mathcal{O}(0.01)$ s.
 Specifically, signatures outside the SM neutrino time window, including both early and delayed signals, can be effectively probed by neutrino telescopes.
@@
 \textit{Acknowledgements}---
-We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching supernovae simulations (available at \url{https://wwwmpa.mpa-garching.mpg.de/supernovaarchive/}) in machine-readable form, and also for stimulating discussions.
+We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching Ssupernovae simulations (available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/}) in machine-readable form, and also for stimulating discussions.
 Y.-Y.
@@
     The lines on this plot show the exclusion sensitivity for IceCube, IceCube-Gen2, and the limits computed in \cite{Brdar:2023tmi} for Hyper-Kamiokande and DUNE. 
+    The sensitivities shown by the dashed line have been previously computed~\cite{Brdar:2023tmi} and use time-integrated data.
     %Sensitivities indicated by solid lines are newly computed in this work, whereas those shown by dashed lines have been previously computed in~\cite{Brdar:2023tmi}
-    The shaded regions are excluded by the combination of energy loss requirement, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from supernova explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.
+    The shaded regions are excluded by the combination of energy loss requirement, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from SN explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.
     }
@@
 Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}.
-The limits from IceCube are shown in SUPPL.\cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from low-energy supernova explosions (SNIIP) \cite{PhysRevLett.128.221103, chauhan2024probing}.
+The limits from IceCube are shown in SUPPL.
+\cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from low-energy SN explosions (SNIIP) \cite{PhysRevLett.128.221103, chauhan2024probing}.
 We also point out that by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside SN, the limits we obtained are conservative relative to the SNIIP region taken from \cite{chauhan2024probing}.
-We notice that the time delay near the exclusion boundary are typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over the limits computed in \cite{Brdar:2023tmi} for DUNE and Hyper-Kamiokande.
+We notice that the time delay near the exclusion boundary is typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over the limits computed in \cite{Brdar:2023tmi} for DUNE and Hyper-Kamiokande.
 

### 2024-03-14 paper/main.tex

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textbf{\textit{Introduction}}---
-The Standard Model (SM) is a remarkable but incomplete theory. 
+\textbf{\textit{Introduction}}---The Standard Model (SM) is a remarkable but incomplete theory. 
 Puzzles such as the non-vanishing neutrino mass, the origin of observed matter-antimatter asymmetry, and the nature of dark matter, among others, seek explanations beyond the SM (BSM).
-There are also no firmly established clues on the energy scale at which the new particles should appear.
-To this end, numerous BSM searches across a wide range of scales have been performed, from collider searches at high energies~\cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero~\cite{Baumann:2015rya}.
+Since there are also no firmly established clues on the energy scale at which the new particles should appear, numerous BSM searches across a wide range of scales have been performed: from collider searches at high energies~\cite{Nath:2010zj} to studies of cosmic microwave background at temperatures near absolute zero~\cite{Baumann:2015rya}.
 
@@
 
+\begin{figure}[t!]
+\vspace{0.27cm}
+    \centering
+    \includegraphics[width=0.48\textwidth]{figures/Supernova_Diagram}
+    \caption{\textit{\textbf{The decay geometry for Majorons produced in a SN.}}
+    Both the additional distance travelled relative to the direct line of sight and the potential non-relativistic speed of the Majoran of can induce a delayed signal relative to the SM signal.
+    }
+    \label{fig:geometry}
+\end{figure}
+
 The IceCube Neutrino Observatory has pioneered the detection of neutrinos at $\mathcal{O}$(PeV) energies~\cite{IceCube:2014stg,IceCube:2018cha} and has identified several specific astrophysical neutrino sources~\cite{IceCube:2018cha,IceCube:2023ame,IceCube:2022der}.
 IceCube is also expected to be able to detect the next galactic SN~\cite{Kopke_2011}.
-In fact, a search for MeV neutrinos from optically obscured galactic SNe was recently performed in \cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts \cite{IceCube:2019acm}.
+In fact, a search for MeV neutrinos from optically obscured galactic SNe was recently performed in~\cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts~\cite{IceCube:2019acm}.
 In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise  within a certain time window, and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ seconds.
@@
 We will set SN bounce time $t_{\rm bounce}$ as $t = 0$.
-Using data from the simulation of $8.8 M_\odot$ progenitor star \cite{Huedepohl2010} and including effects of neutrino oscillations assuming normal mass ordering \cite{Dighe:1999bi}, we calculated standard neutrino fluxes at Earth.
+Using data from the simulation of $8.8 M_\odot$ progenitor star~\cite{Huedepohl2010} and including effects of neutrino oscillations assuming normal mass ordering~\cite{Dighe:1999bi}, we calculated standard neutrino fluxes at Earth.
 Following Ref.~\cite{Fiorillo:2022cdq}, we also calculated the flux of emitted Majorons.
@@
 
-\begin{figure}[t!]
-\vspace{0.27cm}
-    \centering
-    \includegraphics[width=0.48\textwidth]{figures/Supernova_Diagram_Draft-2}
-    \caption{\textbf{The decay geometry for Majorons produced in supernova.}}
-    \label{fig:geometry}
-\end{figure}
-
 Very weakly coupled Majorons immediately stream out after being produced inside the star.
 On their way to Earth, Majorons of energy $E_\phi$ will travel at the speed of $\beta$ for a distance of $L_1$, then decay to (anti)neutrinos of energy $E_\nu$ at an emission angle $\cos\alpha = (2 E_\phi E_{\nu} - m^2_\phi)/(2E_{\nu}E_\phi\beta)$.
-Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a SN that is $D_{\rm SN}$ away (see the decay geometry in \cref{fig:geometry}).
-The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a SN to reach the Earth is given by
-\cite{Jaeckel:2017tud}
+Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a SN that is $D_{\rm SN}$ away;see the decay geometry in \cref{fig:geometry}.
+The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a SN to reach the Earth is given by~\cite{Jaeckel:2017tud}
 \begin{align}
@@
 The higher-mass Majorons, on the other hand, acquire a time delay from traveling sub-luminally and at a large detour, thus producing a later signal with sizable time delay.
+
 We use the \texttt{ASTERIA}~\cite{spencer_griswold_2020_3926835} package to simulate the detector response to the different SN scenarios and the thermal and radioactive noise in the DOMs.
@@
 \begin{equation}
+\label{eq:likelihood}
     -2\Delta\mathrm{LLH} = 2 \left[N_{\mathrm{exp.}} - N_{\mathrm{obs.}} + N_{\mathrm{obs.}}\log\left(\frac{N_{\mathrm{obs.}}}{N_{\mathrm{exp.}}}\right)\right],
@@
 where $N_{\mathrm{obs.}}$ is the number of photons seen in the detector in the given time and $N_{\mathrm{exp.}}$ is the number of photons expected from a particular BSM hypothesis. 
-For each BSM hypothesis, we then select the time range that maximizes the test statistic and use that maximal test statistic value.
+For each BSM hypothesis, we select the time range that maximizes the test statistic and use that maximal test statistic value.
 The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}, which is around $\unit[0.1]{s}$ ($\unit[10]{s}$) for the light (heavy) benchmark case, consistent with its time spread of the produced $\bar{\nu}_e$ flux.
@@
 In the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}, we show the test statistic as a function of the time at which the time range begins, $t_{\mathrm{start}}$, and the duration of the time range, $\Delta t$, for an example BSM hypothesis.
-The distribution of test-statistic values is not sharply peaked in time, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$ \cite{Halzen_2009}.
+The distribution of test-statistic values is not sharply peaked in time, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$~\cite{Halzen_2009}.
 
@@
 \end{figure} 
-Following our strategies above, we obtain the expected exclusion limits for various BSM scenarios from no observed excess of hits on top of background noise and standard neutrino flux.
-The expected exclusion limits are presented in \cref{fig:sensitivity} for the Majoron case considering both IceCube and IceCube-Gen2.
+Under the assumption that no excess neutrino were seen above the expected detector backgrounds and SM neutrinos, we obtain the expected $2\sigma$ exclusion limits by finding the coupling where Eq.~\ref{eq:likelihood} is equal to 3.841.
+These limits are presented in \cref{fig:sensitivity} for the Majoron case considering both IceCube and IceCube-Gen2.
 To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
-Current limits \cite{Fiorillo:2022cdq} from the energy loss requirement, and non-observation of high-energy SN neutrinos from SN 1987A are also shown in \cref{fig:sensitivity} for the Majoron case.
-With future SN explosions, IceCube can improve current limits by one order of magnitude.
+Current limits~\cite{Fiorillo:2022cdq} from the energy loss requirement, and non-observation of high-energy SN neutrinos from SN 1987A are also shown in \cref{fig:sensitivity} for the Majoron case.
+A future SN explosions would enable IceCube to improve current limits by one order of magnitude. 
 Moreover, while current limits from time-integrated observables follow the behavior of $g_\phi\propto m^{-1}_\phi$ as Majoron production rate is proportional to $(g_\phi m_\phi)^2$, IceCube can provide a stronger limit than this by focusing on the time window, especially before the peak of SM $\bar{\nu}_e$ fluxes, to reduce SM condemnations.
@@
 \textit{Acknowledgements}---
-We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching Ssupernovae simulations (available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/}) in machine-readable form, and also for stimulating discussions.
-Y.-Y.
-L is supported by the NSF of China through Grant No.
-12305107, 12247103.
+We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching supernovae simulations---available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/} in machine-readable form---and also for stimulating discussions.
+We would also like to thank Jackapan Pairin for their help designing figures in this work.
+Y.-Y. L is supported by the NSF of China through Grant No. 12305107, 12247103.
 CAA are supported by the Faculty of Arts and Sciences of Harvard University, the National Science Foundation (NSF), the NSF AI Institute for Artificial Intelligence and Fundamental Interactions (IAIFI), the Research Corporation for Science Advancement,
@@
 CAA and JL were partially supported by the Alfred P. Sloan Foundation for part of this work.
-JL acknowledges support from the Belgian American Educational Foundation.
+JL is supported frbyom the Belgian American Educational Foundation.
 
@@
     \caption{\textbf{\textit{Exclusion sensitivities for the magnetic moment case.}}
-    The lines on this plot show the exclusion sensitivity for IceCube, IceCube-Gen2, and the limits computed in \cite{Brdar:2023tmi} for Hyper-Kamiokande and DUNE. 
+    The lines on this plot show the exclusion sensitivity for IceCube, IceCube-Gen2, and the limits computed in~\cite{Brdar:2023tmi} for Hyper-Kamiokande and DUNE. 
     The sensitivities shown by the dashed line have been previously computed~\cite{Brdar:2023tmi} and use time-integrated data.
     %Sensitivities indicated by solid lines are newly computed in this work, whereas those shown by dashed lines have been previously computed in~\cite{Brdar:2023tmi}
-    The shaded regions are excluded by the combination of energy loss requirement, non-observation of photon and neutrino signals from SN1987A studied in \cite{Brdar:2023tmi} and by constraints on the energy release from SN explosion (SNIIP explosion)\cite{PhysRevLett.128.221103, chauhan2024probing}.
+    The shaded regions are excluded by the combination of energy loss requirement, non-observation of photon and neutrino signals from SN1987A studied in~\cite{Brdar:2023tmi} and by constraints on the energy release from SN explosion (SNIIP explosion)~\cite{PhysRevLett.128.221103, chauhan2024probing}.
     }
@@
 \end{figure}
-Here we also present results for active-to-sterile neutrino transition magnetic moment described by \cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
+Here we also present results for active-to-sterile neutrino transition magnetic moment described by~\cite{Magill:2018jla,Brdar:2020quo,Brdar:2023tmi}
 \begin{align}
@@
 We consider the two production channels for $N$ inside the SN: $\nu e^- \to N e^-$ at lower energies and $\nu \gamma \to N$ for larger active neutrino energies.
-Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$ \cite{Plestid:2020vqf}.
+Both processes occur due to the interaction term in \cref{eq:Lag}; after $N$ are produced, they decay to active neutrinos and photons which is again realized through the same term in the Lagrangian, with the decay width for $N\to\nu\gamma$ given by $\Gamma_N = 6d^2 M_N^3/4 \pi$~\cite{Plestid:2020vqf}.
 The limits from IceCube are shown in SUPPL.
-\cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A \cite{Brdar:2023tmi}, and constraints on the energy release from low-energy SN explosions (SNIIP) \cite{PhysRevLett.128.221103, chauhan2024probing}.
-We also point out that by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside SN, the limits we obtained are conservative relative to the SNIIP region taken from \cite{chauhan2024probing}.
-We notice that the time delay near the exclusion boundary is typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over the limits computed in \cite{Brdar:2023tmi} for DUNE and Hyper-Kamiokande.
+\cref{fig:magnetic_moment_sensitivity}, together with previously excluded regions by energy loss, non-observations of photons and neutrinos from SN1987A~\cite{Brdar:2023tmi}, and constraints on the energy release from low-energy SN explosions (SNIIP)~\cite{PhysRevLett.128.221103, chauhan2024probing}.
+We also point out that by neglecting the $N$ production channel $\nu p^+\to N p^+$ inside SN, the limits we obtained are conservative relative to the SNIIP region taken from~\cite{chauhan2024probing}.
+We notice that the time delay near the exclusion boundary is typically of $\Delta t \sim \mathcal{O}(1)$ sec, which is longer than the standard $\bar{\nu}_e$ peak luminosity time scale and this is why IceCube does not improve over the limits computed in~\cite{Brdar:2023tmi} for DUNE and Hyper-Kamiokande.
 

### 2024-03-14 paper/main.tex
Updates from Overleaf

@@
 \usepackage[normalem]{ulem}
-\newcommand{\yy}[1]{\color{red}[YY:#1]\color{black}}
-\newcommand{\YY}[1]{\color{red}#1\color{black}}
 \usepackage{graphicx}% Include figure files
@@
 
-\preprint{USTC-ICTS/PCFT-24-07, APS/123-QED}
+\preprint{USTC-ICTS/PCFT-24-07}
 \bibliographystyle{apsrev4-1}
@@
 \begin{abstract}
-Neutrino telescopes, including IceCube, can detect galactic supernova events by observing the collective rise in photomultiplier count rates with a subsecond time resolution. 
-Leveraging precise timing, we demonstrate for the first time the capability of neutrino telescopes to explore new weakly coupled states emitted from supernovae and subsequently decaying to neutrinos.
+Neutrino telescopes, including IceCube, can detect galactic supernova events by observing the collective rise in photomultiplier count rates with a sub-second time resolution. 
+Leveraging precise timing, we demonstrate the ability of neutrino telescopes to explore new weakly coupled states emitted from supernovae and subsequently decaying to neutrinos.
 Our approach utilizes publicly available packages, \texttt{ASTERIA} and \texttt{SNEWPY}, for simulating detector responses and parametrizing neutrino fluxes originating from Standard Model and new physics.
@@
 Supernovae (SNe) release most of their energy in neutrinos, offering unique opportunities to test BSM physics via neutrino interactions.
-The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only SN observed in neutrinos---have already given tentative constraints on the energies that could be taken away by any light BSM particle copiously produced in the interior of a star.
+The duration of the burst~\cite{Kamiokande-II:1987idp,Bionta:1987qt,Baksan} and inferred total energy of neutrinos~\cite{Loredo:2001rx,Pagliaroli:2008ur,Huedepohl2010} from SN 1987A---the only SN observed in neutrinos---have already given tentative constraints on the energies that could be carried by light BSM particles produced in the interior of a star.
 Indeed, many different BSM scenarios have been constrained in this way, see \textit{e.g.} Refs.~\cite{Raffelt:2011nc,Arguelles:2016uwb,Suliga:2020vpz,Lucente:2021hbp,Caputo:2022rca,Caputo:2021rux,PhysRevD.100.083002,DeRocco:2019njg,Kazanas:2014mca,Magill:2018jla}.
 If, additionally, BSM particles emitted from SNe can decay to neutrinos en route to Earth, even stronger limits can be set, as shown, for instance, in Ref.~\cite{Fiorillo:2022cdq} for Majoron-like bosons and in Ref.~\cite{Brdar:2023tmi} for a realization featuring a neutrino magnetic moment portal.
-Specifically, unlike neutrinos inside the SN core, produced BSM states can stream out without further interactions.
+In contrast to SM neutrinos, BSM states produced in the SN core can freely stream out without further interactions.
 Consequently, they exit with higher energies than neutrinos, typically around $\mathcal{O}(100)$~MeV.
@@
     \caption{\textit{\textbf{The decay geometry for Majorons produced in a SN.}}
-    Both the additional distance travelled relative to the direct line of sight and the potential non-relativistic speed of the Majoran of can induce a delayed signal relative to the SM signal.
+    Both the additional distance travelled relative to the direct line of sight and the potential non-relativistic speed of the Majoron can induce a delayed signal relative to the SM signal.
     }
@@
 In fact, a search for MeV neutrinos from optically obscured galactic SNe was recently performed in~\cite{IceCube:2023ogt} as well as the search for temporal correlation of MeV neutrino events with fast radio bursts~\cite{IceCube:2019acm}.
-In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise  within a certain time window, and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ seconds.
+In both cases, the observable is a collective rise in all photomultiplier rates on top of the background noise in a certain time window, and it turns out that IceCube is sensitive to intervals as short as $\mathcal{O}(0.01)$ seconds.
 In this Letter, we will demonstrate that such precise time resolution will play a crucial role in testing new physics from SNe.
 
-Once produced in SNe, the BSM particles can be nonrelativistic and travel slowly, causing time delays for secondary neutrinos.
-However, it is also possible that new states are rather light, implying that they may even exit the SN at earlier times with respect to certain flavors of SM neutrinos.
+BSM states can give rise to off-time signals in two ways.
+First, if the BSM particles are non-relativistic, they will produce a delayed signal. 
+However, it is also possible that new states are light, implying that they may even exit the SN at earlier times than certain flavors of SM neutrinos.
 Such an early BSM signal, which to the best of our knowledge has not been previously considered, can, for instance, be induced by light BSM states produced from $\nu_e$ scattering inside the SN; they would then subsequently decay to $\bar{\nu}_e$, which chiefly induces the signal at IceCube.
-This would happen at early stages of a SN, around the neutralization burst, when $\nu_e$ are present and antineutrinos have not been produced yet.
+This would happen at early stages of an SN, around the neutralization burst, when $\nu_e$ are present, and $\bar{\nu}_e$ have not been produced yet.
 Such novel timing patterns generically exist in models with new weakly interacting particles, such as the aforementioned Majoron model~\cite{Fiorillo:2022cdq} and the neutrino magnetic moment portal~\cite{Magill:2018jla,Brdar:2020quo}.
 
-In this work we will show that, by using the timing measurements, neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association with forthcoming galactic SN events.\\
+In this work, we will show that, by using the timing measurements, neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association with forthcoming galactic SN events.\\
 %Via the timing measurement, we will show that neutrino telescopes will be able to provide powerful constraints on the BSM parameter space in association with forthcoming galactic SN events.\\
@@
 
-\textbf{\textit{The Model}}---
-Let us first consider the Majoron model, studied in Ref.~\cite{Fiorillo:2022cdq}, where SN 1987A constraints were derived.
+\textbf{\textit{The Model}}---First, we consider the Majoron model, studied in Ref.~\cite{Fiorillo:2022cdq}, where SN 1987A constraints were derived.
 The relevant part of the Lagrangian reads
@@
 \end{align}
-where $\phi$ is the (pseudo)scalar, $m_\phi$ is the respective mass, and $g$ parametrizes interaction strength between $\phi$ and neutrinos.
+where $\phi$ is the (pseudo)scalar, $m_\phi$ is its mass, and $g$ parametrizes interaction strength between $\phi$ and neutrinos.
 We assume flavor universal interaction and hence $g_{\alpha\beta}\equiv g_\phi \, \delta_{\alpha\beta}$. 
-Majorons are produced from (anti)neutrino coalescence in the star and subsequently decay to a pair of (anti)neutrinos resulting in BSM (anti)neutrino flux emitted from the star.
+Majorons are produced from (anti)neutrino coalescence in the star and subsequently decay to a pair of (anti)neutrinos, resulting in BSM (anti)neutrino flux emitted from the star.
 The total decay width is given by $\Gamma_\phi = 3g^2 m_\phi/16 \pi$.
@@
 After $\unit[0.05]{s}$, the flux of Majorons decreases with the total flux of neutrinos of all flavors.
-Thus we found that the Majoron flux peaks around $t \sim \unit[0.05]{s}$.
-We further cross checked the agreement with Ref.~\cite{Fiorillo:2022cdq} by reproducing their bound from SN energy loss.
+Thus, we found that the Majoron flux peaks around $t \sim \unit[0.05]{s}$.
+We further cross-checked the agreement with Ref.~\cite{Fiorillo:2022cdq} by reproducing their bound from SN energy loss.
 
@@
 The shaded regions correspond to the timing windows that give peak sensitivity to the particular model.
-These are the same benchmarks in the parameter space as in Fig.~\ref{fig:fluxes}.
+These are the same benchmarks in the parameter space as in \cref{fig:fluxes}.
     In the right panel, we show the test statistic as a function of the starting time and length of the window for the heavy Majoron benchmark ($m_\phi=200$ MeV).
@@
 
-\textbf{\textit{Detector Response and Statistical Treatment}}---The IceCube Neutrino Observatory comprises 5,160 light-detecting digital optical modules (DOMs) buried in a cubic kilometer of the deep, transparent Antarctic ice sheet.
+\textbf{\textit{Detector Response and Statistical Treatment}}---The IceCube Neutrino Observatory comprises 5,160 light-detecting digital optical modules (DOMs) buried in a cubic kilometer of the deep, transparent Antarctic ice sheet~\cite{IceCube:2016zyt}.
 The DOMs are arranged on 86 strings of 60 DOMs each, with an interstring distance of 125~m (70~m for the eight centermost strings).
@@
 Thus, one may look for excess events in certain time intervals as evidence of this new physics.
-In this work, we simulate the light curve produced by a standard SN with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios mentioned previously; see the left-hand panel of Fig.~\ref{fig:hits_and_likelihood} for light curves of the same two benchmarks from \cref{fig:fluxes}.
+In this work, we simulate the light curve produced by a standard SN with a progenitor mass of $8.8~M_{\odot}$ and those produced by different BSM scenarios mentioned previously; see the left-hand panel of \cref{fig:hits_and_likelihood} for light curves of the same two benchmarks from \cref{fig:fluxes}.
 
-Since more than 93\% of the photons detected in IceCube originate in IBD interactions, the SM-only event rate peaks at around 0.1~s.
+Since more than 93\% of the photons detected in IceCube originate in IBD interactions~\cite{IceCube:2011cwc}, the SM-only event rate peaks at around 0.1~s.
 BSM scenarios, on the other hand, can give rise to an early or delayed signal depending on the particulars of the model.
@@
 For each BSM hypothesis, we select the time range that maximizes the test statistic and use that maximal test statistic value.
-The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of Fig.~\ref{fig:hits_and_likelihood}, which is around $\unit[0.1]{s}$ ($\unit[10]{s}$) for the light (heavy) benchmark case, consistent with its time spread of the produced $\bar{\nu}_e$ flux.
+The optimal ranges for each physics hypothesis are shown by the shaded regions in the left panel of \cref{fig:hits_and_likelihood}, which is around $\unit[0.1]{s}$ ($\unit[10]{s}$) for the light (heavy) benchmark case, consistent with its time spread of the produced $\bar{\nu}_e$ flux.
 
-In the right-hand panel of Fig.~\ref{fig:hits_and_likelihood}, we show the test statistic as a function of the time at which the time range begins, $t_{\mathrm{start}}$, and the duration of the time range, $\Delta t$, for an example BSM hypothesis.
-The distribution of test-statistic values is not sharply peaked in time, and thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$~\cite{Halzen_2009}.
+In the right-hand panel of \cref{fig:hits_and_likelihood}, we show the test statistic as a function of the time at which the time range begins, $t_{\mathrm{start}}$, and the duration of the time range, $\Delta t$, for an example BSM hypothesis.
+The distribution of test-statistic values is not sharply peaked in time.
+Thus, this analysis retains much of its sensitivity even with errors on the reconstruction of $t_{\mathrm{bounce}}\sim\mathcal{O}\left(10^{-3}~\mathrm{s}\right)$~\cite{Halzen_2009}.
 
@@
 \end{figure} 
-Under the assumption that no excess neutrino were seen above the expected detector backgrounds and SM neutrinos, we obtain the expected $2\sigma$ exclusion limits by finding the coupling where Eq.~\ref{eq:likelihood} is equal to 3.841.
-These limits are presented in \cref{fig:sensitivity} for the Majoron case considering both IceCube and IceCube-Gen2.
+Assuming that IceCube does not observe an excess neutrino above the expected detector backgrounds and SM neutrinos, we obtain the expected $2\sigma$ exclusion limits by finding the coupling where \cref{eq:likelihood} is equal to 3.841.
+We show these in \cref{fig:sensitivity} for the Majoron case considering both IceCube and IceCube-Gen2.
 To illustrate the broad physics application of the analysis, we also show results for the sterile neutrino case with magnetic portal in the Supplemental Materials.
@@
 For light $\phi$ case with negligible time delay, IceCube would observe early signals in a time window separated from that when most of the SM flux contribution appears, as we show in the left panel of \cref{fig:hits_and_likelihood}, thus enhancing the reaches.
-On the high mass end, neutrino signals will arrive much later than the SM case, where a time window at late time can be considered to reduce the standard neutrino contaminations.
+On the high mass end, neutrino signals will arrive much later than the SM case, where a time window at late time can be considered to reduce the standard neutrino contamination.
 
@@
 This analysis can be extended to test other BSM realizations including, but not limited to, sterile neutrinos with a mixing portal.
+Additionally, the code used to probe these models is publicly available on \href{https://github.com/jlazar17/NuTel_SNe_BSM/}{GitHub}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\textit{Acknowledgements}---
-We would like to thank Thomas Janka and Daniel Kresse for providing the data from Garching supernovae simulations---available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/} in machine-readable form---and also for stimulating discussions.
-We would also like to thank Jackapan Pairin for their help designing figures in this work.
+\textit{Acknowledgements}---We want to thank Thomas Janka and Daniel Kresse for providing the data from Garching supernovae simulations---available at \url{https://wwwmpa.mpa-garching.mpg.de/ccsnarchive/} in machine-readable form---and also for stimulating discussions.
+We also thank Jackapan Pairin for their help designing figures in this work.
 Y.-Y. L is supported by the NSF of China through Grant No. 12305107, 12247103.
-CAA are supported by the Faculty of Arts and Sciences of Harvard University, the National Science Foundation (NSF), the NSF AI Institute for Artificial Intelligence and Fundamental Interactions (IAIFI), the Research Corporation for Science Advancement,
+CAA are supported by the Faculty of Arts and Sciences of Harvard University, the National Science Foundation (NSF), the NSF AI Institute for Artificial Intelligence and Fundamental Interactions, the Research Corporation for Science Advancement,
 and the David \& Lucile Packard Foundation.
 CAA and JL were partially supported by the Alfred P. Sloan Foundation for part of this work.
-JL is supported frbyom the Belgian American Educational Foundation.
+JL is supported by the Belgian American Educational Foundation.
 

### 2024-03-14 paper/main.tex
Updates from Overleaf

@@
 On their way to Earth, Majorons of energy $E_\phi$ will travel at the speed of $\beta$ for a distance of $L_1$, then decay to (anti)neutrinos of energy $E_\nu$ at an emission angle $\cos\alpha = (2 E_\phi E_{\nu} - m^2_\phi)/(2E_{\nu}E_\phi\beta)$.
-Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a SN that is $D_{\rm SN}$ away;see the decay geometry in \cref{fig:geometry}.
+Daughter (anti)neutrinos will travel for a distance $L_2$ and reach Earth at the angle $\theta$ satisfying $D_{\rm SN} \sin\theta = L_1 \sin\alpha$ for a SN that is $D_{\rm SN}$ away; see the decay geometry in \cref{fig:geometry}.
 The time delay, $\delta t$, relative to a relativistic particle moving along the line-of-sight path from a SN to reach the Earth is given by~\cite{Jaeckel:2017tud}
@@
     Additionally, we also show the reaches by SN cooling and by the lack of observation of high-energy neutrinos from SN1987A as black lines. 
-    The sensitivities shown by the dashed line is obtained following~\cite{Brdar:2023tmi} with time-integrated data.
+    The sensitivities shown by the dashed line are obtained following~\cite{Brdar:2023tmi} with time-integrated data.
     }
